### 2022-02-22 paper.tex
commit template

% --------------------------------------------------------------------------
% Template for IWAENC 2022 papers; to be used with:
%          spconfa4.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
%
% (Last modified by H. Loellmann, LMS, FAU Erlangen-Nuremberg, Jan. 2020)
%
% --------------------------------------------------------------------------

\documentclass{article}
\usepackage[preprint]{spconfa4}
\usepackage{amsmath,graphicx}

% IMPORTANT: Add copyright notice by uncommenting the appropriate line
%----------------------------------------------------------
% For papers in which all authors are employed by the US government,
% \copyrightnotice{U.S. Government work not protected by U.S. copyright}

% For papers in which all authors are employed by a Crown government (UK, Canada, and Australia)
% \copyrightnotice{978-1-6654-6867-1/22/\$31.00~\copyright2022 Crown}

% For papers in which all authors are employed by the European Union,
% \copyrightnotice{978-1-6654-6867-1/22/\$31.00~\copyright2022 European Union}

% For all other papers the copyright notice is
\copyrightnotice{978-1-6654-6867-1/22/\$31.00~\copyright2022 IEEE}

% Title.
% ------
\title{AUTHOR GUIDELINES FOR IWAENC 2022 PROCEEDINGS MANUSCRIPTS}
%
% Single address.
% ---------------
\name{Author(ss) Name(s)\thanks{Thanks to XYZ agency for funding.}}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically.
All manuscripts must be in English.
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

These guidelines include complete descriptions of the fonts, spacing, and related information for producing your proceedings manuscripts.
If you have any questions regarding the paper submission, please contact the conference organizers via email: \texttt{submission@iwaenc2022.org}\,.

\section{Formatting your paper}
\label{sec:format}

The properly formatted paper should be not longer than 4 pages in A4 format (210 mm x 297 mm).  All printed material, including text, illustrations, and charts, must be kept within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do not write or print anything outside the print area. The top margin must be 1 inch (25 mm), except for the title page, and the left margin must be 0.63 inch (16 mm).  All \textit{text} must be in a two-column format. Columns are to be 3.39 inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be fully justified.

\section{Page Title Section}
\label{sec:pagestyle}

The paper title (on the first page) should begin 1.38 inches (35 mm) from the top edge of the page, centered, completely capitalized, and in Times 12-point, boldface type.  The authors' name(s) and affiliation(s) appear below the title in capital and lower case letters.  Papers with multiple authors and affiliations may require two or more lines for this information. Please note that papers must include the authors’ name(s) and affiliation(s) on the PDF.

\section{Type-Style and Fonts}
\label{sec:typestyle}

To achieve the best rendering, we strongly encourage you to use Times-Roman font.  In addition, this will give the online proceedings a more uniform look. Use a font that is no smaller than 9-point type throughout the paper, including figure captions.

In 9-point type font, capital letters are 2 mm high.  If you use the smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make the paper much more readable.  Larger type sizes require correspondingly larger vertical spacing.  Please do not double-space your paper.  TrueType or Postscript Type 1 fonts are preferred.

The first paragraph in each section should not be indented, but all the following paragraphs within the section should be indented as these paragraphs
demonstrate.

\section{Major Headings}
\label{sec:majhead}

Major headings, for example, ``1. Introduction'', should appear in all capital letters, bold face if possible, centered in the column, with one blank line before, and one blank line after. Use a period (``.'') after the heading number, not a colon.

\subsection{Subheadings}
\label{ssec:subhead}

Subheadings should appear in lower case (initial word capitalized) in boldface.  They should start at the left margin on a separate line.

\subsubsection{Sub-subheadings}
\label{sssec:subsubhead}

Sub-subheadings, as in this paragraph, are discouraged. However, if you must use them, they should appear in lower case (initial word capitalized) and start at the left margin on a separate line, with paragraph text beginning on the following line.  They should be in italics.

\section{Page Numbering}
\label{sec:page}

Please do \textbf{not} paginate your paper.  Page numbers and conference identification will be inserted when the paper is included in the proceedings.

\section{Illustrations, Graphs, and Photographs}
\label{sec:illust}

Illustrations must appear within the designated margins.  They may span the two columns.  If possible, position illustrations at the top of columns, rather than in the middle or at the bottom.  Caption and number every illustration. All halftone illustrations must be clear black-and-white prints.  Colors may be used, but they should be selected so as to be readable when printed on a black-only printer.

There are many (often incompatible) ways of including images (e.g., with experimental results) in a LaTeX document, and an example of how to do
this is provided by Fig~\ref{fig:example}.

\begin{figure}[tb]

	\begin{minipage}[b]{1.0\linewidth}
		\centering
		\centerline{\includegraphics[width=8.5cm]{image1}}
		%  \vspace{2.0cm}
		\centerline{(a) Result 1}\medskip
	\end{minipage}
	%
	\begin{minipage}[b]{.48\linewidth}
		\centering
		\centerline{\includegraphics[width=4.0cm]{image3}}
		%  \vspace{1.5cm}
		\centerline{(b) Results 2}\medskip
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.48\linewidth}
		\centering
		\centerline{\includegraphics[width=4.0cm]{image4}}
		%  \vspace{1.5cm}
		\centerline{(c) Result 3}\medskip
	\end{minipage}
	%
	\caption{Example of placing a figure with results.}
	\label{fig:example}
	%
\end{figure}

\section{Footnotes}
\label{sec:foot}

Use footnotes sparingly (or not at all!) and place them at the bottom of the column on the page on which they are referenced. Use Times 9-point type,
single-spaced. To help your readers, avoid using footnotes altogether and include necessary peripheral observations in the text (within parentheses, if
you prefer, as in this sentence).

\section{Relation To Prior Work}
\label{sec:prior}

The text of the paper should contain discussions on how the paper's contributions are related to prior work in the field. It is important to put new work in  context, to give credit to foundational work, and to provide details associated with the previous work that have appeared in the literature. This discussion may be a separate, numbered section or it may appear elsewhere in the body of the manuscript, but it must be present. You should differentiate what is new and how your work expands on or takes a different path from prior studies.

\section{References}
\label{sec:ref}

List and number all bibliographical references at the end of the paper.  The references can be numbered in alphabetical order or in order of appearance in the document.  When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{Smith,Jones}. An additional final page (the fifth page, in most cases) is allowed, but must contain only references to the prior literature.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2022-04-05 paper.tex
only admm not dist, do tests.

@@
 \usepackage{amsmath,graphicx}
+\input{preamble.tex}
 
@@
 % ------
-\title{AUTHOR GUIDELINES FOR IWAENC 2022 PROCEEDINGS MANUSCRIPTS}
+\title{CROSS-RELATION BASED BLIND SYSTEM IDENTIFICATION USING ADMM}
 %
@@
 % ---------------
-\name{Author(ss) Name(s)\thanks{Thanks to XYZ agency for funding.}}
-\address{Author Affiliation(s)}
+\name{Matthias Blochberger\sthanks{THANK EU!}, Filip Elvander\sthanks{THANK FWO?}, Randall Ali, Toon van Waterschoot}
+\address{KU Leuven\\ESAT - Department of Electrical Engineering\\STADIUS\\3001 Leuven}
 %
@@
 \begin{abstract}
-The abstract should appear at the top of the left-hand column of text, about
-0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
-length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
-beginning of the main text.  The abstract should contain about 100 to 150
-words, and should be identical to the abstract text submitted electronically.
+The abstract should appear at the top of the left-hand column of text, about 0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in length.
+Leave a 0.5 inch (12 mm) space between the end of the abstract and the beginning of the main text.
+The abstract should contain about 100 to 150 words, and should be identical to the abstract text submitted electronically.
 All manuscripts must be in English.
@@
 
-\section{Formatting your paper}
-\label{sec:format}
+\section{Problem statement}
+\label{sec:problem_statement}
 
-The properly formatted paper should be not longer than 4 pages in A4 format (210 mm x 297 mm).
-All printed material, including text, illustrations, and charts, must be kept within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high.
-Do not write or print anything outside the print area.
-The top margin must be 1 inch (25 mm), except for the title page, and the left margin must be 0.63 inch (16 mm).
-All \textit{text} must be in a two-column format.
-Columns are to be 3.39 inches (86 mm) wide, with a 0.24 inch (6 mm) space between them.
-Text must be fully justified.
+\section{Distributed BSI}
+\label{sec:admm_bsi}
 
-\section{Page Title Section}
-\label{sec:pagestyle}
+\subsection{ADMM?}
+\label{ssec:admm}
 
-The paper title (on the first page) should begin 1.38 inches (35 mm) from the top edge of the page, centered, completely capitalized, and in Times 12-point, boldface type.
-The authors' name(s) and affiliation(s) appear below the title in capital and lower case letters.
-Papers with multiple authors and affiliations may require two or more lines for this information.
-Please note that papers must include the authors’ name(s) and affiliation(s) on the PDF.
+\section{Numerical Evaluation}
+\label{sec:num_eval}
 
-\section{Type-Style and Fonts}
-\label{sec:typestyle}
+\section{Conclusion}
+\label{sec:conclusion}
 
-To achieve the best rendering, we strongly encourage you to use Times-Roman font.
-In addition, this will give the online proceedings a more uniform look.
-Use a font that is no smaller than 9-point type throughout the paper, including figure captions.
+% \begin{figure}[tb]
 
-In 9-point type font, capital letters are 2 mm high.  If you use the smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
-vertically.
-This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make the paper much more readable.
-Larger type sizes require correspondingly larger vertical spacing.
-Please do not double-space your paper.
-TrueType or Postscript Type 1 fonts are preferred.
-
-The first paragraph in each section should not be indented, but all the following paragraphs within the section should be indented as these paragraphs
-demonstrate.
-
-\section{Major Headings}
-\label{sec:majhead}
-
-Major headings, for example, ``1.
-Introduction'', should appear in all capital letters, bold face if possible, centered in the column, with one blank line before, and one blank line after.
-Use a period (``.'') after the heading number, not a colon.
-
-\subsection{Subheadings}
-\label{ssec:subhead}
-
-Subheadings should appear in lower case (initial word capitalized) in boldface.  They should start at the left margin on a separate line.
-
-\subsubsection{Sub-subheadings}
-\label{sssec:subsubhead}
-
-Sub-subheadings, as in this paragraph, are discouraged.
-However, if you must use them, they should appear in lower case (initial word capitalized) and start at the left margin on a separate line, with paragraph text beginning on the following line.
-They should be in italics.
-
-\section{Page Numbering}
-\label{sec:page}
-
-Please do \textbf{not} paginate your paper.  Page numbers and conference identification will be inserted when the paper is included in the proceedings.
-
-\section{Illustrations, Graphs, and Photographs}
-\label{sec:illust}
-
-Illustrations must appear within the designated margins.
-They may span the two columns.
-If possible, position illustrations at the top of columns, rather than in the middle or at the bottom.
-Caption and number every illustration.
-All halftone illustrations must be clear black-and-white prints.
-Colors may be used, but they should be selected so as to be readable when printed on a black-only printer.
-
-There are many (often incompatible) ways of including images (e.g., with experimental results) in a LaTeX document, and an example of how to do
-this is provided by Fig~\ref{fig:example}.
-
-\begin{figure}[tb]
-
-	\begin{minipage}[b]{1.0\linewidth}
-		\centering
-		\centerline{\includegraphics[width=8.5cm]{image1}}
-		%  \vspace{2.0cm}
-		\centerline{(a) Result 1}\medskip
-	\end{minipage}
-	%
-	\begin{minipage}[b]{.48\linewidth}
-		\centering
-		\centerline{\includegraphics[width=4.0cm]{image3}}
-		%  \vspace{1.5cm}
-		\centerline{(b) Results 2}\medskip
-	\end{minipage}
-	\hfill
-	\begin{minipage}[b]{0.48\linewidth}
-		\centering
-		\centerline{\includegraphics[width=4.0cm]{image4}}
-		%  \vspace{1.5cm}
-		\centerline{(c) Result 3}\medskip
-	\end{minipage}
-	%
-	\caption{Example of placing a figure with results.}
-	\label{fig:example}
-	%
-\end{figure}
-
-\section{Footnotes}
-\label{sec:foot}
-
-Use footnotes sparingly (or not at all!) and place them at the bottom of the column on the page on which they are referenced. Use Times 9-point type,
-single-spaced. To help your readers, avoid using footnotes altogether and include necessary peripheral observations in the text (within parentheses, if
-you prefer, as in this sentence).
-
-\section{Relation To Prior Work}
-\label{sec:prior}
-
-The text of the paper should contain discussions on how the paper's contributions are related to prior work in the field.
-It is important to put new work in  context, to give credit to foundational work, and to provide details associated with the previous work that have appeared in the literature.
-This discussion may be a separate, numbered section or it may appear elsewhere in the body of the manuscript, but it must be present.
-You should differentiate what is new and how your work expands on or takes a different path from prior studies.
-
-\section{References}
-\label{sec:ref}
-
-List and number all bibliographical references at the end of the paper.
-The references can be numbered in alphabetical order or in order of appearance in the document.
-When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{Smith,Jones}.
-An additional final page (the fifth page, in most cases) is allowed, but must contain only references to the prior literature.
+% 	\begin{minipage}[b]{1.0\linewidth}
+% 		\centering
+% 		\centerline{\includegraphics[width=8.5cm]{image1}}
+% 		%  \vspace{2.0cm}
+% 		\centerline{(a) Result 1}\medskip
+% 	\end{minipage}
+% 	%
+% 	\begin{minipage}[b]{.48\linewidth}
+% 		\centering
+% 		\centerline{\includegraphics[width=4.0cm]{image3}}
+% 		%  \vspace{1.5cm}
+% 		\centerline{(b) Results 2}\medskip
+% 	\end{minipage}
+% 	\hfill
+% 	\begin{minipage}[b]{0.48\linewidth}
+% 		\centering
+% 		\centerline{\includegraphics[width=4.0cm]{image4}}
+% 		%  \vspace{1.5cm}
+% 		\centerline{(c) Result 3}\medskip
+% 	\end{minipage}
+% 	%
+% 	\caption{Example of placing a figure with results.}
+% 	\label{fig:example}
+% 	%
+% \end{figure}
 
@@
 % -------------------------------------------------------------------------
-\bibliographystyle{IEEEbib}
-\bibliography{refs}
+% \bibliographystyle{IEEEbib}
+% \bibliography{refs}
 

### 2022-04-12 python/admm_newton_fq.py
some simulation stuff

@@ -1,0 +1,309 @@
+import numpy as np
+
+
+class NodeProcessor:
+    def __init__(self, id, filter_len, rho) -> None:
+        # identifier for node
+        self.id = id
+        # iterator
+        self.k = 0
+        # local solver type
+        self.type = type
+        # definition of signal connections
+        self.group = None
+        # number of FIR filter taps
+        self.L = filter_len
+        # step size / penalty parameter
+        self.rho = rho
+        # step size / penalty parameter
+        self.mu = 1
+        self.eta = 0.98
+        # number of "channels"
+        self.N = None
+        # signal block
+        self.block = None
+        # local primal
+        self.x = None
+        # local dual
+        self.y = None
+        # local dual est old
+        self.z_l = None
+        # estimated
+        self.R_xp_ = None
+        # buffer
+        self.R_buffer = None
+
+        self.setBufferSize(1)
+        pass
+
+    def setLocalSize(self, N) -> None:
+        self.N = N
+        # global indices
+        self.global_indices = None
+        self.reset()
+        pass
+
+    def setBufferSize(self, buffer_size) -> None:
+        self.buffer_size = buffer_size
+        self.buffer_ind = 0
+        # self.reset()
+        pass
+
+    def reset(self) -> None:
+        # signal block
+        self.block = np.zeros(shape=(self.L, self.N), dtype=np.complex128)
+        # local primal
+        self.x = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # self.x[0::self.L] = 1
+        # local dual
+        self.y = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # local copy of global primal
+        self.z_l = np.ones(shape=(self.L * self.N, 1), dtype=np.complex128) / np.sqrt(
+            self.L
+        )
+
+        F_LxL = self.DFT_matrix(self.L)
+        F_2Lx2L = self.DFT_matrix(2 * self.L)
+
+        W_01_Lx2L = np.concatenate([np.zeros(shape=(self.L, self.L)), np.eye(self.L)]).T
+        W_10_2LxL = np.concatenate([np.eye(self.L), np.zeros(shape=(self.L, self.L))])
+
+        self.W_01_Lx2L_fq = F_LxL @ W_01_Lx2L @ np.linalg.inv(F_2Lx2L)
+        self.W_10_2LxL_fq = F_2Lx2L @ W_10_2LxL @ np.linalg.inv(F_LxL)
+
[…]

### 2022-04-12 python/admm_newton_fq_diag.py

@@ -1,0 +1,314 @@
+import numpy as np
+
+
+class NodeProcessor:
+    def __init__(self, id, filter_len, rho) -> None:
+        # identifier for node
+        self.id = id
+        # iterator
+        self.k = 0
+        # local solver type
+        self.type = type
+        # definition of signal connections
+        self.group = None
+        # number of FIR filter taps
+        self.L = filter_len
+        # step size / penalty parameter
+        self.rho = rho
+        # step size / penalty parameter
+        self.mu = 1
+        self.eta = 0.98
+        # number of "channels"
+        self.N = None
+        # signal block
+        self.block = None
+        # local primal
+        self.x = None
+        # local dual
+        self.y = None
+        # local dual est old
+        self.z_l = None
+        # estimated
+        self.R_xp_ = None
+        # buffer
+        self.R_buffer = None
+
+        self.setBufferSize(1)
+        pass
+
+    def setLocalSize(self, N) -> None:
+        self.N = N
+        # global indices
+        self.global_indices = None
+        self.reset()
+        pass
+
+    def setBufferSize(self, buffer_size) -> None:
+        self.buffer_size = buffer_size
+        self.buffer_ind = 0
+        # self.reset()
+        pass
+
+    def reset(self) -> None:
+        # signal block
+        self.block = np.zeros(shape=(self.L, self.N), dtype=np.complex128)
+        # local primal
+        self.x = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # self.x[0::self.L] = 1
+        # local dual
+        self.y = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # local copy of global primal
+        self.z_l = np.ones(shape=(self.L * self.N, 1), dtype=np.complex128) / np.sqrt(
+            self.L
+        )
+
+        F_LxL = self.DFT_matrix(self.L)
+        F_2Lx2L = self.DFT_matrix(2 * self.L)
+
+        W_01_Lx2L = np.concatenate([np.zeros(shape=(self.L, self.L)), np.eye(self.L)]).T
+        W_10_2LxL = np.concatenate([np.eye(self.L), np.zeros(shape=(self.L, self.L))])
+
+        self.W_01_Lx2L_fq = F_LxL @ W_01_Lx2L @ np.linalg.inv(F_2Lx2L)
[…]

### 2022-04-12 python/admm_r1_td.py

@@ -1,0 +1,348 @@
+import numpy as np
+
+
+class NodeProcessor:
+    def __init__(self, id, filter_len, rho) -> None:
+        # identifier for node
+        self.id = id
+        # iterator
+        self.k = 0
+        # local solver type
+        self.type = type
+        # definition of signal connections
+        self.group = None
+        # number of FIR filter taps
+        self.L = filter_len
+        # step size / penalty parameter
+        self.rho = rho
+        self.mu = 0.5
+        self.eta = 0.95
+        self.zeta = 0.95
+        # number of "channels"
+        self.N = None
+        # signal block
+        self.block = None
+        # local primal
+        self.x = None
+        # local dual
+        self.y = None
+        # local dual est
+        self.y_hat = None
+        # local dual est old
+        self.z_l = None
+        # estimated
+        self.H_i = None
+        # buffer
+
+        # self.setBufferSize(2 * self.L)
+        pass
+
+    def setLocalSize(self, N) -> None:
+        self.N = N
+        # global indices
+        self.global_indices = None
+        self.reset()
+        pass
+
+    def setBufferSize(self, buffer_size) -> None:
+        self.buffer_size = buffer_size
+        self.buffer = np.zeros((self.L, self.N, self.buffer_size))
+        # self.reset()
+        pass
+
+    def reset(self) -> None:
+        self.k = 0
+        # signal block
+        self.block = np.zeros(shape=(self.L, self.N))
+        # local primal
+        # self.x = np.zeros(shape=(self.L * self.N, 1))
+        self.x = np.random.normal(size=(self.L * self.N, 1))
+        # self.x[0 :: self.L] = 1
+        # local dual
+        self.y = np.zeros(shape=(self.L * self.N, 1))
+        # local dual est
+        # self.z_l = np.zeros(shape=(self.L*self.N, 1))
+        # self.z_l[0::self.L] = 1
+        # self.z_l = np.ones(shape=(self.L*self.N, 1))
+        self.z_l = np.random.normal(size=(self.L * self.N, 1))
+        # estimated cross-correlatino difference matrix
+        self.R = np.zeros((self.L * self.N, self.L * self.N))
+        self.R1 = np.zeros((self.L * self.N, self.L * self.N))
+        self.H_i = np.eye(self.L * self.N) / self.rho
+        self.H_i1 = np.eye(self.L * self.N) / self.rho
+        self.first = True
+
+        self.buffer_size = self.L
[…]

### 2022-04-12 python/plot_data.py

@@ -1,0 +1,198 @@
+# %%
+import os
+import numpy as np
+import time
+import utils
+
+# import scipy.signal as signal
+import matplotlib.pyplot as plt
+
+# %%
+class SimulationData:
+    variable: str
+    variable_range: list
+
+
+# %%
+SNRs = [5, 10, 15, 20, 30, 40, 50]
+id = 0
+runs_ = []
+run_ = []
+L_ = []
+N_sens_ = []
+SNR_ = []
+h_ = []
+err_MCQN_ = {}
+err_NMCFLMS_ = {}
+err_RNMCFLMS_ = {}
+err_LPRNMCFLMS_ = {}
+err_ADMM_newton_td_ = {}
+err_ADMM_newton_fq_ = {}
+err_ADMM_newton_fq_diag_ = {}
+for SNR in SNRs:
+    err_MCQN_[SNR] = None
+    err_NMCFLMS_[SNR] = None
+    err_RNMCFLMS_[SNR] = None
+    err_LPRNMCFLMS_[SNR] = None
+    err_ADMM_newton_td_[SNR] = None
+    err_ADMM_newton_fq_[SNR] = None
+    err_ADMM_newton_fq_diag_[SNR] = None
+dir = "data/"
+files = sorted(os.listdir(dir))
+
+# %%
+for filename in files:
+    print(filename)
+    with open(dir + filename, "rb") as f:
+        runs = np.load(f)
+        run = np.load(f)
+        L = np.load(f)
+        N_sens = np.load(f)
+        SNR = int(np.load(f))
+        h = np.load(f)
+        err_MCQN = np.load(f)
+        err_NMCFLMS = np.load(f)
+        err_RNMCFLMS = np.load(f)
+        err_LPRNMCFLMS = np.load(f)
+        err_ADMM_newton_td = np.load(f)
+        err_ADMM_newton_fq = np.load(f)
+        err_ADMM_newton_fq_diag = np.load(f)
+
+        err_MCQN_[SNR] = (
+            err_MCQN
+            if err_MCQN_[SNR] is None
+            else np.vstack((err_MCQN_[SNR], err_MCQN))
+        )
+        err_NMCFLMS_[SNR] = (
+            err_NMCFLMS
+            if err_NMCFLMS_[SNR] is None
+            else np.vstack((err_NMCFLMS_[SNR], err_NMCFLMS))
+        )
[…]

### 2022-04-12 python/simo_bsi_central.py

@@ -1,0 +1,557 @@
+import numpy as np
+
+
+class MCALG:
+    def __init__(self, L, N, buffer_size) -> None:
+        self.L = L
+        self.N = N
+        self.buffer_size = buffer_size
+        self.R_buffer = np.zeros(shape=(self.buffer_size, N, N, L, L))
+        self.buffer_ind = 0
+
+    def compute_X(self, x) -> float:
+        X = 0
+        for i in range(self.N - 1):
+            for j in range(i + 1, self.N):
+                e = (
+                    x[:, i, None][::-1].T @ self.h[(j * self.L) : (j * self.L + self.L)]
+                    - x[:, j, None][::-1].T
+                    @ self.h[(i * self.L) : (i * self.L + self.L)]
+                )
+                X += e ** 2
+        return X
+
+    def compute_X_prior(self, x) -> float:
+        X = 0
+        for i in range(self.N - 1):
+            for j in range(i + 1, self.N):
+                e = (
+                    x[:, i, None][::-1].T
+                    @ self.h_old[(j * self.L) : (j * self.L + self.L)]
+                    - x[:, j, None][::-1].T
+                    @ self.h_old[(i * self.L) : (i * self.L + self.L)]
+                )
+                X += e ** 2
+        return X
+
+    def construct_Rxp(self, x):
+        R_xp = np.zeros(shape=(self.L * self.N, self.L * self.N))
+        for i in range(self.N):
+            for j in range(self.N):
+                R_xx = self.compute_Rxx(i, j, x)
+                if i != j:
+                    R_xp[
+                        j * self.L : j * self.L + self.L,
+                        i * self.L : i * self.L + self.L,
+                    ] = -R_xx
+                else:
+                    for n in range(self.N):
+                        if i != n:
+                            R_xp[
+                                n * self.L : n * self.L + self.L,
+                                n * self.L : n * self.L + self.L,
+                            ] += R_xx
+        self.buffer_ind += 1
[…]

### 2022-04-12 python/simulation_random.py

@@ -1,0 +1,300 @@
+# %%
+import sys
+import os.path
+import utils
+import numpy as np
+import scipy.signal as signal
+import admm_r1_td as admm
+import admm_newton_fq as sb_newton_fq
+import admm_newton_fq_diag as sb_newton_fq_diag
+import simo_bsi_central as cent
+import matplotlib.pyplot as plt
+
+# %%
+inp = int(sys.argv[1])
+SNRs = [5, 10, 15, 20, 30, 40, 50]
+SNR = SNRs[inp]
+print("Job: " + sys.argv[1] + "SNR: %d dB" % (SNR))
+
+# %%
+runs = 50
+plot = False
+
+# %%
+L = 64
+N_f = 1024
+N_sens = 3
+
+# %%
+N_s = 16000
+
+# %%
+seed = 12345
+rng = np.random.RandomState()
+rng.seed(seed)
+
+# %%
+for run in range(runs):
+    if os.path.isfile("data/%d_%d.npy" % (inp, run)):
+        print("run %d is already there" % (run))
+        continue
+    # %%
+    h = np.array([]).reshape(0, 1)
+    h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
+    for n in range(N_sens):
+        h_ = rng.normal(size=(L, 1))
+        h_ = h_ / np.linalg.norm(h_)
+        w, hh = signal.freqz(h_, worN=N_f)
+        h_f[n, :] = hh
+        h = np.concatenate([h, h_])
+
+    # %%
+    if plot:
+        fig, ax1 = plt.subplots()
+        ax1.set_title("Digital filter frequency response")
+        for n in range(N_sens):
+            ax1.plot(w, 20 * np.log10(abs(h_f[n, :])))
+        ax1.set_ylabel("Amplitude [dB]")
+        ax1.set_xlabel("Frequency [rad/sample]")
+        ax1.grid()
+        plt.show()
+
+    # %%
+    if plot:
+        plt.stem(h)
+        plt.title("filter taps of stacked imp resp")
+        plt.show()
+
+    # %%
+    network_td = admm.Network(L)
+    rho = 1
+    network_td.addNode("node1", rho)
+    network_td.addNode("node2", rho)
+    network_td.addNode("node3", rho)
+
+    # node 1 sends to node 2 and 3
[…]

### 2022-04-12 python/simulation_random_connectivity.py

@@ -1,0 +1,299 @@
+# %%
+import sys
+import os.path
+import utils
+import numpy as np
+import scipy.signal as signal
+import admm_r1_td as admm
+import admm_newton_fq as sb_newton_fq
+import admm_newton_fq_diag as sb_newton_fq_diag
+import simo_bsi_central as cent
+import matplotlib.pyplot as plt
+
+# %%
+inp = int(sys.argv[1])
+SNRs = [5, 10, 15, 20, 30, 40, 50]
+SNR = SNRs[inp]
+print("Job: " + sys.argv[1] + "SNR: %d dB" % (SNR))
+
+# %%
+runs = 50
+plot = False
+
+# %%
+L = 64
+N_f = 1024
+N_sens = 3
+
+# %%
+N_s = 8000
+
+# %%
+seed = 12345
+rng = np.random.RandomState()
+rng.seed(seed)
+
+# %%
+for run in range(runs):
+    if os.path.isfile("data/%d_%d.npy" % (inp, run)):
+        continue
+    # %%
+    h = np.array([]).reshape(0, 1)
+    h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
+    for n in range(N_sens):
+        h_ = rng.normal(size=(L, 1))
+        h_ = h_ / np.linalg.norm(h_)
+        w, hh = signal.freqz(h_, worN=N_f)
+        h_f[n, :] = hh
+        h = np.concatenate([h, h_])
+
+    # %%
+    if plot:
+        fig, ax1 = plt.subplots()
+        ax1.set_title("Digital filter frequency response")
+        for n in range(N_sens):
+            ax1.plot(w, 20 * np.log10(abs(h_f[n, :])))
+        ax1.set_ylabel("Amplitude [dB]")
+        ax1.set_xlabel("Frequency [rad/sample]")
+        ax1.grid()
+        plt.show()
+
+    # %%
+    if plot:
+        plt.stem(h)
+        plt.title("filter taps of stacked imp resp")
+        plt.show()
+
+    # %%
+    network_td = admm.Network(L)
+    rho = 1
+    network_td.addNode("node1", rho)
+    network_td.addNode("node2", rho)
+    network_td.addNode("node3", rho)
+
+    # node 1 sends to node 2 and 3
+    network_td.setConnection("node1", ["node2"])
[…]

### 2022-04-12 python/simulation_simir.py

@@ -1,0 +1,164 @@
+# %%
+import utils
+import numpy as np
+import scipy.signal as signal
+import admm_r1_td as admm
+import simo_bsi_central as cent
+import matplotlib.pyplot as plt
+
+# %%
+L = 64
+N_f = 1024
+N_sens = 3
+
+# %%
+fs = 16000
+l = 120
+N_s = 8000
+
+# %%
+with open("h.npy", "rb") as f:
+    h = np.load(f)
+
+# %%
+h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
+fig, ax1 = plt.subplots()
+ax1.set_title("Digital filter frequency response")
+for n in range(N_sens):
+    h_ = h[n * L : (n + 1) * L]
+    w, hh = signal.freqz(h_, worN=N_f)
+    h_f[n, :] = hh
+    ax1.plot(w, 20 * np.log10(abs(hh)))
+    # plt.legend()
+ax1.set_ylabel("Amplitude [dB]")
+ax1.set_xlabel("Frequency [rad/sample]")
+ax1.grid()
+plt.show()
+
+# %%
+plt.stem(h)
+plt.title("filter taps of stacked imp resp")
+plt.show()
+
+# %%
+network_td = admm.Network(L)
+rho = 1
+network_td.addNode("node1", rho)
+network_td.addNode("node2", rho)
+network_td.addNode("node3", rho)
+
+# node 1 sends to node 2 and 3
+network_td.setConnection("node1", ["node2"])
+# network_td.setConnection("node2", ["node1"])
+network_td.setConnection("node2", ["node3"])
+network_td.setConnection("node3", ["node1"])
+network_td.setBufferSize(1)
+
+# %% GENERATE AR SIGNAL
+N_ff = 1025
+b1 = signal.firwin(N_ff, 0.25, pass_zero=False)
+M = 10
+Ah = np.zeros((M, N_ff - M - 1))
+for l in range(M):
+    Ah[l, :] = b1[M - l : M - l + N_ff - M - 1]
+y = b1[M + 1 :]
+a_ = np.linalg.solve(Ah @ Ah.T, Ah @ y)
+b = np.concatenate([np.ones((1,)), -a_])
+
+# %%
+p0 = 1e-2
+u = np.random.normal(size=(N_s, 1)) * np.sqrt(p0)
+# %%
[…]

### 2022-04-14 python/plot_data.py
plots

@@ -58,41 +58,48 @@ for filename in files:
         err_ADMM_newton_fq = np.load(f)
         err_ADMM_newton_fq_diag = np.load(f)
 
-        err_MCQN_[SNR] = (
-            err_MCQN
-            if err_MCQN_[SNR] is None
-            else np.vstack((err_MCQN_[SNR], err_MCQN))
-        )
-        err_NMCFLMS_[SNR] = (
-            err_NMCFLMS
-            if err_NMCFLMS_[SNR] is None
-            else np.vstack((err_NMCFLMS_[SNR], err_NMCFLMS))
-        )
-        err_RNMCFLMS_[SNR] = (
-            err_RNMCFLMS
-            if err_RNMCFLMS_[SNR] is None
-            else np.vstack((err_RNMCFLMS_[SNR], err_RNMCFLMS))
-        )
-        err_LPRNMCFLMS_[SNR] = (
-            err_LPRNMCFLMS
-            if err_LPRNMCFLMS_[SNR] is None
-            else np.vstack((err_LPRNMCFLMS_[SNR], err_LPRNMCFLMS))
-        )
-        err_ADMM_newton_td_[SNR] = (
-            err_ADMM_newton_td
-            if err_ADMM_newton_td_[SNR] is None
-            else np.vstack((err_ADMM_newton_td_[SNR], err_ADMM_newton_td))
-        )
-        err_ADMM_newton_fq_[SNR] = (
-            err_ADMM_newton_fq
-            if err_ADMM_newton_fq_[SNR] is None
-            else np.vstack((err_ADMM_newton_fq_[SNR], err_ADMM_newton_fq))
-        )
-        err_ADMM_newton_fq_diag_[SNR] = (
-            err_ADMM_newton_fq_diag
-            if err_ADMM_newton_fq_diag_[SNR] is None
-            else np.vstack((err_ADMM_newton_fq_diag_[SNR], err_ADMM_newton_fq_diag))
-        )
+        if not np.isnan(err_MCQN).any():
+            err_MCQN_[SNR] = (
+                err_MCQN
+                if err_MCQN_[SNR] is None
+                else np.vstack((err_MCQN_[SNR], err_MCQN))
+            )
+        if not np.isnan(err_NMCFLMS).any():
+            err_NMCFLMS_[SNR] = (
+                err_NMCFLMS
[…]

### 2022-04-14 python/simulation_random.py

@@ -17,16 +17,16 @@ SNR = SNRs[inp]
 print("Job: " + sys.argv[1] + "SNR: %d dB" % (SNR))
 
 # %%
-runs = 50
+runs = 100
 plot = False
 
 # %%
-L = 64
+L = 16
 N_f = 1024
 N_sens = 3
 
 # %%
-N_s = 16000
+N_s = 8000
 
 # %%
 seed = 12345
@@ -140,7 +140,7 @@ for run in range(runs):
     # %% CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD
     print("CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD")
     err_MCQN = []
-    rho = 0.4  # step size
+    rho = 0.5  # step size
     lambd = 1e-5  # regularization
     eta = 0.98  # forgetting factor
     buffer_size = L
@@ -155,7 +155,7 @@ for run in range(runs):
     # %% CENTRALIZED NORMALIZED FREQUENCY DOMAIN LMS METHOD
     print("CENTRALIZED NORMALIZED FREQUENCY DOMAIN LMS METHOD")
     err_NMCFLMS = []
-    rho = 0.1  # step size
+    rho = 0.4  # step size
     lambd = 0.98  # forgetting factor
     sigma = 0.01  # regularization
     bsi_nmcflms = cent.NMCFLMS(rho, lambd, sigma, L, N_sens)
@@ -167,7 +167,7 @@ for run in range(runs):
     # %% CENTRALIZED ROBUST NORMALIZED FREQUENCY DOMAIN LMS METHOD
     print("CENTRALIZED ROBUST NORMALIZED FREQUENCY DOMAIN LMS METHOD")
     err_RNMCFLMS = []
-    rho = 0.1  # step size
+    rho = 0.25  # step size
     lambd = 0.98  # forgetting factor
     sigma = 0.01  # regularization
     eta = 0.4  # coupling factor
@@ -182,7 +182,7 @@ for run in range(runs):
         "CENTRALIZED l_p NORM CONSTRAINED ROBUST NORMALIZED FREQUENCY DOMAIN LMS METHOD"
     )
     err_LPRNMCFLMS = []
-    rho = 0.1  # step size
+    rho = 0.3  # step size
     lambd = 0.98  # forgetting factor
     sigma = 0.01  # regularization
     eta = 0.4  # coupling factor
[…]

### 2022-04-14 python/simulation_random_connectivity.py

@@ -17,16 +17,16 @@ SNR = SNRs[inp]
 print("Job: " + sys.argv[1] + "SNR: %d dB" % (SNR))
 
 # %%
-runs = 50
+runs = 20
 plot = False
 
 # %%
-L = 64
+L = 16
 N_f = 1024
-N_sens = 3
+N_sens = 5
 
 # %%
-N_s = 8000
+N_s = 16000
 
 # %%
 seed = 12345
@@ -36,6 +36,7 @@ rng.seed(seed)
 # %%
 for run in range(runs):
     if os.path.isfile("data/%d_%d.npy" % (inp, run)):
+        print("run %d is already there" % (run))
         continue
     # %%
     h = np.array([]).reshape(0, 1)
@@ -70,36 +71,47 @@ for run in range(runs):
     network_td.addNode("node1", rho)
     network_td.addNode("node2", rho)
     network_td.addNode("node3", rho)
+    network_td.addNode("node4", rho)
+    network_td.addNode("node5", rho)
 
     # node 1 sends to node 2 and 3
-    network_td.setConnection("node1", ["node2"])
-    # network_td.setConnection("node2", ["node1"])
+    network_td.setConnection("node1", ["node2", "node3"])
     network_td.setConnection("node2", ["node3"])
-    network_td.setConnection("node3", ["node1"])
+    network_td.setConnection("node3", ["node4"])
+    network_td.setConnection("node4", ["node5"])
+    network_td.setConnection("node5", ["node1"])
     network_td.setBufferSize(1)
 
     network_newton_fq = sb_newton_fq.Network(L)
-    ρ = 0.01
-    network_newton_fq.addNode("node1", ρ)
-    network_newton_fq.addNode("node2", ρ)
-    network_newton_fq.addNode("node3", ρ)
+    rho = 0.01
+    network_newton_fq.addNode("node1", rho)
+    network_newton_fq.addNode("node2", rho)
+    network_newton_fq.addNode("node3", rho)
+    network_newton_fq.addNode("node4", rho)
+    network_newton_fq.addNode("node5", rho)
 
     # node 1 sends to node 2 and 3
-    network_newton_fq.setConnection("node1", ["node2"])
+    network_newton_fq.setConnection("node1", ["node2", "node3"])
     network_newton_fq.setConnection("node2", ["node3"])
[…]

### 2022-04-14 python/plot_data.py
plots

@@ -262,7 +262,7 @@ fig = plt.figure(figsize=(5, 3))
 plt.plot(SNRs, -np.asarray(SNRs), "k--", label="SNR")
 plt.plot(SNRs, 20 * np.log10(err_MCQN_avg), marker="o", label="MCQN")
 plt.plot(SNRs, 20 * np.log10(err_NMCFLMS_avg), marker=">", label="NMCFLMS")
-plt.plot(SNRs, 20 * np.log10(err_RNMCFLMS_avg), marker="o", label="RNMCFLMS")
+# plt.plot(SNRs, 20 * np.log10(err_RNMCFLMS_avg), marker="o", label="RNMCFLMS")
 plt.plot(SNRs, 20 * np.log10(err_LPRNMCFLMS_avg), marker="^", label="LPRNMCFLMS")
 plt.plot(SNRs, 20 * np.log10(err_ADMM_newton_td_avg), marker="v", label="ADMM")
 plt.plot(SNRs, 20 * np.log10(err_ADMM_newton_fq_avg), marker="o", label="ADMM FQ")

### 2022-04-18 generate_irs/generate_irs.py
stuffy wuffy

@@ -1,0 +1,73 @@
+# %%
+import numpy as np
+import matplotlib.pyplot as plt
+import rim
+
+# %%
+xs = [1, 1, 1]
+# xr = np.random.uniform(0, 2, size=(6, 3))
+xr = [
+    [0.92781265, 1.13393288, 0.26736836],
+    [1.43182171, 1.56376992, 1.59195482],
+    [1.93766398, 0.46898242, 0.1320927],
+    [0.47049847, 1.36370444, 0.56008512],
+    [0.18023421, 0.99715069, 1.75508388],
+    [0.33782243, 0.99060236, 1.48623386],
+]
+Nt = 256
+L = [2, 2, 2]
+beta = [0.6, 0.6, 0.6, 0.6, 0.6, 0.6]
+Fs = 8000
+N = [20, 20, 20]
+xr_dirs = [[1, 0, 0], [1, 0, 0], [0, 1, 0], [1, 0, 0], [1, 0, 0], [0, 1, 0]]
+xr_types = ["o", "o", "o", "o", "o", "o"]
+
+h_gen, seed = rim.rim(
+    xs,
+    xr,
+    Nt,
+    L,
+    beta,
+    Fs,
+    Rd=0.0,
+    N=N,
+    Tw=20,
+    Fc=0.9,
+    MicDirs=xr_dirs,
+    MicTypes=xr_types,
+)
+
+# %%
+L = 128
+fig, axes = plt.subplots(h_gen.shape[1], 1, figsize=(8, 10))
+h_gen /= np.max(h_gen)
+h = np.zeros((L * 6,))
+for i, row in enumerate(axes):
+    h_ = h_gen[:, i]
+    h_ /= np.max(h_)
+    start = np.argmax(h_ == 1)
+    h[i * L : (i + 1) * L] = h_[start : start + L]
+    row.plot(h_[start : start + L])
+    row.set_ylabel("Amplitude [1]")
+    row.set_xlabel("Samples [1]")
+    row.spines["right"].set_visible(False)
+    row.spines["top"].set_visible(False)
+    row.set_ylim((-1, 1))
+    row.grid()
+plt.tight_layout()
+plt.show()
+
+# %%
+fig, axes = plt.subplots(1, 1, figsize=(8, 3))
+for i in range(6):
+    x = np.arange(i * L, (i + 1) * L)
+    plt.plot(x, h[i * L : (i + 1) * L])
[…]

### 2022-04-18 python/simulation_rim.py
random and rimjobs

@@ -13,9 +13,9 @@ import matplotlib.pyplot as plt
 # %%
 process_id = int(sys.argv[1])
 SNR = int(sys.argv[2])
-N_sens = int(sys.argv[3])
-L = int(sys.argv[4])
-print("Job: %d, SNR: %d, N_sens: %d, L: %d" % (process_id, SNR, N_sens, L))
+N_sens = 6
+L = 128
+print("Job: %d, SNR: %d, N_sens: %d, L: %f" % (process_id, SNR, N_sens, L))
 
 # %%
 runs = 50
@@ -27,7 +27,7 @@ N_f = 1024
 # N_sens = 3
 
 # %%
-N_s = 20000
+N_s = 16000
 
 # %%
 seed = 12345
@@ -35,34 +35,28 @@ rng = np.random.RandomState()
 rng.seed(seed)
 
 # %%
+with open("../generate_irs/h.npy", "rb") as f:
+    h = np.load(f)
+# %%
 for run in range(runs):
-    if os.path.isfile("data/simulation_random/%d_%d.npy" % (process_id, run)):
+    if os.path.isfile("data/simulation_rim/%d_%d.npy" % (process_id, run)):
         print("run %d is already there" % (run))
         continue
-    # %%
-    h = np.array([]).reshape(0, 1)
-    h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
-    for n in range(N_sens):
-        h_ = rng.normal(size=(L, 1))
-        h_ = h_ / np.linalg.norm(h_)
-        w, hh = signal.freqz(h_, worN=N_f)
-        h_f[n, :] = hh
-        h = np.concatenate([h, h_])
+
+    # # %%
+    # if plot:
+    #     fig, ax1 = plt.subplots()
+    #     ax1.set_title("Digital filter frequency response")
+    #     for n in range(N_sens):
+    #         ax1.plot(w, 20 * np.log10(abs(h_f[n, :])))
+    #     ax1.set_ylabel("Amplitude [dB]")
+    #     ax1.set_xlabel("Frequency [rad/sample]")
+    #     ax1.grid()
+    #     plt.show()
 
     # %%
     if plot:
-        fig, ax1 = plt.subplots()
-        ax1.set_title("Digital filter frequency response")
-        for n in range(N_sens):
-            ax1.plot(w, 20 * np.log10(abs(h_f[n, :])))
-        ax1.set_ylabel("Amplitude [dB]")
-        ax1.set_xlabel("Frequency [rad/sample]")
[…]

### 2022-04-21 python/simulation_random.py
final random sim hopefully

@@ -18,7 +18,7 @@ L = int(sys.argv[4])
 print("Job: %d, SNR: %d, N_sens: %d, L: %d" % (process_id, SNR, N_sens, L))
 
 # %%
-runs = 50
+runs = 30
 plot = False
 
 # %%
@@ -27,7 +27,7 @@ N_f = 1024
 # N_sens = 3
 
 # %%
-N_s = 20000
+N_s = 8000 * 100
 
 # %%
 seed = 12345
@@ -92,7 +92,8 @@ for run in range(runs):
         network_newton_fq.setConnection(name, connections)
         network_newton_fq_diag.setConnection(name, connections)
 
-    # %% GENERATE AR SIGNAL
+    # %%
+    # GENERATE AR SIGNAL
     N_ff = 1025
     b1 = signal.firwin(N_ff, 0.25, pass_zero=False)
     M = 20
@@ -124,9 +125,10 @@ for run in range(runs):
         x[k, :, None] = H @ s_[k : k + L][::-1] + n_var * rng.normal(size=(N_sens, 1))
 
     # %%
-    hopsize = 1
+    hopsize = L
 
-    # %% CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD
+    # %%
+    # CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD
     print("CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD")
     err_MCQN = []
     rho = 0.5  # step size
@@ -141,7 +143,8 @@ for run in range(runs):
         err_MCQN.append(bsi_mcqn.get_error(h))
     err_MCQN = np.asarray(err_MCQN)
 
-    # %% CENTRALIZED NORMALIZED FREQUENCY DOMAIN LMS METHOD
+    # %%
+    # CENTRALIZED NORMALIZED FREQUENCY DOMAIN LMS METHOD
     print("CENTRALIZED NORMALIZED FREQUENCY DOMAIN LMS METHOD")
     err_NMCFLMS = []
     rho = 0.4  # step size
@@ -153,7 +156,8 @@ for run in range(runs):
         err_NMCFLMS.append(bsi_nmcflms.get_error(h))
     err_NMCFLMS = np.asarray(err_NMCFLMS)
 
-    # %% CENTRALIZED ROBUST NORMALIZED FREQUENCY DOMAIN LMS METHOD
+    # %%
[…]

### 2022-04-21 python/admm_newton_fq.py
stuffy

@@ -282,7 +282,7 @@ class Network:
             #     return
             x_avg[node.global_indices] += node.x * self.g[node.global_indices]
             y_avg[node.global_indices] += node.y * self.g[node.global_indices]
-        pp = node.rho * x_avg + y_avg  # WHAT DO WITH RHO IF NOT SAME FOR ALL
+        pp = x_avg + 1 / node.rho * y_avg  # WHAT DO WITH RHO IF NOT SAME FOR ALL
         self.z = pp / (np.linalg.norm(pp)) * self.L / self.N
         pass
 

### 2022-04-21 python/admm_newton_fq_diag.py

@@ -287,7 +287,7 @@ class Network:
             #     return
             x_avg[node.global_indices] += node.x * self.g[node.global_indices]
             y_avg[node.global_indices] += node.y * self.g[node.global_indices]
-        pp = node.rho * x_avg + y_avg  # WHAT DO WITH RHO IF NOT SAME FOR ALL
+        pp = x_avg + 1 / node.rho * y_avg  # WHAT DO WITH RHO IF NOT SAME FOR ALL
         self.z = pp / (np.linalg.norm(pp)) * self.L / self.N
         pass
 

### 2022-04-21 python/plot_data.py
connectivity sim and plots

@@ -14,7 +14,7 @@ class SimulationData:
     variable_range: list
 
 
-# %%
+# %% random IRS
 SNRs = [5, 10, 15, 20, 30, 40, 50]
 id = 0
 runs_ = []
@@ -38,10 +38,12 @@ for SNR in SNRs:
     err_ADMM_newton_td_[SNR] = None
     err_ADMM_newton_fq_[SNR] = None
     err_ADMM_newton_fq_diag_[SNR] = None
-dir = "data/"
-files = sorted(os.listdir(dir))
 
-# %%
+L_p = 64
+N_p = 5
+
+dir = "data/simulation_random/"
+files = sorted(os.listdir(dir))
 for filename in files:
     print(filename)
     with open(dir + filename, "rb") as f:
@@ -58,6 +60,9 @@ for filename in files:
         err_ADMM_newton_td = np.load(f)
         err_ADMM_newton_fq = np.load(f)
         err_ADMM_newton_fq_diag = np.load(f)
+
+        if L != L_p or N_sens != N_p:
+            continue
 
         if not np.isnan(err_MCQN).any():
             err_MCQN_[SNR] = (
@@ -112,32 +117,39 @@ for filename in files:
     id += 1
 # %%
 for SNR in SNRs:
-    if err_MCQN_[SNR] is None:
-        continue
     fig = plt.figure(figsize=(8, 6))
-    plt.plot(20 * np.log10(np.nanmedian(err_MCQN_[SNR], axis=0)[:-L]), label="MCQN")
-    plt.plot(
-        20 * np.log10(np.nanmedian(err_NMCFLMS_[SNR], axis=0)[:-L]), label="NMCFLMS"
-    )
-    plt.plot(
-        20 * np.log10(np.nanmedian(err_RNMCFLMS_[SNR], axis=0)[:-L]), label="RNMCFLMS"
-    )
-    plt.plot(
-        20 * np.log10(np.nanmedian(err_LPRNMCFLMS_[SNR], axis=0)[:-L]),
-        label="LPRNMCFLMS",
-    )
-    plt.plot(
-        20 * np.log10(np.nanmedian(err_ADMM_newton_td_[SNR], axis=0)[:-L]),
-        label="ADMM",
-    )
-    plt.plot(
-        20 * np.log10(np.nanmedian(err_ADMM_newton_fq_[SNR], axis=0)[:-L]),
-        label="ADMM FQ",
-    )
[…]

### 2022-04-21 python/simulation_random_connectivity.py

@@ -18,7 +18,7 @@ density = float(sys.argv[4])
 print("Job: %d, SNR: %d, N_sens: %d, density: %f" % (process_id, SNR, N_sens, density))
 
 # %%
-runs = 50
+runs = 30
 seed = 12345
 plot = False
 
@@ -35,7 +35,9 @@ rng.seed(seed)
 
 # %%
 for run in range(runs):
-    if os.path.isfile("data/%d_%d.npy" % (process_id, run)):
+    if os.path.isfile(
+        "data/simulation_random_connectivity/%d_%d.npy" % (process_id, run)
+    ):
         print("run %d is already there" % (run))
         continue
     # %%
@@ -67,10 +69,7 @@ for run in range(runs):
 
     # %%
     # connectivity: ring + random inbetween ones
-    G = utils.generateConnectionMatrix(N_sens, density, rng)
-    offdiag = np.arange(N_sens - 1)
-    G[offdiag, offdiag + 1] = 1  # setting the directed ring as base
-    np.fill_diagonal(G, 0)
+    G = utils.generateRandomConnectionMatrixWithRing(N_sens, density, rng)
 
     network_td = admm.Network(L)
     network_newton_fq = sb_newton_fq.Network(L)
@@ -82,48 +81,18 @@ for run in range(runs):
         network_td.addNode(name, rho)
         network_newton_fq.addNode(name, rho)
         network_newton_fq_diag.addNode(name, rho)
+    for n in range(N_sens):
+        name = "node%d" % (n)
+        connections = []
+        for j in range(N_sens):
+            name1 = "node%d" % (j)
+            if G[n, j] > 0:
+                connections.append(name1)
+        network_td.setConnection(name, connections)
+        network_newton_fq.setConnection(name, connections)
+        network_newton_fq_diag.setConnection(name, connections)
 
-    network_td.addNode("node2", rho)
-    network_td.addNode("node3", rho)
-    network_td.addNode("node4", rho)
-    network_td.addNode("node5", rho)
-
-    # node 1 sends to node 2 and 3
-    network_td.setConnection("node1", ["node2", "node3"])
-    network_td.setConnection("node2", ["node3"])
-    network_td.setConnection("node3", ["node4"])
-    network_td.setConnection("node4", ["node5"])
-    network_td.setConnection("node5", ["node1"])
-    network_td.setBufferSize(1)
-
-    rho = 0.01
[…]

### 2022-04-21 python/plot_data.py
connectivity sim and plots

@@ -320,7 +320,7 @@ plt.show()
 # %%
 lim = 2500
 for N_sens in [4, 8]:
-    fig = plt.figure(figsize=(3, 3))
+    fig = plt.figure(figsize=(3, 2.5))
     for i in range(len(densities)):
         if err_ADMM_newton_fq_diag_[i][N_sens] is not None:
             plt.plot(
@@ -336,7 +336,8 @@ for N_sens in [4, 8]:
     plt.xlim(0, lim)
     plt.ylim(-40, 0)
     plt.grid()
-    plt.legend()
+    if N_sens == 8:
+        plt.legend()
     plt.tight_layout()
     plt.show()
     utils.savefig(fig, "NPM_over_time_M%d" % (N_sens))

### 2022-04-21 tikz/problem_splitting.tex
almost finished

% Tikz File 'topology_general.tex'
\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz,amsmath,amssymb}
\usetikzlibrary{arrows,snakes,backgrounds}
    \begin{document}
    \begin{tikzpicture}[->,shorten >=1pt,auto,semithick]
        \tikzstyle{admmnode}=[
            circle,
            draw=black,
            thick,
            fill=gray,
            text=black
        ]

        \node[admmnode, fill=OliveGreen!40] (A) at (0,1.5){\(1\)};
        \node[admmnode, fill=MidnightBlue!40] (B) at (1.5,0){\(2\)};
        \node[admmnode, fill=BurntOrange!40] (C) at (0,-1.5){\(3\)};
        \node[admmnode, fill=Maroon!40] (D) at (-1.299038105676658,-0.75){\(4\)};
        \node[admmnode, fill=SkyBlue!40] (E) at (-1.299038105676658,0.75){\(5\)};

        \draw[-stealth, line width=1.25] (A) to[bend left=20] node[]{}  (B);
        \draw[-stealth, line width=1.25] (A) to[bend left=0] node[]{} (C);
        \draw[-stealth, line width=1.25] (B) to[bend left=20] node[]{} (C);
        \draw[-stealth, line width=1.25] (C) to[bend left=10] node[]{} (D);
        \draw[-stealth, line width=1.25] (D) to[bend left=10] node[]{} (E);
        \draw[-stealth, line width=1.25] (E) to[bend left=10] node[]{} (A);

    \end{tikzpicture}
\end{document}

### 2022-04-22 python/plot_data.py
experiments 1 plots

@@ -192,32 +192,63 @@ for SNR in SNRs:
     )
 
 # %%
-fig = plt.figure(figsize=(5, 3))
+fig = plt.figure(figsize=(3, 2.5))
 # plt.plot(SNRs, -np.asarray(SNRs), "k--", label="SNR")
 plt.plot(SNRs, 20 * np.log10(err_MCQN_avg), marker="o", label="MCQN")
 plt.plot(SNRs, 20 * np.log10(err_NMCFLMS_avg), marker=">", label="NMCFLMS")
-plt.plot(SNRs, 20 * np.log10(err_RNMCFLMS_avg), marker="o", label="RNMCFLMS")
-plt.plot(SNRs, 20 * np.log10(err_LPRNMCFLMS_avg), marker="^", label="LPRNMCFLMS")
+# plt.plot(SNRs, 20 * np.log10(err_RNMCFLMS_avg), marker="o", label="RNMCFLMS")
+plt.plot(SNRs, 20 * np.log10(err_LPRNMCFLMS_avg), marker="^", label=r"$l_p$-RNMCFLMS")
 # plt.plot(SNRs, 20 * np.log10(err_ADMM_newton_td_avg), marker="v", label="ADMM")
 # plt.plot(SNRs, 20 * np.log10(err_ADMM_newton_fq_avg), marker="o", label="ADMM FQ")
 plt.plot(
     SNRs,
     20 * np.log10(err_ADMM_newton_fq_diag_avg),
     marker="s",
-    label="ADMM FQ DIAG",
+    label="ADMM BSI",
 )
 # plt.title("Median misalignment after 8000 Samples")
 plt.xlabel("SNR [dB]")
 plt.ylabel("Average NPM [dB]")
 plt.xticks(SNRs)
-# plt.yticks(-SNRs)
+plt.xlim(3,52)
+plt.ylim(-85,-10)
+# plt.yticks(-np.asarray(SNRs))
 plt.grid()
-plt.legend(fontsize="small", ncol=2)
+plt.legend(fontsize="small")
 plt.tight_layout()
 plt.show()
 
 # %%
 utils.savefig(fig, "NPM_over_SNR_L%d_M%d" % (L_p, N_p))
+
+# %%
+fig = plt.figure(figsize=(3, 2.5))
+SNR = 10
+if err_MCQN_[SNR] is not None:
[…]

### 2022-04-27 paper.tex
minor grammar changes

@@
 \input{preamble.tex}
+
+% \excludecomment{note}
+% \excludecomment{attention}
+
+% Common variables
+\newcommand{\h}{\mtxb{h}}
+\newcommand{\x}{\mtxb{x}}
+\newcommand{\R}{\mtxb{R}}
+\newcommand{\w}{\mtxb{w}}
+\newcommand{\z}{\mtxb{z}}
+\newcommand{\uu}{\mtxb{u}}
+\newcommand{\aRho}{\mtxb{P}}
+\newcommand{\hf}{{\bm{h}}}
+\newcommand{\xf}{{\bm{x}}}
+\newcommand{\Rf}{{\bm{{R}}}}
+\newcommand{\wf}{{\bm{w}}}
+\newcommand{\zf}{{\bm{z}}}
+\newcommand{\uuf}{{\bm{u}}}
+\newcommand{\aRhof}{{\bm{{P}}}}
+\newcommand{\I}{\mtxb{I}}
+\newcommand{\Cset}{\mathcal{C}}
+\newcommand{\Csetb}{\bar{\mathcal{C}}}
+\newcommand{\Mset}{\mathcal{M}}
+\newcommand{\Nset}{\mathcal{N}}
 
@@
 % ------
-\title{CROSS-RELATION BASED BLIND SYSTEM IDENTIFICATION USING ADMM}
+\title{CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE ADMM}
 %
@@
 % ---------------
-\name{Matthias Blochberger\sthanks{THANK EU!}, Filip Elvander\sthanks{THANK FWO?}, Randall Ali, Toon van Waterschoot}
-\address{KU Leuven\\ESAT - Department of Electrical Engineering\\STADIUS\\3001 Leuven}
-%
-% For example:
-% ------------
-%\address{School\\
-%	Department\\
-%	Address}
-%
-% Two addresses (uncomment and modify for two-address case).
-% ----------------------------------------------------------
-%\twoauthors
-%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
-%	{School A-B\\
-%	Department A-B\\
-%	Address A-B}
-%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
-%	while at ...}}
-%	{School C-D\\
-%	Department C-D\\
-%	Address C-D}
+\name{Matthias Blochberger\sthanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.
+956369.}, Filip Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, Randall Ali, Toon van Waterschoot, Marc Moonen}
+\address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
 %
@@
 \begin{abstract}
-The abstract should appear at the top of the left-hand column of text, about 0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in length.
-Leave a 0.5 inch (12 mm) space between the end of the abstract and the beginning of the main text.
-The abstract should contain about 100 to 150 words, and should be identical to the abstract text submitted electronically.
-All manuscripts must be in English.
+    In this contribution, we propose a cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM).
+    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into lower-dimensional sub-problems with reduced computational complexity, which can be solved in parallel.
+    Each sub-problem yields estimates for a subset of channel frequency responses, which then are combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
+    With numerical simulations, we show that it is possible to achieve convergence speeds comparable to low-cost frequency-domain algorithms and estimation errors better than a high-performing Quasi-Newton algorithm.
 \end{abstract}
@@
 \begin{keywords}
-One, two, three, four, five
+    blind system identification, multichannel signal processing, ADMM, Online-ADMM
 \end{keywords}
@@
 
-These guidelines include complete descriptions of the fonts, spacing, and related information for producing your proceedings manuscripts.
-If you have any questions regarding the paper submission, please contact the conference organizers via email: \texttt{submission@iwaenc2022.org}\,.
+The problem of blind system identification (BSI), which aims to estimate channel impulse responses of an unknown system without knowing the input signal, has been the subject of extensive research over recent decades.
+It was introduced in \cite{satoMethodSelfRecoveringEqualization1975} and various algorithms have been proposed since.
+Early algorithms used higher-order statistics \cite{godardSelfRecoveringEqualizationCarrier1980,tongNewApproachBlind1991,mecidel1991tutorial} for channel estimation, however a high computational complexity has motivated research into algorithms using only second-order statistics.
+Suh algorithms include the cross-relation (CR) algorithm \cite{tong1994blind, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
 
+Out of various multichannel BSI algorithms which have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.
+The normalized multi-channel frequency-domain LMS (NMCFLMS) \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} algorithm for instance is an efficient algorithm utilizing the fast Fourier transform (FFT) which has been extended to include constraints to improve robustness to noise and performance on acoustic impulse responses (RNMCFLMS \cite{huNoiseRobustBlind2015}, \(l_p\)-RNMCFLMS \cite{heNoiseRobustFrequencyDomain2018}, phase-constrained-\(l_p\)-RNMCFLMS \cite{joRobustBlindMultichannel2021}).
+The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the BFGS method to estimate the Hessian of the problem.
+
+The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves convex optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
+In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
+The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
+
+The resulting algorithm provides good estimation results while keeping the computational complexity low and providing scalability through distributed processing possibilities.
+
+% #############################################################################
+% #############################################################################
 \section{Problem statement}
@@
 
-\section{Distributed BSI}
-\label{sec:admm_bsi}
+% #############################################################################
+\subsection{Signal Model}
+\label{ssec:signal_model}
+We consider an acoustic SIMO system with the input signal \(\mtxb{s}(n)\) and \(i \in \Mset\) with \(\Mset \triangleq \{1,\ldots,M\} \) outputs \(\x_i(n)\) defined as
+\begin{align}
+    \mtxb{s}(n) &= \begin{bmatrix}
+        s(n)&s(n-1)&\ldots&s(n-2L+2)
+    \end{bmatrix}^{\T}\\
+    \x_i(n) &= \begin{bmatrix}
+        x_i(n)&x_i(n-1)&\ldots&x_i(n-L+1)
+    \end{bmatrix}^{\T}.
+\end{align}
+Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated.
+The signal model is described by
+\begin{equation}
+    \x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n),
+\end{equation}
+where \(\mtxb{H}_i\) is the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) which represents the system to be identified.
 
-\subsection{ADMM?}
-\label{ssec:admm}
+% #############################################################################
+\subsection{Cross-relation approach}
+\label{ssec:cross_rel}
+The cross-relation approach for BSI aims to use only the output signals of the system to identify it.
+This can be achieved by exploiting the relative channel information when more than one channel is available, and the identifiability conditions \cite{guanghanxuLeastsquaresApproachBlind1995} are satisfied.
+These conditions are: (i) the channel transfer functions have no common zeros (i.e.
+are not co-prime), and (ii) the covariance matrix of the input signal \(\mtxb{s}(n)\) is of full rank (i.e.
+the signal fully excites the channels).
 
+The fundamental equality of this approach in the noiseless case \(\mtxb{v}_i(n) = 0\), is 
+\begin{equation}
+    \x_i^{\T}(n) \h_j = \x_j^{\T}(n) \h_i,\quad i,j \in \Mset,\,i\neq j\label{eq:cross_rel:equality_conv}
+\end{equation}
+which states that the channel output signal convolved with the impulse response of another is equal to the vice-versa as follows from the commutativity property of the convolution.
+Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij} = \ev{\x_i \x_j^\T}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g.
+\cite{huangAdaptiveMultichannelLeast2002} for a more thourough derivation) yields the system of equations
+\begin{equation}
+    \R(n) \h = \bm{0}, \label{eq:cross_rel:null_space}\\
+\end{equation}
+where \(\R\) is an \(M L \times M L\) matrix given by:
+\begin{equation}
+    \R = \begin{bmatrix}
+        \sum_{i \neq 1} \R_{ii} & -\R_{21} & \cdots & -\R_{M1}\\
+        -\R_{12} & \sum_{i \neq 2} \R_{ii} & \cdots & -\R_{M2}\\
+        \vdots & \vdots & \ddots & \vdots\\
+        -\R_{1M} & -\R_{2M} & \cdots & \sum_{i \neq M} \R_{ii}\\
+    \end{bmatrix},\label{eq:cross_rel:data_matrix}
+\end{equation}
+and \(\h = \begin{bmatrix}
+    \h_1^\T & \cdots & \h_M^\T
+\end{bmatrix}^\T\).
+Formulating the problem in the frequency domain, the derivation is analogous.
+We denote all frequency-domain variables in bold cursive (e.g.
+\(\Rf\)) compared to the time-domain bold upright (e.g \(\R\)).
+The derivation involves the frame-based overlap-save technique, working with signal frames \(\x_{i,2L}(m)\) of length \(2L\), frame index \(m\), leading to the system of equations
+\begin{equation}
+    \Rf(m) \hf = \bm{0} \label{eq:frequency_domain:null_space}\\
+\end{equation}
+where the \(M L \times M L\) matrix is recursivly computed by \begin{equation}
+    \Rf(m) = \eta \Rf(m-1) + (1-\eta )\hat{\Rf}(m)
+\end{equation}
+instead of estimating the expectation by sample averages.
+Here, \(\eta \in [0,1]\) is an exponential smoothing factor and \(\hat{\Rf}(m)\) is constructed analogous to \eqref{eq:cross_rel:data_matrix}, however with covariance matrices replaced by cross-spectrum matrices
+\begin{equation}
+    \Rf_{ij}(m) = \bm{{S}}_{i}^\herm (m) \bm{{S}}_{j}(m),
+\end{equation}
+with 
+\begin{equation}
+    \bm{{S}}_{i}(m) = \bm{{W}}^{01}_{L \times 2L} \bm{{D}}_{i}(m) \bm{{W}}^{10}_{2L \times L}.
+\end{equation}
+The matrix \(\bm{{D}}_{i}(m) = \operatorname{diag} \left\{ \operatorname{FFT}_{2L} \left\{ \x_{i,2L}(m) \right\} \right\}\) contains the  signal spectrum on its diagonal and the overlap-save matrices are defined as
+\begin{align}
+    \mtxb{W}_{L \times 2L}^{01} &= \begin{bmatrix}
+        \mtxb{0}_{L \times L} & \mtxb{I}_{L \times L}
+    \end{bmatrix},\\
+    \mtxb{W}_{2L \times L}^{10} &= \begin{bmatrix}
+        \mtxb{I}_{L \times L} & \mtxb{0}_{L \times L}
+    \end{bmatrix}^\T,\\
+    \bm{{W}}_{L \times 2L}^{01} &= \mtxb{F}_{L \times L} \mtxb{W}_{L \times 2L}^{01} \mtxb{F}_{2L \times 2L}^{-1},\\
+    \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1},
+\end{align} where $\mtxb{F}$ is the DFT matrix for sizes L and 2L.
+Analogous to the time-domain formulation, the vector \(\hf\) is a stacked vector of complex-valued frequency responses.
+In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem.
+%  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
+% As this effectively seeks the \(a\)-scaled eigenvector of the squared hermitian matrix \(\Rf^\herm \Rf\) corresponding to the smallest eigenvalue, we can replace it with its non-squared form \(\Rf\) as the eigenvectors for both are equal.
+To compute the estimates, we minimize the cost function
+\begin{equation}
+    J(\hf)(m+1) = \hf^\herm(m) \Rf(m) \hf(m),\label{eq:frequency_domain:cost_function}
+\end{equation}
+as the minimization problem
+\begin{align}
+    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \Rf(m) \hf(m), \label{eq:frequency_domain:min_prob}\\
+    \text{s.t. } \quad &\hf^\herm(m) \hf(m) = a.
+\end{align}
+In the following section, we introduce a novel adaptive algorithm to find a solution to this problem.
+
+% #############################################################################
+% #############################################################################
+\section{Proposed Algorithm}
+\label{sec:proposed_method}
+
+% #############################################################################
+\subsection{Problem Splitting}
+\label{ssec:problem_splitting}
+In state-of-the-art algorithms \cite{heNoiseRobustFrequencyDomain2018,habetsOnlineQuasiNewtonAlgorithm2010}, the minimization problem \eqref{eq:frequency_domain:min_prob} is solved in its full form resulting in potentially high computational effort when the number of channels and length of impulse responses or number of DFT bins is large.
+Here however, we split the problem into \(N \in \mathbb{N}\) sub-problems and denote the index set of these \(N\) sub-problems as \(\Nset \triangleq \{1,\ldots,N\}\).
+Each sub-problem is defined by a subset of the full channel set \(\Cset_i \subseteq \Mset\) with \(i \in \Nset\).
+Following from that, we define the sets \(\Csetb_j = \left\{ i \vert j \in \Cset_i \right\}\) for \(i,j \in \Mset\) which is the set of sub-problems a channel  \(j\) is part of.
+This channel-to-sub-problem relation can also be expressed as a \(M \times P\) matrix \(\mtxb{G}\) where the sets \(\Cset_i\) and \(\Csetb_j\) are the indices of non-zero elements of the rows and columns respectively (see \autoref{fig:problem_splitting:problem_splitting_matrix}).
+Further, \(M_i = \left| \Cset_i \right| \) and \(N_j = \left| \Csetb_j \right| \) with \(i,j \in \Mset\). 
+We replace the cost function \eqref{eq:frequency_domain:cost_function} with the separable cost function 
+\begin{equation}
+    \tilde{J}(\hf) = \sum_{i \in \Nset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Nset} \wf_i^\T \aRhof_i \wf_i
+    \label{eq:problem_splitting:cost_function}
+\end{equation}
+where \(\wf_i\) is defined as the stacked vector of estimated frequency responses analogous to \(\hf\) (cf.
+\autoref{ssec:cross_rel}) and \(\aRhof\) is constructed as defined in \eqref{eq:cross_rel:data_matrix}, both using the respective subset \(\Cset_i\).
+If the channel subsets are proper \(\Cset_i \subset \Mset\), this leads to \(N\) sub-problems, each with smaller dimensions than the original centralized problem, reducing complexity.
+The lowest-dimensionality is attained when each \(\Cset_i\) has two elements, i.e. two channels, with parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
+In \autoref{fig:problem_splitting:problem_splitting_matrix}, we try to visualize which information is used to solve the sub-problems compared to the initial problem for a general case.
+
+\begin{figure}
+    \centering
+    \subfloat[][]{\includegraphics[trim={1.8cm 0 1.7cm 0},clip,scale=0.7]{images/parameter_mapping.pdf}}
+    \subfloat[][]{\includestandalone[trim={0.65cm 0 0 0},clip,scale=0.7]{tikz/connection_matrix}}
+    \subfloat[][]{\includestandalone[trim={0.6cm 0 0 0},clip,scale=0.6]{tikz/problem_splitting_matrix}}
+    % \includestandalone[scale=1]{tikz/topology_general}
+    \vspace*{-0.3cm}
+    \caption{Problem splitting and parameter mapping for a general case with \(M=5\) channels and \(N=4\) sub-problems.
+(a) shows the mapping of the local estimate components \((\wf_i)_j\) to the global consensus components \((\hf)_j\) via \(\mathcal{G}(i,j)\), (b) \(\mtxb{G}\) with 1 (\(\blacksquare\)) and 0 (\(\square\)), (c) shows \(i,j\)-cross-relations used by sub-problems compared to full \(M\)-channel problem.}
+    \label{fig:problem_splitting:problem_splitting_matrix}
+\end{figure}
+
+% #############################################################################
+\subsection{General-Form Consensus ADMM}
+\label{ssec:general_consensus_admm}
+Minimization problems with separable const functions can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}.
+In the previous section we introduced the split cost function \eqref{eq:problem_splitting:cost_function} which we now set in the context of the general-form consensus problem
+\begin{align}
+    \operatorname{minimize} \quad &\sum_{i \in \Nset} \tilde{J}_i(\wf_i)\\
+    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Nset,\,j \in \Cset_i
+\end{align}
+where \(\mathcal{G}(i,j)=g\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
+one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\) (cf.
+\autoref{fig:problem_splitting:problem_splitting_matrix}).
+For brevity, the mapped global variables \((\tilde{\hf}_i)_j = \hf_{\mathcal{G}(i,j)}\) are introduced.
+The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces the consensus, i.e. a common solution taking into account data of all sub-problems.
+
+The augmented Lagrangian for this particular general-form consensus problem is
+% \begin{equation}
+%     \mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Mset} \left( \wf_i^\herm \aRhof_i \wf_i + 2 \Re \left\{ \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right\} + \rho \left\| \wf_i - \tilde{\hf}_i \right\|\label{eq:general_consensus_admm:lagrangian}
+% \end{equation}
+\begin{align}
+    &\mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Mset} \left( \wf_i^\herm \aRhof_i \wf_i + \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right)\vphantom{+ \frac{\rho}{2} \left\| \wf_i - \tilde{\hf}_i \right\|^2} \right.\nonumber\\
+    &\left.
++ \left(\wf_i - \tilde{\hf}_i\right)^\herm \uuf_i + \left( \wf_i - \tilde{\hf}_i \right)^\herm \rho \I \left( \wf_i - \tilde{\hf}_i \right) \right).\label{eq:general_consensus_admm:lagrangian}
+\end{align}
+The ADMM then consists of the steps:
+\begin{align}
+    \wf_i^{k+1} &= \underset{\wf_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\wf,\hf^k,\uuf^k),\label{eq:general_consensus_admm:local}\\
+    \hf^{k+1} &= \underset{\hf, \|\hf\| = a}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\wf^{k+1},\hf,\uuf^k)\label{eq:general_consensus_admm:global}\\
+    \uuf_i^{k+1} &= \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right).\label{eq:general_consensus_admm:dual}
+\end{align}
+% \begin{align}
+%     &\wf_i^{k+1} = \underset{\wf_i}{\operatorname{argmin}} \left\{ \wf_i^\herm \aRhof_i \wf_i + \uuf_i^{k\,\herm} \left(\wf_i - \tilde{\hf}_i^{k}\right) \vphantom{+ \left\| \wf_i - \tilde{\hf}_i^{k} \right\|^2}\right.\nonumber\\
+%     &\left.+ \left(\wf_i - \tilde{\hf}_i^{k}\right)^\herm \uuf_i^{k} + \left( \wf_i - \tilde{\hf}_i^{k} \right)^\herm \rho \I \left( \wf_i - \tilde{\hf}_i^{k} \right) \right\},\label{eq:general_consensus_admm:local}\\
+%     &\hf^{k+1} = \underset{\hf, \|\hf\| = a}{\operatorname{argmin}} \left\{ \sum_{i \in \Mset} \left( \tilde{\hf}_i^{\herm} \uuf_i^{k} + \uuf_i^{k\,\herm} \tilde{\hf}_i \vphantom{\frac{\rho}{2} \| \wf_i^{k+1} - \tilde{\hf}_i \|^2} \right.\right.\nonumber\\
+%     &\left.
+\qquad \qquad \vphantom{\sum_{i=1}^{M} pp } \left.+ \left( \wf_i^{k+1} - \tilde{\hf}_i \right)^\herm \rho \I \left( \wf_i^{k+1} - \tilde{\hf}_i \right)  \right) \right\},\label{eq:general_consensus_admm:global}\\
+%     &\uuf_i^{k+1} = \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right).\label{eq:general_consensus_admm:dual}
+% \end{align}
+As this is still denoted as an iterative algorithm, we will introduce the online/adaptive aspect of the proposed one next.
+
+\subsection{Online ADMM-BSI}
+\label{ssec:online_admm}
+We introduced the original problem \eqref{eq:frequency_domain:null_space} with time-dependent data matrix.
+Following from this, also the data term in \eqref{eq:general_consensus_admm:lagrangian} is time-dependent, which from here on out will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \aRhof_i^{m} \wf_i\).
+A thorough look at time-varying data terms in ADMM can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as "Online-ADMM".
+
+We transform the iterative batch processing method \eqref{eq:general_consensus_admm:local}-\eqref{eq:general_consensus_admm:dual} into an adaptive one by computing only a (small) finite number of iterations with each time-frame-\(m\) specific data term.
+Here specifically, we apply one iteration per time frame, which manifests itself as simply replacing the iteration index \(k\) with the time index \(m\)
+
+The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform a Newton update step
+\begin{equation}
+    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \aRhof_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right)\label{eq:online_admm:local_update}
+\end{equation}
+where \(0  < \mu\leq 1\) is a step size and \(\bm{{V}}_i^m = \left(\aRhof_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
+As this inverse is costly to compute, it is approximated by a diagonalized matrix
+\begin{equation}
+    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \left( \operatorname{diag} \left\{ \aRhof_i^m \right\} + \rho \mtxb{1} \right)^{-1}\right\},
+\end{equation}
+similar to NMCFLMS \cite{huangClassFrequencydomainAdaptive2003}, which is straightforward to compute.
+
+For the update step of the consensus variable \(\hf\), it may be readily verified (cf.
+\cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by
+\begin{equation}
+    \hf^{m+1} = a\frac{\bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} }{\left\| \bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} \right\|}.\label{eq:online_admm:consensus_update}
+\end{equation}
+where the \(M L \times 1\) vectors \(\bar{\wf}^{m+1}, \bar{\uuf}^{m+1}\) are computed as the mapped averages
+\begin{equation}
+    (\bar{\wf}^{m+1})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\wf_i^{m+1})_j,\quad g,i,j \in \Mset,
+\end{equation}
+and
+\begin{equation}
+    (\bar{\uuf}^{m})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\uuf_i^{m})_j,\quad g,i,j \in \Mset.
+\end{equation}
+This results in a computationally inexpensive update step forcing the norm of the consensus to have value \(a\).
+
+% #############################################################################
+% #############################################################################
 \section{Numerical Evaluation}
-\label{sec:num_eval}
+\label{sec:perf_eval}
 
-\section{Conclusion}
+\begin{figure}[t]
+    \centering
+    \subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_time_SNR10.png}\label{fig:perf_eval:NPM_over_time_SNR10}}\\
+    \vspace*{-0.3cm}
+    \subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_SNR_L64_M5.png}\label{fig:perf_eval:NPM_over_SNR_L64_M5}}
+    \vspace*{-0.2cm}
+    \caption{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!64\) at different SNR values.
+Shown are (a) NPM at \(\text{SNR}=10\,\text{dB}\) over frame index \(m\) for convergence speed comparison and (b) the steady-state NPMs over different SNRs.}
+    \label{fig:perf_eval:NPM_over_time_exp1}
+\end{figure}
+
+The performance of the proposed algorithm is assessed via numerical simulations.
+As error measure, we use the normalized projection misalignment (NPM) \cite{huangClassFrequencydomainAdaptive2003}
+\begin{equation}
+    \text{NPM}(m) = 20\,\log_{10} \left(\frac{\left\| \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m) \right\|_2}{\left\|\h(m)\right\|_2} \right)
+\end{equation}
+where \(\h\) is the stacked vector of impulse response estimates (cf.
+\autoref{ssec:cross_rel}), which are the inversely Fourier-transformed estimated frequency responses stacked in \(\hf\) and \(\h_{\text{t}}\) is the ground truth.
+Further, the signal-to-noise ratio (SNR) for the experiments is defined as 
+\begin{equation}
+    \text{SNR} = 10 \log_{10} \left(\frac{\sigma_s^2 \| \h_t \|}{M \sigma_v^2} \right)
+\end{equation}
+where \(\sigma_s^2\) and \(\sigma_v^2\) are the variance of signal and noise respectively which both are modelled by (channel-independent) white Gaussian noise (WGN).
+
+The first experiment evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-channel system (\(M=5,\, N=5\)).
+The impulse responses are drawn from a Normal distribution with unit variance, and the signal is 100 seconds (\(f_s=8000\)) of WGN to ensure convergence of all algorithms.
+The step sizes are hand tuned for stable convergence: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
+\autoref{fig:perf_eval:NPM_over_time_exp1} shows the median of 30 Monte-Carlo runs where the averaged NPM of the last \(100\) frames is taken as measurement.
+It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
+
+\begin{figure}[t]
+    \centering
+    % \hspace*{-0.4cm}\subfloat[][\(M\!=\!4,P\!=\!4\)]{\includegraphics[height=4cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
+    \hspace*{-0.2cm}\subfloat[][\(M\!=\!4,N\!=\!4\)]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}
+        \put(54,48){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.5]{tikz/connection_matrix_eval}}
+    \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
+    \hspace*{-0.0cm}\subfloat[][\(M\!=\!8,N\!=\!8\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
+    \vspace*{-0.2cm}
+    \caption{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of the sub-problem overlap \(\zeta\).}
+    \label{fig:perf_eval:NPM_over_time_exp2}
+\end{figure}
+
+The second experiment is a small-scale assessment of the influence of the overlap of sub-problems.
+Two base scenarios, \(M=4,\,N=4\) and \(M=8,\,N=8\), are evaluated using short (\(L=16\)) random impulse responses and different values for the sub-problem overlap parameter \(\zeta\) which is defined as the ratio of ones to zeros of only considering elements of \(\mtxb{G}\) that are not part of the main diagonal, superdiagonal and the first element of the last row (marked gray in \autoref{fig:perf_eval:NPM_over_time_M4}).
+Random patterns satisfying this definition for \(\zeta \in \{0.0,\,0.25,\,0.5,\,0.75\}\) are generated.
+\autoref{fig:perf_eval:NPM_over_time_exp2} shows the median of 30 Monte-Carlo runs for the two setups, which shows the proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error is not dependent on \(\zeta\).
+
+% #############################################################################
+% #############################################################################
+\section{Conclusions}
 \label{sec:conclusion}
-
-% \begin{figure}[tb]
-
-% 	\begin{minipage}[b]{1.0\linewidth}
-% 		\centering
-% 		\centerline{\includegraphics[width=8.5cm]{image1}}
-% 		%  \vspace{2.0cm}
-% 		\centerline{(a) Result 1}\medskip
-% 	\end{minipage}
-% 	%
-% 	\begin{minipage}[b]{.48\linewidth}
-% 		\centering
-% 		\centerline{\includegraphics[width=4.0cm]{image3}}
-% 		%  \vspace{1.5cm}
-% 		\centerline{(b) Results 2}\medskip
-% 	\end{minipage}
-% 	\hfill
-% 	\begin{minipage}[b]{0.48\linewidth}
-% 		\centering
-% 		\centerline{\includegraphics[width=4.0cm]{image4}}
-% 		%  \vspace{1.5cm}
-% 		\centerline{(c) Result 3}\medskip
-% 	\end{minipage}
-% 	%
-% 	\caption{Example of placing a figure with results.}
-% 	\label{fig:example}
-% 	%
-% \end{figure}
+In this paper, a novel adaptive ADMM algorithm for blind system identification was developed.
+The algorithm separates the BSI problem into lower-dimensional sub-problems to reduce complexity and allow parallel processing while maintaining steady-state error performance and convergence speed.
+Comparison to state-of-the-art algorithms in numerical simulations shows improved steady-state error measures for randomly generated impulse responses.
+A further experiment to assess the influence of sub-problem overlap shows that steady-state performance is not affected by the separation while convergence speed is.
 
@@
 % BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
-% style file from IEEE produces unsorted bibliography list.
+% style file from IEEE produces an unsorted bibliography list.
 % -------------------------------------------------------------------------
-% \bibliographystyle{IEEEbib}
-% \bibliography{refs}
+\bibliographystyle{IEEEbib}
+\bibliography{iwaenc2022}
 

### 2022-04-27 paper.tex
grammar fixes and citation file

@@
 \begin{equation}
-    \R(n) \h = \bm{0}, \label{eq:cross_rel:null_space}\\
+    \R(n) \h = \bm{0} \label{eq:cross_rel:null_space}\\
 \end{equation}
@@
         -\R_{1M} & -\R_{2M} & \cdots & \sum_{i \neq M} \R_{ii}\\
-    \end{bmatrix},\label{eq:cross_rel:data_matrix}
+    \end{bmatrix}\label{eq:cross_rel:data_matrix}
 \end{equation}
@@
 \begin{equation}
-    \Rf_{ij}(m) = \bm{{S}}_{i}^\herm (m) \bm{{S}}_{j}(m),
+    \Rf_{ij}(m) = \bm{X}_{i}^\herm (m) \bm{X}_{j}(m)
 \end{equation}
@@
 \begin{equation}
-    \bm{{S}}_{i}(m) = \bm{{W}}^{01}_{L \times 2L} \bm{{D}}_{i}(m) \bm{{W}}^{10}_{2L \times L}.
+    \bm{X}_{i}(m) = \bm{{W}}^{01}_{L \times 2L} \bm{{D}}_{i}(m) \bm{{W}}^{10}_{2L \times L}.
 \end{equation}
-The matrix \(\bm{{D}}_{i}(m) = \operatorname{diag} \left\{ \operatorname{FFT}_{2L} \left\{ \x_{i,2L}(m) \right\} \right\}\) contains the  signal spectrum on its diagonal and the overlap-save matrices are defined as
+The matrix \(\bm{{D}}_{i}(m) = \operatorname{diag} \left\{ \operatorname{FFT}_{2L} \left\{ \x_{i,2L}(m) \right\} \right\}\) contains the  signal spectrum on its diagonal and
+\begin{align}
+    \bm{{W}}_{L \times 2L}^{01} &= \mtxb{F}_{L \times L} \mtxb{W}_{L \times 2L}^{01} \mtxb{F}_{2L \times 2L}^{-1}\\
+    \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1}
+\end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the DFT matrices for sizes L and 2L respectively and 
 \begin{align}
@@
         \mtxb{0}_{L \times L} & \mtxb{I}_{L \times L}
-    \end{bmatrix},\\
+    \end{bmatrix}\\
     \mtxb{W}_{2L \times L}^{10} &= \begin{bmatrix}
         \mtxb{I}_{L \times L} & \mtxb{0}_{L \times L}
-    \end{bmatrix}^\T,\\
-    \bm{{W}}_{L \times 2L}^{01} &= \mtxb{F}_{L \times L} \mtxb{W}_{L \times 2L}^{01} \mtxb{F}_{2L \times 2L}^{-1},\\
-    \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1},
-\end{align} where $\mtxb{F}$ is the DFT matrix for sizes L and 2L.
+    \end{bmatrix}^\T
+\end{align}
+denote the time-domain overlap-save matrices.
+
 Analogous to the time-domain formulation, the vector \(\hf\) is a stacked vector of complex-valued frequency responses.
-In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem.
+In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem:
 %  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
 % As this effectively seeks the \(a\)-scaled eigenvector of the squared hermitian matrix \(\Rf^\herm \Rf\) corresponding to the smallest eigenvalue, we can replace it with its non-squared form \(\Rf\) as the eigenvectors for both are equal.
-To compute the estimates, we minimize the cost function
-\begin{equation}
-    J(\hf)(m+1) = \hf^\herm(m) \Rf(m) \hf(m),\label{eq:frequency_domain:cost_function}
-\end{equation}
-as the minimization problem
+% To compute the estimates, we minimize the cost function
+% \begin{equation}
+%     J(\hf)(m+1) = \hf^\herm(m) \Rf(m) \hf(m)\label{eq:frequency_domain:cost_function}
+% \end{equation}
+% as the minimization problem
 \begin{align}
-    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \Rf(m) \hf(m), \label{eq:frequency_domain:min_prob}\\
-    \text{s.t. } \quad &\hf^\herm(m) \hf(m) = a.
+    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \Rf(m) \hf(m) \label{eq:frequency_domain:min_prob}\\
+    \text{s.t. } \quad &\hf^\herm(m) \hf(m) = a
 \end{align}
-In the following section, we introduce a novel adaptive algorithm to find a solution to this problem.
+where \(a\) is a scaling to be chosen.
+
+In the following section, we introduce an adaptive algorithm using ADMM to find a solution to this problem.
 
@@
 Each sub-problem is defined by a subset of the full channel set \(\Cset_i \subseteq \Mset\) with \(i \in \Nset\).
-Following from that, we define the sets \(\Csetb_j = \left\{ i \vert j \in \Cset_i \right\}\) for \(i,j \in \Mset\) which is the set of sub-problems a channel  \(j\) is part of.
-This channel-to-sub-problem relation can also be expressed as a \(M \times P\) matrix \(\mtxb{G}\) where the sets \(\Cset_i\) and \(\Csetb_j\) are the indices of non-zero elements of the rows and columns respectively (see \autoref{fig:problem_splitting:problem_splitting_matrix}).
+Following from that, we define the sets \(\Csetb_j = \left\{ i \vert j \in \Cset_i \right\}\) for \(i,j \in \Mset\) where for each channel \(j\) a set represents the sub-problems that particular channel is part of.
+This channel-to-sub-problem relation can also be represented as a \(M \times N\) matrix \(\mtxb{G}\) where the sets \(\Cset_i\) and \(\Csetb_j\) are the indices of non-zero elements of the rows and columns respectively (see \autoref{fig:problem_splitting:problem_splitting_matrix}).
 Further, \(M_i = \left| \Cset_i \right| \) and \(N_j = \left| \Csetb_j \right| \) with \(i,j \in \Mset\).
-We replace the cost function \eqref{eq:frequency_domain:cost_function} with the separable cost function 
+
+We replace the cost function minimized in \eqref{eq:frequency_domain:min_prob} with the separable cost function 
 \begin{equation}
-    \tilde{J}(\hf) = \sum_{i \in \Nset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Nset} \wf_i^\T \aRhof_i \wf_i
+    \tilde{J}(\hf) = \sum_{i \in \Nset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Nset} \wf_i^\herm \aRhof_i \wf_i
     \label{eq:problem_splitting:cost_function}
@@
 \label{ssec:general_consensus_admm}
-Minimization problems with separable const functions can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}.
+Minimization problems with separable cost functions can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}.
 In the previous section we introduced the split cost function \eqref{eq:problem_splitting:cost_function} which we now set in the context of the general-form consensus problem
@@
 \begin{align}
-    &\mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Mset} \left( \wf_i^\herm \aRhof_i \wf_i + \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right)\vphantom{+ \frac{\rho}{2} \left\| \wf_i - \tilde{\hf}_i \right\|^2} \right.\nonumber\\
+    &\mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Nset} \left( \wf_i^\herm \aRhof_i \wf_i + \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right)\vphantom{+ \frac{\rho}{2} \left\| \wf_i - \tilde{\hf}_i \right\|^2} \right.\nonumber\\
     &\left.
@@
 Following from this, also the data term in \eqref{eq:general_consensus_admm:lagrangian} is time-dependent, which from here on out will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \aRhof_i^{m} \wf_i\).
-A thorough look at time-varying data terms in ADMM can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as "Online-ADMM".
+A thorough look at time-varying data terms in ADMM can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as ``Online-ADMM".
 

### 2022-04-29 paper.tex
include feedback randy & filip

@@
 This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.
-956369.}, Filip Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, Randall Ali, Toon van Waterschoot, Marc Moonen}
+956369.
+Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}, Filip Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, Randall Ali, Toon van Waterschoot, Marc Moonen, Jan (?), Jesper (?)}
 \address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
@@
 \begin{abstract}
-    In this contribution, we propose a cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM).
+    In this paper, we propose a cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM).
     The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into lower-dimensional sub-problems with reduced computational complexity, which can be solved in parallel.
@@
 Suh algorithms include the cross-relation (CR) algorithm \cite{tong1994blind, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
-
 Out of various multichannel BSI algorithms which have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.
@@
 
-The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves convex optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
+The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
 In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
@@
 
-The resulting algorithm provides good estimation results while keeping the computational complexity low and providing scalability through distributed processing possibilities.
+As shown in numerical simulations, the resulting algorithm provides good estimation results as compared to state-of-the-art algorithms while keeping the computational complexity low and providing scalability through distributed processing possibilities.
+% All code to generate the results and this paper are available at \cite{Blochberger_CROSS-RELATION-BASED_FREQUENCY-DOMAIN_BLIND_2022}
 
@@
 \label{ssec:signal_model}
-We consider an acoustic SIMO system with the input signal \(\mtxb{s}(n)\) and \(i \in \Mset\) with \(\Mset \triangleq \{1,\ldots,M\} \) outputs \(\x_i(n)\) defined as
+We consider an acoustic SIMO system with the input signal \(\mtxb{s}(n)\) and \(M\) outputs \(\x_i(n)\) defined as
 \begin{align}
@@
 \end{align}
-Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated.
+where \(i \in \Mset \triangleq \{1,\ldots,M\} \).
+Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated to \(\mtxb{s}(n)\).
 The signal model is described by
@@
 \end{equation}
-where \(\mtxb{H}_i\) is the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) which represents the system to be identified.
+where \(\mtxb{H}_i\) is the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) of length \(L\) which represents the system to be identified.
+The impulse response length \(L\) is assumed to be known.
 
@@
 are not co-prime), and (ii) the covariance matrix of the input signal \(\mtxb{s}(n)\) is of full rank (i.e.
-the signal fully excites the channels).
+the signal has a number of modes \(\geq 2L+1\)).
 
@@
 which states that the channel output signal convolved with the impulse response of another is equal to the vice-versa as follows from the commutativity property of the convolution.
-Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij} = \ev{\x_i \x_j^\T}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g.
+Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g.
 \cite{huangAdaptiveMultichannelLeast2002} for a more thourough derivation) yields the system of equations
@@
 \end{equation}
-where the \(M L \times M L\) matrix is recursivly computed by \begin{equation}
-    \Rf(m) = \eta \Rf(m-1) + (1-\eta )\hat{\Rf}(m)
+where the \(M L \times M L\) matrix is recursivly estimated by \begin{equation}
+    \hat{\Rf}(m) = \eta \hat{\Rf}(m-1) + (1-\eta )\tilde{\Rf}(m).
 \end{equation}
-instead of estimating the expectation by sample averages.
-Here, \(\eta \in [0,1]\) is an exponential smoothing factor and \(\hat{\Rf}(m)\) is constructed analogous to \eqref{eq:cross_rel:data_matrix}, however with covariance matrices replaced by cross-spectrum matrices
+where \(\eta \in [0,1]\) is an exponential smoothing factor and \(\tilde{\Rf}(m)\) is constructed analogous to \eqref{eq:cross_rel:data_matrix}, however with covariance matrices replaced by instantaneous cross-spectrum matrices
 \begin{equation}
-    \Rf_{ij}(m) = \bm{X}_{i}^\herm (m) \bm{X}_{j}(m)
+    \tilde{\Rf}_{ij}(m) = \bm{X}_{i} (m) \bm{X}_{j}^\herm (m)
 \end{equation}
@@
     \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1}
-\end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the DFT matrices for sizes L and 2L respectively and 
-\begin{align}
-    \mtxb{W}_{L \times 2L}^{01} &= \begin{bmatrix}
+\end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the discrete Fourier transform (DFT) matrices for sizes L and 2L respectively and \(
+    \mtxb{W}_{L \times 2L}^{01} = \begin{bmatrix}
         \mtxb{0}_{L \times L} & \mtxb{I}_{L \times L}
-    \end{bmatrix}\\
-    \mtxb{W}_{2L \times L}^{10} &= \begin{bmatrix}
+    \end{bmatrix}\)
+    and \(
+    \mtxb{W}_{2L \times L}^{10} = \begin{bmatrix}
         \mtxb{I}_{L \times L} & \mtxb{0}_{L \times L}
-    \end{bmatrix}^\T
-\end{align}
+    \end{bmatrix}^\T\)
 denote the time-domain overlap-save matrices.
@@
 Analogous to the time-domain formulation, the vector \(\hf\) is a stacked vector of complex-valued frequency responses.
-In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem:
+In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002}:
 %  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
@@
 \begin{align}
-    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \Rf(m) \hf(m) \label{eq:frequency_domain:min_prob}\\
-    \text{s.t. } \quad &\hf^\herm(m) \hf(m) = a
+    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \hat{\Rf}(m) \hf(m) \label{eq:frequency_domain:min_prob}\\
+    \text{s.t. } \quad &\hf^\herm(m+1) \hf(m+1) = 1.
 \end{align}
-where \(a\) is a scaling to be chosen.
 
@@
 Following from that, we define the sets \(\Csetb_j = \left\{ i \vert j \in \Cset_i \right\}\) for \(i,j \in \Mset\) where for each channel \(j\) a set represents the sub-problems that particular channel is part of.
-This channel-to-sub-problem relation can also be represented as a \(M \times N\) matrix \(\mtxb{G}\) where the sets \(\Cset_i\) and \(\Csetb_j\) are the indices of non-zero elements of the rows and columns respectively (see \autoref{fig:problem_splitting:problem_splitting_matrix}).
+% This channel-to-sub-problem relation can also be represented as a \(M \times N\) matrix \(\mtxb{G}\) where the sets \(\Cset_i\) and \(\Csetb_j\) are the indices of non-zero elements of the rows and columns respectively (see \autoref{fig:problem_splitting:problem_splitting_matrix}).
 Further, \(M_i = \left| \Cset_i \right| \) and \(N_j = \left| \Csetb_j \right| \) with \(i,j \in \Mset\).
@@
 \begin{equation}
-    \tilde{J}(\hf) = \sum_{i \in \Nset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Nset} \wf_i^\herm \aRhof_i \wf_i
+    \tilde{J}(\hf) = \sum_{i \in \Nset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Nset} \wf_i^\herm \hat{\aRhof}_i \wf_i
     \label{eq:problem_splitting:cost_function}
@@
 where \(\wf_i\) is defined as the stacked vector of estimated frequency responses analogous to \(\hf\) (cf.
-\autoref{ssec:cross_rel}) and \(\aRhof\) is constructed as defined in \eqref{eq:cross_rel:data_matrix}, both using the respective subset \(\Cset_i\).
+\autoref{ssec:cross_rel}) and \(\hat{\aRhof}\) is constructed as defined in \eqref{eq:cross_rel:data_matrix}, both using the respective subset \(\Cset_i\).
 If the channel subsets are proper \(\Cset_i \subset \Mset\), this leads to \(N\) sub-problems, each with smaller dimensions than the original centralized problem, reducing complexity.
-The lowest-dimensionality is attained when each \(\Cset_i\) has two elements, i.e. two channels, with parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
-In \autoref{fig:problem_splitting:problem_splitting_matrix}, we try to visualize which information is used to solve the sub-problems compared to the initial problem for a general case.
+The lowest-dimensionality is attained when each \(\Cset_i\) has two elements, i.e.
+two channels, assuming perfect parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
+
+% \begin{figure}
+%     \centering
+%     \subfloat[][]{\includegraphics[trim={1.8cm 0 1.7cm 0},clip,scale=0.7]{images/parameter_mapping.pdf}}
+%     \subfloat[][]{\includestandalone[trim={0.65cm 0 0 0},clip,scale=0.7]{tikz/connection_matrix}}
+%     \subfloat[][]{\includestandalone[trim={0.6cm 0 0 0},clip,scale=0.6]{tikz/problem_splitting_matrix}}
+%     % \includestandalone[scale=1]{tikz/topology_general}
+%     \vspace*{-0.3cm}
+%     \caption{Problem splitting and parameter mapping for a general case with \(M=5\) channels and \(N=4\) sub-problems.
+(a) shows the mapping of the local estimate components \((\wf_i)_j\) to the global consensus components \((\hf)_j\) via \(\mathcal{G}(i,j)\), (b) \(\mtxb{G}\) with 1 (\(\blacksquare\)) and 0 (\(\square\)), (c) shows \(i,j\)-cross-relations used by sub-problems compared to full \(M\)-channel problem.}
+%     \label{fig:problem_splitting:problem_splitting_matrix}
+% \end{figure}
 
@@
     \centering
-    \subfloat[][]{\includegraphics[trim={1.8cm 0 1.7cm 0},clip,scale=0.7]{images/parameter_mapping.pdf}}
-    \subfloat[][]{\includestandalone[trim={0.65cm 0 0 0},clip,scale=0.7]{tikz/connection_matrix}}
-    \subfloat[][]{\includestandalone[trim={0.6cm 0 0 0},clip,scale=0.6]{tikz/problem_splitting_matrix}}
+    \includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}
     % \includestandalone[scale=1]{tikz/topology_general}
-    \vspace*{-0.3cm}
-    \caption{Problem splitting and parameter mapping for a general case with \(M=5\) channels and \(N=4\) sub-problems.
-(a) shows the mapping of the local estimate components \((\wf_i)_j\) to the global consensus components \((\hf)_j\) via \(\mathcal{G}(i,j)\), (b) \(\mtxb{G}\) with 1 (\(\blacksquare\)) and 0 (\(\square\)), (c) shows \(i,j\)-cross-relations used by sub-problems compared to full \(M\)-channel problem.}
+    \vspace*{-0.5cm}
+    \caption{Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for a general case with \(M=4\) channels and \(N=4\) sub-problems.}
     \label{fig:problem_splitting:problem_splitting_matrix}
@@
 \end{align}
-where \(\mathcal{G}(i,j)=g\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
+where \(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
 one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\) (cf.
@@
 The augmented Lagrangian for this particular general-form consensus problem is
-% \begin{equation}
-%     \mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Mset} \left( \wf_i^\herm \aRhof_i \wf_i + 2 \Re \left\{ \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right\} + \rho \left\| \wf_i - \tilde{\hf}_i \right\|\label{eq:general_consensus_admm:lagrangian}
-% \end{equation}
 \begin{align}
-    &\mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Nset} \left( \wf_i^\herm \aRhof_i \wf_i + \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right)\vphantom{+ \frac{\rho}{2} \left\| \wf_i - \tilde{\hf}_i \right\|^2} \right.\nonumber\\
-    &\left.
+    \mathcal{L}_{\rho} (\wf,\hf,\uuf) &= \sum_{i \in \Nset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
+\vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|} \nonumber\\
+    \vphantom{\wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)} & \qquad \qquad \qquad \qquad \left.+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right)\label{eq:general_consensus_admm:lagrangian}
+\end{align}
+% \begin{align}
+%     &\mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Nset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right)\vphantom{+ \frac{\rho}{2} \left\| \wf_i - \tilde{\hf}_i \right\|^2} \right.\nonumber\\
+%     &\left.
 + \left(\wf_i - \tilde{\hf}_i\right)^\herm \uuf_i + \left( \wf_i - \tilde{\hf}_i \right)^\herm \rho \I \left( \wf_i - \tilde{\hf}_i \right) \right).\label{eq:general_consensus_admm:lagrangian}
-\end{align}
+% \end{align}
 The ADMM then consists of the steps:
@@
     \wf_i^{k+1} &= \underset{\wf_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\wf,\hf^k,\uuf^k),\label{eq:general_consensus_admm:local}\\
-    \hf^{k+1} &= \underset{\hf, \|\hf\| = a}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\wf^{k+1},\hf,\uuf^k)\label{eq:general_consensus_admm:global}\\
+    \hf^{k+1} &= \underset{\hf, \|\hf\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\wf^{k+1},\hf,\uuf^k)\label{eq:general_consensus_admm:global}\\
     \uuf_i^{k+1} &= \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right).\label{eq:general_consensus_admm:dual}
@@
 % \begin{align}
-%     &\wf_i^{k+1} = \underset{\wf_i}{\operatorname{argmin}} \left\{ \wf_i^\herm \aRhof_i \wf_i + \uuf_i^{k\,\herm} \left(\wf_i - \tilde{\hf}_i^{k}\right) \vphantom{+ \left\| \wf_i - \tilde{\hf}_i^{k} \right\|^2}\right.\nonumber\\
+%     &\wf_i^{k+1} = \underset{\wf_i}{\operatorname{argmin}} \left\{ \wf_i^\herm \hat{\aRhof}_i \wf_i + \uuf_i^{k\,\herm} \left(\wf_i - \tilde{\hf}_i^{k}\right) \vphantom{+ \left\| \wf_i - \tilde{\hf}_i^{k} \right\|^2}\right.\nonumber\\
 %     &\left.+ \left(\wf_i - \tilde{\hf}_i^{k}\right)^\herm \uuf_i^{k} + \left( \wf_i - \tilde{\hf}_i^{k} \right)^\herm \rho \I \left( \wf_i - \tilde{\hf}_i^{k} \right) \right\},\label{eq:general_consensus_admm:local}\\
@@
 % \end{align}
-As this is still denoted as an iterative algorithm, we will introduce the online/adaptive aspect of the proposed one next.
+As this is still denoted as an iterative algorithm, we will introduce the online/adaptive aspect of the proposed algorithm in the following.
 
@@
 \label{ssec:online_admm}
-We introduced the original problem \eqref{eq:frequency_domain:null_space} with time-dependent data matrix.
-Following from this, also the data term in \eqref{eq:general_consensus_admm:lagrangian} is time-dependent, which from here on out will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \aRhof_i^{m} \wf_i\).
-A thorough look at time-varying data terms in ADMM can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as ``Online-ADMM".
+We introduced the original problem in \eqref{eq:frequency_domain:null_space} with time-dependent data matrix.
+It therefore follows that the data term in \eqref{eq:general_consensus_admm:lagrangian} is also time-dependent, which from here on will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \hat{\aRhof}_i^{m} \wf_i\).
+A thorough overview of time-varying data terms in ADMM can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as ``Online-ADMM".
 
@@
 
-The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform a Newton update step
+The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the update step
 \begin{equation}
-    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \aRhof_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right)\label{eq:online_admm:local_update}
+    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right)\label{eq:online_admm:local_update}
 \end{equation}
-where \(0  < \mu\leq 1\) is a step size and \(\bm{{V}}_i^m = \left(\aRhof_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
+where \(0  < \mu\leq 1\) is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
 As this inverse is costly to compute, it is approximated by a diagonalized matrix
 \begin{equation}
-    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \left( \operatorname{diag} \left\{ \aRhof_i^m \right\} + \rho \mtxb{1} \right)^{-1}\right\},
+    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \left( \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right)^{-1}\right\},
 \end{equation}
@@
 \begin{equation}
-    \hf^{m+1} = a\frac{\bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} }{\left\| \bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} \right\|}.\label{eq:online_admm:consensus_update}
+    \hf^{m+1} = \frac{\bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} }{\left\| \bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} \right\|}.\label{eq:online_admm:consensus_update}
 \end{equation}
@@
 \end{equation}
-This results in a computationally inexpensive update step forcing the norm of the consensus to have value \(a\).
+This results in a computationally inexpensive update step forcing the norm of the consensus to have unit value.
 
@@
 The performance of the proposed algorithm is assessed via numerical simulations.
-As error measure, we use the normalized projection misalignment (NPM) \cite{huangClassFrequencydomainAdaptive2003}
+As an error measure, we use the normalized projection misalignment (NPM) \cite{huangClassFrequencydomainAdaptive2003}
 \begin{equation}
@@
 \autoref{ssec:cross_rel}), which are the inversely Fourier-transformed estimated frequency responses stacked in \(\hf\) and \(\h_{\text{t}}\) is the ground truth.
-Further, the signal-to-noise ratio (SNR) for the experiments is defined as 
+The signal-to-noise ratio (SNR) for the simulations is defined as
 \begin{equation}
@@
 
-The first experiment evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-channel system (\(M=5,\, N=5\)).
-The impulse responses are drawn from a Normal distribution with unit variance, and the signal is 100 seconds (\(f_s=8000\)) of WGN to ensure convergence of all algorithms.
-The step sizes are hand tuned for stable convergence: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
-\autoref{fig:perf_eval:NPM_over_time_exp1} shows the median of 30 Monte-Carlo runs where the averaged NPM of the last \(100\) frames is taken as measurement.
+The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-channel system (\(M=5,\, N=5\)).
+The impulse responses are drawn from a Normal distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.
+The step sizes are hand tuned for similar convergence speed: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
+\autoref{fig:perf_eval:NPM_over_time_exp1} shows the median of 30 Monte-Carlo runs where the averaged NPM of the last \(100\) frames is plotted.
 It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
@@
     \centering
-    % \hspace*{-0.4cm}\subfloat[][\(M\!=\!4,P\!=\!4\)]{\includegraphics[height=4cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
-    \hspace*{-0.2cm}\subfloat[][\(M\!=\!4,N\!=\!4\)]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}
-        \put(54,48){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.5]{tikz/connection_matrix_eval}}
-    \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
+    \hspace*{-0.2cm}\subfloat[][\(M\!=\!4,P\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
+    % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4,N\!=\!4\)]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}
+    %     \put(54,48){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.5]{tikz/connection_matrix_eval}}
+    % \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
     \hspace*{-0.0cm}\subfloat[][\(M\!=\!8,N\!=\!8\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
     \vspace*{-0.2cm}
-    \caption{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of the sub-problem overlap \(\zeta\).}
+    \caption{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of the sub-problem overlap \(\zeta\) for \(\text{SNR}=20\,\text{dB}\).}
     \label{fig:perf_eval:NPM_over_time_exp2}
@@
 The second experiment is a small-scale assessment of the influence of the overlap of sub-problems.
-Two base scenarios, \(M=4,\,N=4\) and \(M=8,\,N=8\), are evaluated using short (\(L=16\)) random impulse responses and different values for the sub-problem overlap parameter \(\zeta\) which is defined as the ratio of ones to zeros of only considering elements of \(\mtxb{G}\) that are not part of the main diagonal, superdiagonal and the first element of the last row (marked gray in \autoref{fig:perf_eval:NPM_over_time_M4}).
+Two base scenarios, \(M=4,\,N=4\) and \(M=8,\,N=8\), are evaluated using short (\(L=16\)) random impulse responses and different values for the sub-problem overlap parameter \(\zeta\) which is defined as the ratio of ones to zeros of only considering elements of \(\mtxb{G}\) that are not part of the main diagonal, superdiagonal and the first element of the last row (marked gray on the inset of \autoref{fig:perf_eval:NPM_over_time_M4}).
 Random patterns satisfying this definition for \(\zeta \in \{0.0,\,0.25,\,0.5,\,0.75\}\) are generated.
@@
 \label{sec:conclusion}
-In this paper, a novel adaptive ADMM algorithm for blind system identification was developed.
-The algorithm separates the BSI problem into lower-dimensional sub-problems to reduce complexity and allow parallel processing while maintaining steady-state error performance and convergence speed.
-Comparison to state-of-the-art algorithms in numerical simulations shows improved steady-state error measures for randomly generated impulse responses.
-A further experiment to assess the influence of sub-problem overlap shows that steady-state performance is not affected by the separation while convergence speed is.
+In this paper, an adaptive ADMM algorithm for blind system identification was developed.
+The algorithm separates the BSI problem into lower-dimensional sub-problems to reduce computational complexity and allows for parallel or distributed processing while maintaining steady-state error performance and convergence speed.
+Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms and that  steady-state performance is not affected by speparating the BSI problem into sub-problems while convergence speed is.
 
@@
 \bibliographystyle{IEEEbib}
-\bibliography{iwaenc2022}
+\bibliography{refs}
 

### 2022-04-30 paper.tex
pre distributed commit

@@
 \end{equation}
-where \(0  < \mu\leq 1\) is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
+where \(\mu\) (\(0  < \mu\leq 1\)) is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
 As this inverse is costly to compute, it is approximated by a diagonalized matrix
@@
 
-The second experiment is a small-scale assessment of the influence of the overlap of sub-problems.
+The second simulation is a small-scale assessment of the influence of the overlap of sub-problems.
 Two base scenarios, \(M=4,\,N=4\) and \(M=8,\,N=8\), are evaluated using short (\(L=16\)) random impulse responses and different values for the sub-problem overlap parameter \(\zeta\) which is defined as the ratio of ones to zeros of only considering elements of \(\mtxb{G}\) that are not part of the main diagonal, superdiagonal and the first element of the last row (marked gray on the inset of \autoref{fig:perf_eval:NPM_over_time_M4}).

### 2022-05-01 paper.tex
change abstract to distributed algorithm

@@
 % ------
-\title{CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE ADMM}
+\title{DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM}
 %
@@
 % ---------------
-\name{Matthias Blochberger\sthanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+\name{M.
+Blochberger\sthanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
 This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.
 956369.
-Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}, Filip Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, Randall Ali, Toon van Waterschoot, Marc Moonen, Jan (?), Jesper (?)}
+Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}, F.
+Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, R.
+Ali, T.
+van Waterschoot, M.
+Moonen, J.
+Østergaard, J.
+Jensen}
 \address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
@@
 \begin{abstract}
-    In this paper, we propose a cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM).
-    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into lower-dimensional sub-problems with reduced computational complexity, which can be solved in parallel.
-    Each sub-problem yields estimates for a subset of channel frequency responses, which then are combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
-    With numerical simulations, we show that it is possible to achieve convergence speeds comparable to low-cost frequency-domain algorithms and estimation errors better than a high-performing Quasi-Newton algorithm.
+    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a sensor network with a fusion center.
+    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
+    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
+    Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to the networks fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
+    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
 \end{abstract}
@@
 \begin{keywords}
-    blind system identification, multichannel signal processing, ADMM, Online-ADMM
+    blind system identification, multichannel signal processing, distributed signal processing, ADMM, Online-ADMM
 \end{keywords}

### 2022-05-02 paper.tex
change abstract to distributed algorithm

@@
 \input{preamble.tex}
+\ninept
 
@@
     Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to the networks fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
-    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
+    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to fully centralized low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
 \end{abstract}
@@
 
-The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
-In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
-The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
+While there exist distributed signal processing algorithms for applications such as noise cancellation \cite{}, echo control \cite{} or beamforming \cite{}, there is a gap regarding BSI which we are starting to fill with this contribution.
+The general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems with cost functions separable in its variable.
+We separate the inter-channel cross-relations of the BSI problem according to the networks topology, i.e. each node
+
+to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
+
+% The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
+% In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
+% The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
 
@@
 \begin{align}
-    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \hat{\Rf}(m) \hf(m) \label{eq:frequency_domain:min_prob}\\
-    \text{s.t. } \quad &\hf^\herm(m+1) \hf(m+1) = 1.
+    \hat{\hf} = \arg \min_{\hf} \quad &\hf^\herm \hat{\Rf} \hf \label{eq:frequency_domain:min_prob}\\
+    \text{s.t. } \quad &\hf^\herm \hf = 1.
 \end{align}

### 2022-05-02 paper.tex
include feedback randy & filip

--- 2022-04-30 paper.tex
@@
 Early algorithms used higher-order statistics \cite{godardSelfRecoveringEqualizationCarrier1980,tongNewApproachBlind1991,mecidel1991tutorial} for channel estimation, however a high computational complexity has motivated research into algorithms using only second-order statistics.
-Suh algorithms include the cross-relation (CR) algorithm \cite{tong1994blind, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
+Such algorithms include the cross-relation (CR) algorithm \cite{tong1994blind, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
 Out of various multichannel BSI algorithms which have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.

### 2022-05-02 paper.tex
add constraint where its missing
new intro

--- 2022-05-01 paper.tex
@@
     The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
-    Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to the networks fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
-    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
+    Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to a fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
+    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to fully centralized low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
 \end{abstract}
@@
 It was introduced in \cite{satoMethodSelfRecoveringEqualization1975} and various algorithms have been proposed since.
-Early algorithms used higher-order statistics \cite{godardSelfRecoveringEqualizationCarrier1980,tongNewApproachBlind1991,mecidel1991tutorial} for channel estimation, however a high computational complexity has motivated research into algorithms using only second-order statistics.
-Suh algorithms include the cross-relation (CR) algorithm \cite{tong1994blind, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
+Early algorithms used higher-order statistics \cite{godardSelfRecoveringEqualizationCarrier1980,tongNewApproachBlind1991,mendelTutorialHigherorderStatistics1991} for channel estimation, however a high computational complexity has motivated research into algorithms using only second-order statistics.
+Such algorithms include the cross-relation (CR) algorithm \cite{langtongBlindIdentificationEqualization1994, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
 Out of various multichannel BSI algorithms which have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.
@@
 The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the BFGS method to estimate the Hessian of the problem.
+\begin{attention}
+    This is also a time-domain algorithm, should a comparison even be made? MCQN in plots
+\end{attention}
 
-The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
-In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
+The expanding field of distributed signal processing brought forward algorithms for distributed noise control, echo cancellation, or beamforming, however, research into the task of BSI is limited.
+\begin{attention}
+    cite
+\end{attention}
+While there exist time-domain algorithms as introduced in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, they do not pose apt comparisons to the frequency-domain algorithm being proposed.
+In this paper, we use the general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} to distribute and solve the optimization problem posed by the task.
+We separate the inter-channel cross-relations of the BSI problem according to the network's topology, i.e.
+each node solves a sub-problem using data from its network neighbors, and the entirety of connected nodes subsequently reaches a consensus for the channel frequency responses.
 The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
 
-As shown in numerical simulations, the resulting algorithm provides good estimation results as compared to state-of-the-art algorithms while keeping the computational complexity low and providing scalability through distributed processing possibilities.
-% All code to generate the results and this paper are available at \cite{Blochberger_CROSS-RELATION-BASED_FREQUENCY-DOMAIN_BLIND_2022}
+As shown in numerical simulations, the resulting algorithm provides good estimation results as compared to state-of-the-art centralized frequency-domain algorithms.
 
@@
 \label{sec:problem_statement}
+
+% #############################################################################
+\subsection{Sensor Network}
+\label{ssec:sensor_network}
+We consider a network consisting of \(M\) sensor nodes, each capable of acquiring a signal and independent processing.
 
@@
 
-Analogous to the time-domain formulation, the vector \(\hf\) is a stacked vector of complex-valued frequency responses.
+Analogous to the time-domain formulation, the \(ML \times 1\) vector \(\hf\) is a stacked vector of complex-valued frequency responses.
 In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002}:
@@
 If the channel subsets are proper \(\Cset_i \subset \Mset\), this leads to \(N\) sub-problems, each with smaller dimensions than the original centralized problem, reducing complexity.
-The lowest-dimensionality is attained when each \(\Cset_i\) has two elements, i.e.
+The lowest dimensionality is attained when each \(\Cset_i\) has two elements, i.e.
 two channels, assuming perfect parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
@@
     \operatorname{minimize} \quad &\sum_{i \in \Nset} \tilde{J}_i(\wf_i)\\
-    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Nset,\,j \in \Cset_i
+    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Nset,\,j \in \Cset_i\\
+    &\hf^\herm \hf = 1
 \end{align}
@@
 The algorithm separates the BSI problem into lower-dimensional sub-problems to reduce computational complexity and allows for parallel or distributed processing while maintaining steady-state error performance and convergence speed.
-Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms and that  steady-state performance is not affected by speparating the BSI problem into sub-problems while convergence speed is.
+Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms and that steady-state performance is not affected by separating the BSI problem into sub-problems while convergence speed is.
 

### 2022-05-02 paper.tex
starting with toons suggestions

@@
 \newcommand{\Cset}{\mathcal{C}}
-\newcommand{\Csetb}{\bar{\mathcal{C}}}
 \newcommand{\Mset}{\mathcal{M}}
-\newcommand{\Nset}{\mathcal{N}}
+\newcommand{\Sset}{\mathcal{S}}
+\newcommand{\Rset}{\mathcal{R}}
 
@@
 The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the BFGS method to estimate the Hessian of the problem.
-\begin{attention}
+\begin{todo}
     This is also a time-domain algorithm, should a comparison even be made? MCQN in plots
-\end{attention}
+\end{todo}
 
-The expanding field of distributed signal processing brought forward algorithms for distributed noise control, echo cancellation, or beamforming, however, research into the task of BSI is limited.
-\begin{attention}
+The expanding field of distributed signal processing in wireless sensor networks (WSN) brought forward algorithms for distributed noise control, echo cancellation, or beamforming, however, research into the task of BSI is limited.
+\begin{todo}
     cite
-\end{attention}
+\end{todo}
 While there exist time-domain algorithms as introduced in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, they do not pose apt comparisons to the frequency-domain algorithm being proposed.
@@
 \label{ssec:sensor_network}
-We consider a network consisting of \(M\) sensor nodes, each capable of acquiring a signal and independent processing.
+We consider a WSN consisting of \(M\) sensor nodes, each acquiring a signal and equipped with a processing unit, and define the index set  \(i \in \Mset \triangleq \{1,\ldots,M\} \) representing these.
+Each node shares information with a set of neighboring nodes \(\Sset_i\) with \(i \in \Mset\), and receives information by a set of nodes \(\Rset_i\) with \(i \in \Mset\).
+% These connection links between nodes are represented as the \(M \times M\) network connection matrix \(\mtxb{C}\) with its elements defined as \(\mathrm{G}_{ij} = 1\) if the \(i\)-th node shares its signal information with the \(j\)-th node and \(\mathrm{G}_{ij} = 0\) otherwise.
+\autoref{fig:sensor_network:WSN} shows a network where each node shares its signal information with one or more neighbors.
+\begin{todo}
+    Which type of topology should be introduced. With fusion center? ring topology, "star" topology, depends on how consensus is introduced...\\
+    Make figure nicer.
+\end{todo}
+\begin{figure}
+    \centering
+    \includestandalone[trim={0 0 0 0},clip,height=2.5cm]{tikz/topology_general}
+    % \vspace*{-0.3cm}
+    \caption{WSN}
+    \label{fig:sensor_network:WSN}
+\end{figure}
+% \begin{figure}
+%     \centering
+%     \subfloat[][]{\includegraphics[trim={1.8cm 0 1.7cm 0},clip,scale=0.7]{images/parameter_mapping.pdf}}
+%     \subfloat[][]{\includestandalone[trim={0.65cm 0 0 0},clip,scale=0.7]{tikz/connection_matrix}}
+%     \subfloat[][]{\includestandalone[trim={0.6cm 0 0 0},clip,scale=0.6]{tikz/problem_splitting_matrix}}
+%     % \includestandalone[scale=1]{tikz/topology_general}
+%     \vspace*{-0.3cm}
+%     \caption{Problem splitting and parameter mapping for a general case with \(M=5\) channels and \(N=4\) sub-problems.
+(a) shows the mapping of the local estimate components \((\wf_i)_j\) to the global consensus components \((\hf)_j\) via \(\mathcal{G}(i,j)\), (b) \(\mtxb{G}\) with 1 (\(\blacksquare\)) and 0 (\(\square\)), (c) shows \(i,j\)-cross-relations used by sub-problems compared to full \(M\)-channel problem.}
+%     \label{fig:problem_splitting:problem_splitting_matrix}
+% \end{figure}
 
@@
 \label{ssec:signal_model}
-We consider an acoustic SIMO system with the input signal \(\mtxb{s}(n)\) and \(M\) outputs \(\x_i(n)\) defined as
-\begin{align}
-    \mtxb{s}(n) &= \begin{bmatrix}
+We consider an acoustic SIMO system with the input signal \(\mtxb{s}(n) = \begin{bmatrix}
     s(n)&s(n-1)&\ldots&s(n-2L+2)
-    \end{bmatrix}^{\T}\\
-    \x_i(n) &= \begin{bmatrix}
+\end{bmatrix}^{\T}\) and the \(M\) output signals \(\x_i(n)= \begin{bmatrix}
     x_i(n)&x_i(n-1)&\ldots&x_i(n-L+1)
-    \end{bmatrix}^{\T}.
-\end{align}
-where \(i \in \Mset \triangleq \{1,\ldots,M\} \).
+\end{bmatrix}^{\T}\) aquired by the sensor nodes of the WSN.
+% \begin{align}
+%     \mtxb{s}(n) &= \begin{bmatrix}
+%         s(n)&s(n-1)&\ldots&s(n-2L+2)
+%     \end{bmatrix}^{\T}\\
+%     \x_i(n) &= \begin{bmatrix}
+%         x_i(n)&x_i(n-1)&\ldots&x_i(n-L+1)
+%     \end{bmatrix}^{\T}.
+% \end{align}
 Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated to \(\mtxb{s}(n)\).
@@
 where \(\mtxb{H}_i\) is the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) of length \(L\) which represents the system to be identified.
-The impulse response length \(L\) is assumed to be known.
+For this paper, the length of the impulse responses \(L\) is assumed to be known.
 
@@
 \begin{equation}
-    \R(n) \h = \bm{0} \label{eq:cross_rel:null_space}\\
+    \R \h = \bm{0} \label{eq:cross_rel:null_space}\\
 \end{equation}
@@
 \begin{equation}
-    \Rf(m) \hf = \bm{0} \label{eq:frequency_domain:null_space}\\
+    \Rf \hf = \bm{0} \label{eq:frequency_domain:null_space}\\
 \end{equation}
@@
     \bm{{W}}_{L \times 2L}^{01} &= \mtxb{F}_{L \times L} \mtxb{W}_{L \times 2L}^{01} \mtxb{F}_{2L \times 2L}^{-1}\\
-    \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1}
+    \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1}\label{eq:frequency_domain:overlap}
 \end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the discrete Fourier transform (DFT) matrices for sizes L and 2L respectively and \(
@@
 Analogous to the time-domain formulation, the \(ML \times 1\) vector \(\hf\) is a stacked vector of complex-valued frequency responses.
-In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002}:
+The null space problem in \eqref{eq:frequency_domain:null_space} can not be solved by computing the eigenvector corresponding to the zero-valued eigenvalue because, in the presence of noise, the system matrix \(\Rf\) is of full rank and may not have any.
+Therefore it is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002} with a non-triviality constraint to avoid the zero solution:
 %  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
@@
 
-In the following section, we introduce an adaptive algorithm using ADMM to find a solution to this problem.
+In the following section, we introduce a distributed adaptive algorithm to find a solution to this problem.
 
@@
 
-% #############################################################################
-\subsection{Problem Splitting}
-\label{ssec:problem_splitting}
-In state-of-the-art algorithms \cite{heNoiseRobustFrequencyDomain2018,habetsOnlineQuasiNewtonAlgorithm2010}, the minimization problem \eqref{eq:frequency_domain:min_prob} is solved in its full form resulting in potentially high computational effort when the number of channels and length of impulse responses or number of DFT bins is large.
-Here however, we split the problem into \(N \in \mathbb{N}\) sub-problems and denote the index set of these \(N\) sub-problems as \(\Nset \triangleq \{1,\ldots,N\}\).
-Each sub-problem is defined by a subset of the full channel set \(\Cset_i \subseteq \Mset\) with \(i \in \Nset\).
-Following from that, we define the sets \(\Csetb_j = \left\{ i \vert j \in \Cset_i \right\}\) for \(i,j \in \Mset\) where for each channel \(j\) a set represents the sub-problems that particular channel is part of.
+% % #############################################################################
+% \subsection{Problem Splitting}
+% \label{ssec:problem_splitting}
+% In state-of-the-art algorithms \cite{heNoiseRobustFrequencyDomain2018,habetsOnlineQuasiNewtonAlgorithm2010}, the minimization problem \eqref{eq:frequency_domain:min_prob} is solved in its full form resulting in potentially high computational effort when the number of channels and length of impulse responses or number of DFT bins is large.
+% Here however, we split the problem into \(N \in \mathbb{N}\) sub-problems and denote the index set of these \(N\) sub-problems as \(\Nset \triangleq \{1,\ldots,N\}\).
+% Each sub-problem is defined by a subset of the full channel set \(\Cset_i \subseteq \Mset\) with \(i \in \Nset\).
+% Following from that, we define the sets \(\Csetb_j = \left\{ i \vert j \in \Cset_i \right\}\) for \(i,j \in \Mset\) where for each channel \(j\) a set represents the sub-problems that particular channel is part of.
 % This channel-to-sub-problem relation can also be represented as a \(M \times N\) matrix \(\mtxb{G}\) where the sets \(\Cset_i\) and \(\Csetb_j\) are the indices of non-zero elements of the rows and columns respectively (see \autoref{fig:problem_splitting:problem_splitting_matrix}).
-Further, \(M_i = \left| \Cset_i \right| \) and \(N_j = \left| \Csetb_j \right| \) with \(i,j \in \Mset\).
-
-We replace the cost function minimized in \eqref{eq:frequency_domain:min_prob} with the separable cost function 
-\begin{equation}
-    \tilde{J}(\hf) = \sum_{i \in \Nset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Nset} \wf_i^\herm \hat{\aRhof}_i \wf_i
-    \label{eq:problem_splitting:cost_function}
-\end{equation}
-where \(\wf_i\) is defined as the stacked vector of estimated frequency responses analogous to \(\hf\) (cf.
-\autoref{ssec:cross_rel}) and \(\hat{\aRhof}\) is constructed as defined in \eqref{eq:cross_rel:data_matrix}, both using the respective subset \(\Cset_i\).
-If the channel subsets are proper \(\Cset_i \subset \Mset\), this leads to \(N\) sub-problems, each with smaller dimensions than the original centralized problem, reducing complexity.
-The lowest dimensionality is attained when each \(\Cset_i\) has two elements, i.e.
-two channels, assuming perfect parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
+% Further, \(M_i = \left| \Cset_i \right| \) and \(N_j = \left| \Csetb_j \right| \) with \(i,j \in \Mset\).
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}
-    % \includestandalone[scale=1]{tikz/topology_general}
-    \vspace*{-0.5cm}
-    \caption{Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for a general case with \(M=4\) channels and \(N=4\) sub-problems.}
-    \label{fig:problem_splitting:problem_splitting_matrix}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}
+%     % \includestandalone[scale=1]{tikz/topology_general}
+%     \vspace*{-0.5cm}
+%     \caption{Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for a general case with \(M=4\) channels and \(N=4\) sub-problems.}
+%     \label{fig:problem_splitting:problem_splitting_matrix}
+% \end{figure}
 
@@
 \label{ssec:general_consensus_admm}
-Minimization problems with separable cost functions can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}.
-In the previous section we introduced the split cost function \eqref{eq:problem_splitting:cost_function} which we now set in the context of the general-form consensus problem
+We replace the cost function minimized in \eqref{eq:frequency_domain:min_prob} with the separable cost function 
+\begin{equation}
+    \tilde{J}(\hf) = \sum_{i \in \Mset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Mset} \wf_i^\herm \hat{\aRhof}_i \wf_i
+    \label{eq:problem_splitting:cost_function}
+\end{equation}
+where \(\wf_i\) is defined as the stacked vector of estimated frequency responses analogous to \(\hf\) and \(\hat{\aRhof}\) is the frequency-domain cross-relation matrix analogous to \(\Rf\) as introduced in \autoref{ssec:cross_rel}, however, both using the respective set of channels \(\Rset_i\) available at node \(i\).
+% If the channel subsets are proper \(\Cset_i \subset \Mset\), this leads to \(N\) sub-problems, each with smaller dimensions than the original centralized problem, reducing complexity.
+% The lowest dimensionality is attained when each \(\Cset_i\) has two elements, i.e.
+two channels, assuming perfect parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
+Minimization problems with separable cost functions as introduced here can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}
 \begin{align}
-    \operatorname{minimize} \quad &\sum_{i \in \Nset} \tilde{J}_i(\wf_i)\\
-    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Nset,\,j \in \Cset_i\\
+    \operatorname{minimize} \quad &\sum_{i \in \Rset} \tilde{J}_i(\wf_i)\\
+    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Mset,\,j \in \Rset_i\\
     &\hf^\herm \hf = 1
 \end{align}
-where \(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
-one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\) (cf.
-\autoref{fig:problem_splitting:problem_splitting_matrix}).
+where \(\wf_i\) will be referred to as the local variable, \(\hf\) as the global variable or consensus.
+\(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
+one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\).
 For brevity, the mapped global variables \((\tilde{\hf}_i)_j = \hf_{\mathcal{G}(i,j)}\) are introduced.
-The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces the consensus, i.e. a common solution taking into account data of all sub-problems.
+The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces the consensus, i.e.
+a common solution taking into account estimates of all nodes that share data of the same channel.
 
@@
 \begin{align}
-    \mathcal{L}_{\rho} (\wf,\hf,\uuf) &= \sum_{i \in \Nset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
+    \mathcal{L}_{\rho} (\wf,\hf,\uuf) &= \sum_{i \in \Rset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
 \vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|} \nonumber\\
@@
 \end{equation}
-where \(\mu\) (\(0  < \mu\leq 1\)) is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
-As this inverse is costly to compute, it is approximated by a diagonalized matrix
+where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
+The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so to reduce complexity, we introduce the approximation
 \begin{equation}
@@
 This results in a computationally inexpensive update step forcing the norm of the consensus to have unit value.
+\begin{todo}
+    Okay, so \eqref{eq:online_admm:consensus_update} is the major hurdle for selling this algorithm as distributed.
+This step still requires some sort of fusion center.
+But there must be a way to avoid that, maybe can be figured out this week?
+\end{todo}
 
@@
 \autoref{fig:perf_eval:NPM_over_time_exp2} shows the median of 30 Monte-Carlo runs for the two setups, which shows the proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error is not dependent on \(\zeta\).
+\begin{todo}
+    Rewrite this. Confusing.
+\end{todo}
 

### 2022-05-02 paper.tex
starting with toons suggestions

@@
 \begin{abstract}
-    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a sensor network with a fusion center.
+    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a wireless sensor network (WSN).
     The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
     The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
-    Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to a fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
-    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to fully centralized low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
+    Each node delivers estimates for the subset of channel frequency responses, which then are combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
+    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to fully centralized low-cost frequency-domain algorithms.
 \end{abstract}
@@
 \begin{todo}
-    cite
+    References
 \end{todo}
@@
     Which type of topology should be introduced. With fusion center? ring topology, "star" topology, depends on how consensus is introduced...\\
-    Make figure nicer.
+    Finish \autoref{fig:sensor_network:WSN}.
 \end{todo}
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}
-%     % \includestandalone[scale=1]{tikz/topology_general}
-%     \vspace*{-0.5cm}
-%     \caption{Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for a general case with \(M=4\) channels and \(N=4\) sub-problems.}
-%     \label{fig:problem_splitting:problem_splitting_matrix}
-% \end{figure}
-
 % #############################################################################
@@
 \(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
-one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\).
+one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\) (cf.
+\autoref{fig:problem_splitting:parameter_mapping}).
 For brevity, the mapped global variables \((\tilde{\hf}_i)_j = \hf_{\mathcal{G}(i,j)}\) are introduced.
@@
 a common solution taking into account estimates of all nodes that share data of the same channel.
+\begin{todo}
+    Combine \autoref{fig:sensor_network:WSN} and \autoref{fig:problem_splitting:parameter_mapping}.
+\end{todo}
+
+\begin{figure}
+    \centering
+    \includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}
+    % \includestandalone[scale=1]{tikz/topology_general}
+    \vspace*{-0.5cm}
+    \caption{Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for a network with \(M=4\) channels.}
+    \label{fig:problem_splitting:parameter_mapping}
+\end{figure}
 

### 2022-05-03 paper.tex
changes to distributed paper

@@
 \newcommand{\Mset}{\mathcal{M}}
-\newcommand{\Sset}{\mathcal{S}}
+\newcommand{\Tset}{\mathcal{T}}
 \newcommand{\Rset}{\mathcal{R}}
@@
     In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a wireless sensor network (WSN).
-    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
+    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system and a consensus fusion center.
     The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
@@
 % #############################################################################
-\subsection{Sensor Network}
-\label{ssec:sensor_network}
-We consider a WSN consisting of \(M\) sensor nodes, each acquiring a signal and equipped with a processing unit, and define the index set  \(i \in \Mset \triangleq \{1,\ldots,M\} \) representing these.
-Each node shares information with a set of neighboring nodes \(\Sset_i\) with \(i \in \Mset\), and receives information by a set of nodes \(\Rset_i\) with \(i \in \Mset\).
-% These connection links between nodes are represented as the \(M \times M\) network connection matrix \(\mtxb{C}\) with its elements defined as \(\mathrm{G}_{ij} = 1\) if the \(i\)-th node shares its signal information with the \(j\)-th node and \(\mathrm{G}_{ij} = 0\) otherwise.
-\autoref{fig:sensor_network:WSN} shows a network where each node shares its signal information with one or more neighbors.
-\begin{todo}
-    Which type of topology should be introduced. With fusion center? ring topology, "star" topology, depends on how consensus is introduced...\\
-    Finish \autoref{fig:sensor_network:WSN}.
-\end{todo}
-\begin{figure}
-    \centering
-    \includestandalone[trim={0 0 0 0},clip,height=2.5cm]{tikz/topology_general}
-    % \vspace*{-0.3cm}
-    \caption{WSN}
-    \label{fig:sensor_network:WSN}
-\end{figure}
-% \begin{figure}
-%     \centering
-%     \subfloat[][]{\includegraphics[trim={1.8cm 0 1.7cm 0},clip,scale=0.7]{images/parameter_mapping.pdf}}
-%     \subfloat[][]{\includestandalone[trim={0.65cm 0 0 0},clip,scale=0.7]{tikz/connection_matrix}}
-%     \subfloat[][]{\includestandalone[trim={0.6cm 0 0 0},clip,scale=0.6]{tikz/problem_splitting_matrix}}
-%     % \includestandalone[scale=1]{tikz/topology_general}
-%     \vspace*{-0.3cm}
-%     \caption{Problem splitting and parameter mapping for a general case with \(M=5\) channels and \(N=4\) sub-problems.
-(a) shows the mapping of the local estimate components \((\wf_i)_j\) to the global consensus components \((\hf)_j\) via \(\mathcal{G}(i,j)\), (b) \(\mtxb{G}\) with 1 (\(\blacksquare\)) and 0 (\(\square\)), (c) shows \(i,j\)-cross-relations used by sub-problems compared to full \(M\)-channel problem.}
-%     \label{fig:problem_splitting:problem_splitting_matrix}
-% \end{figure}
-
-% #############################################################################
 \subsection{Signal Model}
@@
     x_i(n)&x_i(n-1)&\ldots&x_i(n-L+1)
-\end{bmatrix}^{\T}\) aquired by the sensor nodes of the WSN.
-% \begin{align}
-%     \mtxb{s}(n) &= \begin{bmatrix}
-%         s(n)&s(n-1)&\ldots&s(n-2L+2)
-%     \end{bmatrix}^{\T}\\
-%     \x_i(n) &= \begin{bmatrix}
-%         x_i(n)&x_i(n-1)&\ldots&x_i(n-L+1)
-%     \end{bmatrix}^{\T}.
-% \end{align}
+\end{bmatrix}^{\T}\)
+where \(i \in \Mset \triangleq \{1, \ldots, M\} \).
 Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated to \(\mtxb{s}(n)\).
@@
 \begin{equation}
-    \x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n),
+    \x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n)
 \end{equation}
@@
 
-In the following section, we introduce a distributed adaptive algorithm to find a solution to this problem.
+% #############################################################################
+\subsection{Sensor Network}
+\label{ssec:sensor_network}
+\begin{todo}
+    is this even worth a subsection?
+\end{todo}
+
+We consider a WSN consisting of \(M\) sensor nodes and a consensus fusion center where each node acquires an output signal \(\x_i(n)\).
+We define a set \(\Tset_i\) for each node \(i\) with \(i \in \Mset\), which contains the indices of all nodes which have access to the signals \(\x_i(n)\), i.e.
+the signal information is transmitted to.
+Note that \(i \in \Tset_i\) for the purpose of simplifying notation in later sections, but evidently, no actual transmission is necessary in that case.
+Further, we define a set \(\Rset_i\) for each node with \(i \in \Mset\), which contains all indices of nodes which the node receives from.
+Furthermore, all nodes exchange information on the consensus with the fusion center.
+Network topologies with fusion centers come with the drawback of introducing the necessity of nodes transmitting additional data, however, the task of mitigating this will be addressed in future work.
+\autoref{fig:sensor_network:WSN} shows a network where each node shares its signal information with one or more neighbors.
+
+In the following section, we introduce a distributed adaptive algorithm to find a solution to \eqref{eq:frequency_domain:min_prob} utilizing the sensor nodes.
+
+\begin{figure}
+    \centering
+    \subfloat[][]{\includestandalone[trim={0 0 0 0},clip,width=0.23\columnwidth]{tikz/topology_general}\label{fig:sensor_network:WSN}}\hspace*{0.02\columnwidth}
+    \subfloat[][]{\includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=0.75\columnwidth]{images/parameter_mapping2.pdf}\label{fig:problem_splitting:parameter_mapping}}
+    \vspace*{-0.1cm}
+    \caption{(a) shows a minimal example of a network topology with 4 nodes (\(\circ\)) and consensus fusion center (\(\diamond\)).
+Black and grey arrows indicate exchange of signal information and consensus information respectively.
+(b) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
+    \label{fig:sensor_network:WSN_mapping}
+\end{figure}
 
@@
 where \(\wf_i\) is defined as the stacked vector of estimated frequency responses analogous to \(\hf\) and \(\hat{\aRhof}\) is the frequency-domain cross-relation matrix analogous to \(\Rf\) as introduced in \autoref{ssec:cross_rel}, however, both using the respective set of channels \(\Rset_i\) available at node \(i\).
-% If the channel subsets are proper \(\Cset_i \subset \Mset\), this leads to \(N\) sub-problems, each with smaller dimensions than the original centralized problem, reducing complexity.
-% The lowest dimensionality is attained when each \(\Cset_i\) has two elements, i.e.
-two channels, assuming perfect parallel processing, effectively reducing problem size from \(ML \times ML\) to \(2L \times 2L\).
-Minimization problems with separable cost functions as introduced here can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}
+Minimization problems with separable cost functions, as introduced here, can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}
 \begin{align}
-    \operatorname{minimize} \quad &\sum_{i \in \Rset} \tilde{J}_i(\wf_i)\\
+    \operatorname{minimize} \quad &\sum_{i \in \Mset} \tilde{J}_i(\wf_i)\\
     \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Mset,\,j \in \Rset_i\\
@@
 a common solution taking into account estimates of all nodes that share data of the same channel.
-\begin{todo}
-    Combine \autoref{fig:sensor_network:WSN} and \autoref{fig:problem_splitting:parameter_mapping}.
-\end{todo}
-
-\begin{figure}
-    \centering
-    \includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}
-    % \includestandalone[scale=1]{tikz/topology_general}
-    \vspace*{-0.5cm}
-    \caption{Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for a network with \(M=4\) channels.}
-    \label{fig:problem_splitting:parameter_mapping}
-\end{figure}
 
@@
 \begin{align}
-    \mathcal{L}_{\rho} (\wf,\hf,\uuf) &= \sum_{i \in \Rset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
+    \mathcal{L}_{\rho} (\wf,\hf,\uuf) &= \sum_{i \in \Mset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
 \vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|} \nonumber\\
-    \vphantom{\wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)} & \qquad \qquad \qquad \qquad \left.+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right)\label{eq:general_consensus_admm:lagrangian}
+    \vphantom{\wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)} & \qquad \qquad \qquad \qquad \left.+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right).\label{eq:general_consensus_admm:lagrangian}
 \end{align}
-% \begin{align}
-%     &\mathcal{L}_{\rho} (\wf,\hf,\uuf) = \sum_{i \in \Nset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right)\vphantom{+ \frac{\rho}{2} \left\| \wf_i - \tilde{\hf}_i \right\|^2} \right.\nonumber\\
-%     &\left.
-+ \left(\wf_i - \tilde{\hf}_i\right)^\herm \uuf_i + \left( \wf_i - \tilde{\hf}_i \right)^\herm \rho \I \left( \wf_i - \tilde{\hf}_i \right) \right).\label{eq:general_consensus_admm:lagrangian}
-% \end{align}
 The ADMM then consists of the steps:
@@
 \end{align}
-% \begin{align}
-%     &\wf_i^{k+1} = \underset{\wf_i}{\operatorname{argmin}} \left\{ \wf_i^\herm \hat{\aRhof}_i \wf_i + \uuf_i^{k\,\herm} \left(\wf_i - \tilde{\hf}_i^{k}\right) \vphantom{+ \left\| \wf_i - \tilde{\hf}_i^{k} \right\|^2}\right.\nonumber\\
-%     &\left.+ \left(\wf_i - \tilde{\hf}_i^{k}\right)^\herm \uuf_i^{k} + \left( \wf_i - \tilde{\hf}_i^{k} \right)^\herm \rho \I \left( \wf_i - \tilde{\hf}_i^{k} \right) \right\},\label{eq:general_consensus_admm:local}\\
-%     &\hf^{k+1} = \underset{\hf, \|\hf\| = a}{\operatorname{argmin}} \left\{ \sum_{i \in \Mset} \left( \tilde{\hf}_i^{\herm} \uuf_i^{k} + \uuf_i^{k\,\herm} \tilde{\hf}_i \vphantom{\frac{\rho}{2} \| \wf_i^{k+1} - \tilde{\hf}_i \|^2} \right.\right.\nonumber\\
-%     &\left.
-\qquad \qquad \vphantom{\sum_{i=1}^{M} pp } \left.+ \left( \wf_i^{k+1} - \tilde{\hf}_i \right)^\herm \rho \I \left( \wf_i^{k+1} - \tilde{\hf}_i \right)  \right) \right\},\label{eq:general_consensus_admm:global}\\
-%     &\uuf_i^{k+1} = \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right).\label{eq:general_consensus_admm:dual}
-% \end{align}
 As this is still denoted as an iterative algorithm, we will introduce the online/adaptive aspect of the proposed algorithm in the following.
@@
 \label{ssec:online_admm}
-We introduced the original problem in \eqref{eq:frequency_domain:null_space} with time-dependent data matrix.
+We introduced the original problem in \eqref{eq:frequency_domain:null_space} with a time-dependent data matrix.
 It therefore follows that the data term in \eqref{eq:general_consensus_admm:lagrangian} is also time-dependent, which from here on will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \hat{\aRhof}_i^{m} \wf_i\).
@@
 where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
-The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so to reduce complexity, we introduce the approximation
+The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce complexity, we introduce the approximation
 \begin{equation}
-    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \left( \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right)^{-1}\right\},
+    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \left( \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right)^{-1}\right\}
 \end{equation}
-similar to NMCFLMS \cite{huangClassFrequencydomainAdaptive2003}, which is straightforward to compute.
+which is straightforward to compute.
 
@@
 \begin{equation}
-    (\bar{\wf}^{m+1})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\wf_i^{m+1})_j,\quad g,i,j \in \Mset,
+    (\bar{\wf}^{m+1})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\wf_i^{m+1})_j,\quad g,i \in \Mset, \, j \in \Tset_g
 \end{equation}
@@
 \begin{equation}
-    (\bar{\uuf}^{m})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\uuf_i^{m})_j,\quad g,i,j \in \Mset.
+    (\bar{\uuf}^{m})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\uuf_i^{m})_j,\quad g,i \in \Mset, \, j \in \Tset_g
 \end{equation}
+with \(N_g = | \Tset_g |\) being the cardinality of the set.
 This results in a computationally inexpensive update step forcing the norm of the consensus to have unit value.
 \begin{todo}
-    Okay, so \eqref{eq:online_admm:consensus_update} is the major hurdle for selling this algorithm as distributed.
-This step still requires some sort of fusion center.
-But there must be a way to avoid that, maybe can be figured out this week?
+    Here could be added that the consensus update step doesnt have to be done each time step which would reduce the number of transmissions (obviously slows convergence).
+But that would be a claim that is not backed by convergence proof, only simulation results.
 \end{todo}

### 2022-05-04 paper.tex
ALMOST

@@
 % \excludecomment{attention}
-
-% Common variables
-\newcommand{\h}{\mtxb{h}}
-\newcommand{\x}{\mtxb{x}}
-\newcommand{\R}{\mtxb{R}}
-\newcommand{\w}{\mtxb{w}}
-\newcommand{\z}{\mtxb{z}}
-\newcommand{\uu}{\mtxb{u}}
-\newcommand{\aRho}{\mtxb{P}}
-\newcommand{\hf}{{\bm{h}}}
-\newcommand{\xf}{{\bm{x}}}
-\newcommand{\Rf}{{\bm{{R}}}}
-\newcommand{\wf}{{\bm{w}}}
-\newcommand{\zf}{{\bm{z}}}
-\newcommand{\uuf}{{\bm{u}}}
-\newcommand{\aRhof}{{\bm{{P}}}}
-\newcommand{\I}{\mtxb{I}}
-\newcommand{\Cset}{\mathcal{C}}
-\newcommand{\Mset}{\mathcal{M}}
-\newcommand{\Tset}{\mathcal{T}}
-\newcommand{\Rset}{\mathcal{R}}
 
@@
 \name{M.
-Blochberger\sthanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
-This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.
-956369.
+Blochberger\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
+This research received funding in part by the Research Foundation - Flanders (FWO) grant 12ZD622N as well as from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
+This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.
 Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}, F.
-Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, R.
-Ali, T.
-van Waterschoot, M.
+Elvander, R.
+Ali, M.
 Moonen, J.
 Østergaard, J.
-Jensen}
+Jensen, T.
+van Waterschoot}
 \address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
@@
     In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a wireless sensor network (WSN).
-    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system and a consensus fusion center.
-    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
-    Each node delivers estimates for the subset of channel frequency responses, which then are combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
-    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to fully centralized low-cost frequency-domain algorithms.
+    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
+    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels in a way that is determined by the network topology.
+    Each node delivers estimates for the subset of channel frequency responses, which then are combined into a consensus estimate per channel using general-form consensus ADMM in an adaptive updating scheme.
+    With numerical simulations, we show that it is possible to achieve convergence speeds and steady-state misalignment values comparable to fully centralized low-cost frequency-domain algorithms.
 \end{abstract}
@@
 
-The problem of blind system identification (BSI), which aims to estimate channel impulse responses of an unknown system without knowing the input signal, has been the subject of extensive research over recent decades.
+The problem of blind system identification (BSI), which aims to estimate channel responses of an unknown system without knowing the input signal, has been the subject of extensive research over recent decades.
 It was introduced in \cite{satoMethodSelfRecoveringEqualization1975} and various algorithms have been proposed since.
@@
 The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the BFGS method to estimate the Hessian of the problem.
-\begin{todo}
-    This is also a time-domain algorithm, should a comparison even be made? MCQN in plots
-\end{todo}
 
 The expanding field of distributed signal processing in wireless sensor networks (WSN) brought forward algorithms for distributed noise control, echo cancellation, or beamforming, however, research into the task of BSI is limited.
+\cite{bertrandApplicationsTrendsWireless2011b}
 \begin{todo}
@@
 These conditions are: (i) the channel transfer functions have no common zeros (i.e.
-are not co-prime), and (ii) the covariance matrix of the input signal \(\mtxb{s}(n)\) is of full rank (i.e.
+the polynomials are not co-prime), and (ii) the covariance matrix of the input signal \(\mtxb{s}(n)\) is of full rank (i.e.
 the signal has a number of modes \(\geq 2L+1\)).
@@
 Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g.
-\cite{huangAdaptiveMultichannelLeast2002} for a more thourough derivation) yields the system of equations
+\cite{huangAdaptiveMultichannelLeast2002} for a more thorough derivation) yields the system of equations
 \begin{equation}
@@
 and \(\h = \begin{bmatrix}
-    \h_1^\T & \cdots & \h_M^\T
+    \h_1^\T & \ldots & \h_M^\T
 \end{bmatrix}^\T\).
 Formulating the problem in the frequency domain, the derivation is analogous.
-We denote all frequency-domain variables in bold cursive (e.g.
+We denote all frequency-domain variables in bold italic (e.g.
 \(\Rf\)) compared to the time-domain bold upright (e.g \(\R\)).
@@
 \end{equation}
-where the \(M L \times M L\) matrix is recursivly estimated by \begin{equation}
+where \(\hf = \begin{bmatrix}
+    \hf_1^\T & \ldots & \hf_M^\T
+\end{bmatrix}^\T \) is a stacked vector of channel frequency responses and the \(M L \times M L\) matrix \(\Rf\) is recursively estimated by \begin{equation}
     \hat{\Rf}(m) = \eta \hat{\Rf}(m-1) + (1-\eta )\tilde{\Rf}(m).
 \end{equation}
-where \(\eta \in [0,1]\) is an exponential smoothing factor and \(\tilde{\Rf}(m)\) is constructed analogous to \eqref{eq:cross_rel:data_matrix}, however with covariance matrices replaced by instantaneous cross-spectrum matrices
+where \(\eta \in [0,1]\) is an exponential smoothing factor and \(\tilde{\Rf}(m)\) is constructed analogously to \eqref{eq:cross_rel:data_matrix}, however with covariance matrices replaced by instantaneous cross-spectrum matrices
 \begin{equation}
@@
     \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1}\label{eq:frequency_domain:overlap}
-\end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the discrete Fourier transform (DFT) matrices for sizes L and 2L respectively and \(
+\end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the discrete Fourier transform (DFT) matrices for sizes \(L\) and \(2L\) respectively and \(
     \mtxb{W}_{L \times 2L}^{01} = \begin{bmatrix}
@@
 
-Analogous to the time-domain formulation, the \(ML \times 1\) vector \(\hf\) is a stacked vector of complex-valued frequency responses.
-The null space problem in \eqref{eq:frequency_domain:null_space} can not be solved by computing the eigenvector corresponding to the zero-valued eigenvalue because, in the presence of noise, the system matrix \(\Rf\) is of full rank and may not have any.
-Therefore it is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002} with a non-triviality constraint to avoid the zero solution:
+Analogously to the time-domain formulation, the \(ML \times 1\) vector \(\hf\) is a stacked vector of complex-valued frequency responses.
+The null-space problem in \eqref{eq:frequency_domain:null_space} can not be solved by computing the eigenvector corresponding to the zero-valued eigenvalue because, in the presence of noise, the system matrix \(\Rf\) is of full rank and may not have any.
+Therefore it is best solved by posing it as a quadratic minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002} with a non-triviality constraint to avoid the zero solution:
 %  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
@@
 % #############################################################################
-\subsection{Sensor Network}
+\subsection{Wireless Sensor Network}
 \label{ssec:sensor_network}
-\begin{todo}
-    is this even worth a subsection?
-\end{todo}
 
-We consider a WSN consisting of \(M\) sensor nodes and a consensus fusion center where each node acquires an output signal \(\x_i(n)\).
-We define a set \(\Tset_i\) for each node \(i\) with \(i \in \Mset\), which contains the indices of all nodes which have access to the signals \(\x_i(n)\), i.e.
+We consider a WSN consisting of \(M\) sensors each acquiring an output signal \(\x_i(n)\).
+We define a set \(\Tset_i \subseteq \Mset\) for each node \(i\) with \(i \in \Mset\), which contains the indices of all nodes which have access to the signals \(\x_i(n)\), i.e.
 the signal information is transmitted to.
-Note that \(i \in \Tset_i\) for the purpose of simplifying notation in later sections, but evidently, no actual transmission is necessary in that case.
-Further, we define a set \(\Rset_i\) for each node with \(i \in \Mset\), which contains all indices of nodes which the node receives from.
-Furthermore, all nodes exchange information on the consensus with the fusion center.
-Network topologies with fusion centers come with the drawback of introducing the necessity of nodes transmitting additional data, however, the task of mitigating this will be addressed in future work.
-\autoref{fig:sensor_network:WSN} shows a network where each node shares its signal information with one or more neighbors.
+Further, we define a set \(\Rset_i \subseteq \Mset\) for each node with \(i \in \Mset\), which contains all indices of nodes from which the node receives signal information.
+Note that \(i \in \Tset_i\) and \(i \in \Rset_i\) for simplifying notation in later sections, but evidently, no actual transmission is necessary in that case, as the signal \(\x_i(n)\) is available locally at node \(i\).
+\autoref{fig:sensor_network:WSN_overview} shows a network where each node shares its signal information with one or more neighbors.
+For this work, we assume synchronicity of all nodes (i.e. no sampling rate offset) and perfect transmission of data with no time delay.
 
@@
     \centering
-    \subfloat[][]{\includestandalone[trim={0 0 0 0},clip,width=0.23\columnwidth]{tikz/topology_general}\label{fig:sensor_network:WSN}}\hspace*{0.02\columnwidth}
-    \subfloat[][]{\includegraphics[trim={0.3cm 0.25cm 1.7cm 0.0cm},clip,width=0.75\columnwidth]{images/parameter_mapping2.pdf}\label{fig:problem_splitting:parameter_mapping}}
+    \subfloat[][]{\includestandalone[trim={0 0 0 0},clip,width=0.2\columnwidth]{tikz/topology_general}\label{fig:sensor_network:WSN_overview}}\hspace*{0.05\columnwidth}
+    \subfloat[][]{\includestandalone[trim={0 0 0 0},clip,width=0.6\columnwidth]{tikz/topology_details}\label{fig:sensor_network:WSN_detail}}\\
+    \vspace*{-0.2cm}
+    \subfloat[][]{\includegraphics[trim={0.2cm 0.25cm 1.9cm 0.0cm},clip,width=\columnwidth]{images/parameter_mapping2.pdf}\label{fig:problem_splitting:parameter_mapping}}
     \vspace*{-0.1cm}
-    \caption{(a) shows a minimal example of a network topology with 4 nodes (\(\circ\)) and consensus fusion center (\(\diamond\)).
-Black and grey arrows indicate exchange of signal information and consensus information respectively.
-(b) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global consensus variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
+    \caption{(a) shows an example of a network topology with 4 nodes (\(\circ\)).
+Arrows indicate exchange of signal information.
+(b) visualizes the data transmitted between nodes \(i\) and \(j\) for each frame \(m\).
+(c) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
     \label{fig:sensor_network:WSN_mapping}
@@
 \label{ssec:general_consensus_admm}
+Defined by \(\Rset_i\), each node \(i \in \Mset\) has its own signal information and additionally signal information of its neighbors available.
+This is used to solve a BSI problem of the same form as in \eqref{eq:frequency_domain:min_prob}, which however only involves the subset of channels.
+We define the local variables \(\wf_i = \left[ \left\{ (\wf_i)_j^\T \right\}_{j \in \Rset_i} \right]^\T\), which is a stacked vector of locally estimated frequency responses (cf.
+\autoref{fig:problem_splitting:parameter_mapping}).
+Further, the global variable \(\hf = \begin{bmatrix}
+    \hf_1^\T & \ldots & \hf_M^\T
+\end{bmatrix}^\T\) is the stacked vector of all \(M\) channel response consensus variables.
+Lastly, we define the matrix \(\hat{\aRhof}_i\), which is the frequency-domain cross-relation matrix analogous to \(\hat{\Rf}\) as introduced in \autoref{ssec:cross_rel}, however only using the signals \(\x_j\) with \(j \in \Rset_i\).
+
 We replace the cost function minimized in \eqref{eq:frequency_domain:min_prob} with the separable cost function 
 \begin{equation}
-    \tilde{J}(\hf) = \sum_{i \in \Mset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Mset} \wf_i^\herm \hat{\aRhof}_i \wf_i
+    \tilde{J}(\wf) = \sum_{i \in \Mset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Mset} \wf_i^\herm \hat{\aRhof}_i \wf_i.
     \label{eq:problem_splitting:cost_function}
 \end{equation}
-where \(\wf_i\) is defined as the stacked vector of estimated frequency responses analogous to \(\hf\) and \(\hat{\aRhof}\) is the frequency-domain cross-relation matrix analogous to \(\Rf\) as introduced in \autoref{ssec:cross_rel}, however, both using the respective set of channels \(\Rset_i\) available at node \(i\).
+with \(\wf \triangleq (\wf_1,\ldots,\wf_M)\) as the local stacked estimates.
 Minimization problems with separable cost functions, as introduced here, can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}
 \begin{align}
-    \operatorname{minimize} \quad &\sum_{i \in \Mset} \tilde{J}_i(\wf_i)\\
-    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Mset,\,j \in \Rset_i\\
-    &\hf^\herm \hf = 1
+    \underset{\wf,\,\hf}{\operatorname{minimize}} \quad &\sum_{i \in \Mset} \tilde{J}_i(\wf_i)\label{eq:general_consensus_admm:min_prob}\\
+    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Mset,\,j \in \Rset_i\label{eq:general_consensus_admm:eq_constraint}\\
+    &\hf^\herm \hf = 1\label{eq:general_consensus_admm:norm_constraint}
 \end{align}
-where \(\wf_i\) will be referred to as the local variable, \(\hf\) as the global variable or consensus.
-\(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
-one of the frequency responses in the stacked vector, to the corresponding global variable components \((\hf)_g\) (cf.
+where \(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
+one of the frequency responses in the stacked vector, to the corresponding global variable components \(\hf_j\) (cf.
 \autoref{fig:problem_splitting:parameter_mapping}).
 For brevity, the mapped global variables \((\tilde{\hf}_i)_j = \hf_{\mathcal{G}(i,j)}\) are introduced.
-The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces the consensus, i.e.
+This defines \(\tilde{\hf}_i = \left[ \left\{ \hf_j^\T \right\}_{j \in \Rset_i} \right]^\T\).
+The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces consensus, i.e.
 a common solution taking into account estimates of all nodes that share data of the same channel.
@@
 \begin{align}
-    \mathcal{L}_{\rho} (\wf,\hf,\uuf) &= \sum_{i \in \Mset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
-\vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|} \nonumber\\
-    \vphantom{\wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)} & \qquad \qquad \qquad \qquad \left.+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right).\label{eq:general_consensus_admm:lagrangian}
+    \mathcal{L}_{\rho} &(\wf,\hf,\uuf) = \sum_{i \in \Mset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
+\vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2} \nonumber\\
+    \vphantom{\wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)} & \qquad \qquad \qquad \qquad \left.
++ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right)\label{eq:general_consensus_admm:lagrangian}
 \end{align}
-The ADMM then consists of the steps:
+where \(\uuf \triangleq (\uuf_1,\ldots,\uuf_M)\) are the stacked local dual variables (Lagrange multipliers) \(\uuf_i = \left[ \left\{ (\uuf_i)_j^{\T} \right\}_{j \in \Rset_i} \right]^\T\) with \((\uuf_i)_j\) denoting the dual variable for channel \(j\) at node \(i\).
+These variables follow from the equality constraints in \eqref{eq:general_consensus_admm:eq_constraint}.
+% The local variables \(\wf\) and global variable \(\hf\) are as introduced
+The ADMM then consists of the steps \cite{boydDistributedOptimizationStatistical2011}:
 \begin{align}
@@
 \end{align}
-As this is still denoted as an iterative algorithm, we will introduce the online/adaptive aspect of the proposed algorithm in the following.
+where \(k\) is the iteration index. Evidently, this is an iterative algorithm, therefore we will introduce the online/adaptive aspect of the proposed algorithm in the following.
 
@@
 \label{ssec:online_admm}
-We introduced the original problem in \eqref{eq:frequency_domain:null_space} with a time-dependent data matrix.
-It therefore follows that the data term in \eqref{eq:general_consensus_admm:lagrangian} is also time-dependent, which from here on will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \hat{\aRhof}_i^{m} \wf_i\).
-A thorough overview of time-varying data terms in ADMM can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as ``Online-ADMM".
+We introduced the original problem in \eqref{eq:frequency_domain:null_space} with a time-dependent estimate \(\hat{\Rf(m)}\) of the matrix \(\Rf(m)\).
+It therefore follows that the data term in \eqref{eq:general_consensus_admm:lagrangian} can also be considered time-dependent, which from here on will be denoted with the additional superscript time index \(m\) as \(\wf_i^\herm \hat{\aRhof}_i^{m} \wf_i\).
+A thorough review of ADMM with time-varying data terms can be found in \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014} where it is referred to as ``Online-ADMM".
+We transform the iterative batch processing method \eqref{eq:general_consensus_admm:local}-\eqref{eq:general_consensus_admm:dual} into an adaptive one by computing only a (small) finite number of iterations with each time-frame-\(m\) specific data term.
+Here specifically, we apply one iteration per time frame, which manifests itself as simply replacing the iteration index \(k\) with the time frame index \(m\).
 
-We transform the iterative batch processing method \eqref{eq:general_consensus_admm:local}-\eqref{eq:general_consensus_admm:dual} into an adaptive one by computing only a (small) finite number of iterations with each time-frame-\(m\) specific data term.
-Here specifically, we apply one iteration per time frame, which manifests itself as simply replacing the iteration index \(k\) with the time index \(m\)
-
-The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the update step 
+The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the update step as
 \begin{equation}
@@
 \end{equation}
-where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the inverse Hessian of the problem.
-The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce complexity, we introduce the approximation
+where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the regularized inverse Hessian of the problem.
+The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce computational complexity, we introduce the approximation
 \begin{equation}
-    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \left( \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right)^{-1}\right\}
+    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1}
 \end{equation}
@@
 
-For the update step of the consensus variable \(\hf\), it may be readily verified (cf.
+% The global variable \(\hf\), a stacked vector of the \(M\) single-channel consensus variables \(\hf_i\), is updated by a distributed update.
+It may be readily verified (cf. \cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by an update step which computes
+\begin{equation}
+    \hf_i^{m+1} = \frac{\bar{\hf}_i^{m+1}}{\sqrt{\sum_{j \in \Tset_i} \phi_i}}\label{eq:online_admm:consensus_update}
+\end{equation}
+for each node \(i \in \Mset\) with the local unnormalized consensus
+\begin{equation}
+    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}.
+\end{equation}
+and the squared norm \(\phi_i = \|\bar{\hf}_i^{m+1}\|^2\).
+Here, \(\bar{\wf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\wf_j)_i\) and \(\bar{\uuf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uuf_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) computed at node \(i\).
+The values of all \(\phi_i\), \(i \in \Mset\) are transmitted and relayed through the network until can compute the denominator in \eqref{eq:online_admm:consensus_update}.
+
+The dual variables are straightforward to compute as
+\begin{equation}
+    \uuf_i^{m+1} = \uuf_i^{m} + \rho \left( \wf_i^{m+1} - \tilde{\hf}_i^{m+1} \right).\label{eq:online_admm:dual_update}
+\end{equation}
+
+The computations of local, consensus and dual variables, in \eqref{eq:online_admm:local_update}, \eqref{eq:online_admm:consensus_update} and \eqref{eq:online_admm:dual_update} respectively, require data transmitted by other nodes (cf.
+\autoref{fig:sensor_network:WSN_detail}).
+For this paper, we assume that all transmissions are done instantaneously whenever variables are required by neighboring nodes.
+
+% \autoref{alg:dbsi} presents the full algorithm including inter-node transmissions.
+
+% \begin{algorithm}
+%     \caption{Distributed BSI with ADMM}\label{alg:dbsi}
+%     \begin{algorithmic}
+%         \For {\(m=0,1,2,...\)}
+%             \For{\(i \in \Mset\)}
+%                 \State Acquire signal vector \(x_i^{(m)}\)
+%                 \ForAll{\(j \in \Tset_i\)}
+%                     \State Send \(x_i^{(t)},\bar{h}_i^{(t)},\bar{y}_i^{(t)}\) to node \(j\)
+%                 \EndFor
+%                 \ForAll{\(k \in \mathcal{R}_i\)}
+%                     \State Receive \(x_{k}^{(t)},\bar{h}_{k}^{(t)},\bar{y}_{k}^{(t)}\) from node \(k\)
+%                 \EndFor
+%                 \State Update \(\phi_i^{(t+1)} \leftarrow \phi_i^{(t)}\) using \eqref{eq:admm_local}
+%                 \State Update \(\gamma_i^{(t+1)} \leftarrow \gamma_i^{(t)}\) using \eqref{eq:admm_consensus}
+%                 \State Update \(\lambda_i^{(t+1)} \leftarrow \lambda_i^{(t)}\) using \eqref{eq:admm_dual}
+%                 \ForAll{\(k \in \mathcal{R}_i\)}
+%                     \State Send \(\hat{h}_{ki}^{(t)},y_{ki}^{(t)}\) to node \(k\)
+%                 \EndFor
+%                 \ForAll{\(j \in \Tset_i\)}
+%                     \State Receive \(\hat{h}_{ij}^{(t)},y_{ij}^{(t)}\) to node \(j\)
+%                 \EndFor
+%             \EndFor
+%         \EndFor
+%     \end{algorithmic}
+% \end{algorithm}
+
+% For the update step of the consensus variable \(\hf\), it may be readily verified (cf.
 \cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by
-\begin{equation}
-    \hf^{m+1} = \frac{\bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} }{\left\| \bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} \right\|}.\label{eq:online_admm:consensus_update}
-\end{equation}
-where the \(M L \times 1\) vectors \(\bar{\wf}^{m+1}, \bar{\uuf}^{m+1}\) are computed as the mapped averages
-\begin{equation}
-    (\bar{\wf}^{m+1})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\wf_i^{m+1})_j,\quad g,i \in \Mset, \, j \in \Tset_g
-\end{equation}
-and
-\begin{equation}
-    (\bar{\uuf}^{m})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\uuf_i^{m})_j,\quad g,i \in \Mset, \, j \in \Tset_g
-\end{equation}
-with \(N_g = | \Tset_g |\) being the cardinality of the set.
-This results in a computationally inexpensive update step forcing the norm of the consensus to have unit value.
-\begin{todo}
-    Here could be added that the consensus update step doesnt have to be done each time step which would reduce the number of transmissions (obviously slows convergence).
-But that would be a claim that is not backed by convergence proof, only simulation results.
-\end{todo}
+% \begin{equation}
+%     \hf^{m+1} = \frac{\bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} }{\left\| \bar{\wf}^{m+1} + \frac{1}{\rho} \bar{\uuf}^{m} \right\|}.\label{eq:online_admm:consensus_update}
+% \end{equation}
+% where the \(M L \times 1\) vectors \(\bar{\wf}^{m+1}, \bar{\uuf}^{m+1}\) are computed as the mapped averages
+% \begin{equation}
+%     (\bar{\wf}^{m+1})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\wf_i^{m+1})_j,\quad g,i \in \Mset, \, j \in \Tset_g
+% \end{equation}
+% and
+% \begin{equation}
+%     (\bar{\uuf}^{m})_g = \frac{1}{N_g} \sum_{\mathcal{G}(i,j)=g} (\uuf_i^{m})_j,\quad g,i \in \Mset, \, j \in \Tset_g
+% \end{equation}
+% with \(N_g = | \Tset_g |\) being the cardinality of the set.
+% This results in a computationally inexpensive update step forcing the norm of the consensus to have unit value.
 
@@
     \centering
-    \subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_time_SNR10.png}\label{fig:perf_eval:NPM_over_time_SNR10}}\\
+    \hspace*{-0.2cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_time_SNR10.png}\label{fig:perf_eval:NPM_over_time_SNR10}}\\
     \vspace*{-0.3cm}
-    \subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_SNR_L64_M5.png}\label{fig:perf_eval:NPM_over_SNR_L64_M5}}
+    \hspace*{-0.2cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_SNR_L64_M5.png}\label{fig:perf_eval:NPM_over_SNR_L64_M5}}
     \vspace*{-0.2cm}
@@
 As an error measure, we use the normalized projection misalignment (NPM) \cite{huangClassFrequencydomainAdaptive2003}
+% \begin{equation}
+%     \text{NPM}(m) = 20\,\log_{10} \left(\frac{\left\| \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m) \right\|_2}{\left\|\h(m)\right\|_2} \right)
+% \end{equation}
 \begin{equation}
-    \text{NPM}(m) = 20\,\log_{10} \left(\frac{\left\| \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m) \right\|_2}{\left\|\h(m)\right\|_2} \right)
+    \text{NPM}(m) = 20\,\log_{10} \left(\left\| \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m) \right\| / \left\|\h(m)\right\| \right)
 \end{equation}
 where \(\h\) is the stacked vector of impulse response estimates (cf.
-\autoref{ssec:cross_rel}), which are the inversely Fourier-transformed estimated frequency responses stacked in \(\hf\) and \(\h_{\text{t}}\) is the ground truth.
+\autoref{ssec:cross_rel}), which are the inversely Fourier-transformed estimated frequency responses \(\hf_i\) stacked in \(\hf\) and \(\h_{\text{t}}\) is the ground truth.
 The signal-to-noise ratio (SNR) for the simulations is defined as
@@
 
-The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-channel system (\(M=5,\, N=5\)).
-The impulse responses are drawn from a Normal distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.
+The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)).
+The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.
 The step sizes are hand tuned for similar convergence speed: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
-\autoref{fig:perf_eval:NPM_over_time_exp1} shows the median of 30 Monte-Carlo runs where the averaged NPM of the last \(100\) frames is plotted.
+\autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM of 30 Monte-Carlo runs over frame index \(m\).
+\autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median of 30 Monte-Carlo runs where the averaged NPM of \(100\) frames after convergence is plotted.
 It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
+The choice to present the median is based on the fact that randomly generated impulse responses may have close common zeros diminishing identifyability (for all algorithms) \cite{naylorNearCommonZerosBlind2008}, here then considered outliers.
 
@@
     \centering
-    \hspace*{-0.2cm}\subfloat[][\(M\!=\!4,P\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
-    % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4,N\!=\!4\)]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}
-    %     \put(54,48){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.5]{tikz/connection_matrix_eval}}
-    % \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
-    \hspace*{-0.0cm}\subfloat[][\(M\!=\!8,N\!=\!8\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
+    % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
+    \hspace*{-0.2cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}
+        \put(57,42.5){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.6]{tikz/topology_inset_simulation}}
+    \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
+    \hspace*{-0.0cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
     \vspace*{-0.2cm}
-    \caption{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of the sub-problem overlap \(\zeta\) for \(\text{SNR}=20\,\text{dB}\).}
+    \caption[Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\)]{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\) for \(\text{SNR}=20\,\text{dB}\).
+NPM is plotted for systems of (a) 4 nodes/channels and (b) 8 nodes/channels.
+The inset of (a) shows the base ring topology (black arrows) and all other possible connections (dashed black arrows).}
     \label{fig:perf_eval:NPM_over_time_exp2}
@@
 The second simulation is a small-scale assessment of the influence of the overlap of sub-problems.
-Two base scenarios, \(M=4,\,N=4\) and \(M=8,\,N=8\), are evaluated using short (\(L=16\)) random impulse responses and different values for the sub-problem overlap parameter \(\zeta\) which is defined as the ratio of ones to zeros of only considering elements of \(\mtxb{G}\) that are not part of the main diagonal, superdiagonal and the first element of the last row (marked gray on the inset of \autoref{fig:perf_eval:NPM_over_time_M4}).
-Random patterns satisfying this definition for \(\zeta \in \{0.0,\,0.25,\,0.5,\,0.75\}\) are generated.
-\autoref{fig:perf_eval:NPM_over_time_exp2} shows the median of 30 Monte-Carlo runs for the two setups, which shows the proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error is not dependent on \(\zeta\).
-\begin{todo}
-    Rewrite this. Confusing.
-\end{todo}
+Two base scenarios, \(M=4\) and \(M=8\) are evaluated using short (\(L=16\)) random impulse responses and with semi-random topologies.
+Each topology is generated by forming a ring topology as marked with solid arrows on the inset of \autoref{fig:perf_eval:NPM_over_time_M4} and additionally randomly selecting a defined number of connections from all remaining possible connections, marked with dashed arrows.
+The parameter \(\zeta\) is defined as the number of randomly selected connections to possible connections (excluding the ring topology).
+Topologies satisfying this definition for \(\zeta \in \{0.0,\,0.25,\,0.5,\,0.75\}\) were generated.
+\autoref{fig:perf_eval:NPM_over_time_exp2} shows the median of 30 Monte-Carlo runs for the two setups, which suggests a proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error appears not dependent on \(\zeta\).
+\begin{attention}
+    Some plots and values will change slightly.
+\end{attention}
 
@@
 \label{sec:conclusion}
-In this paper, an adaptive ADMM algorithm for blind system identification was developed.
-The algorithm separates the BSI problem into lower-dimensional sub-problems to reduce computational complexity and allows for parallel or distributed processing while maintaining steady-state error performance and convergence speed.
-Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms and that steady-state performance is not affected by separating the BSI problem into sub-problems while convergence speed is.
+In this paper, a distributed adaptive algorithm for blind system identification using ADMM in the context of sensor networks was developed.
+Each node in a WSN solves a BSI sub-problem estimating channel responses using signal data from neighboring nodes to form the cross-relation problem with a subset of channels.
+Through 
+\begin{todo}
+    FINISH
+\end{todo}
+%  while maintaining steady-state error performance and convergence speed.
+% Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms and that steady-state performance is not affected by separating the BSI problem into sub-problems while convergence speed is.
 

### 2022-05-04 tikz/topology_details.tex
ALMOST

% Tikz File 'topology_details.tex'
\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz,amsmath,amssymb}
\input{../preamble.tex}
\usetikzlibrary{arrows,snakes,backgrounds}
\begin{document}
    \begin{tikzpicture}[->,shorten >=1pt,auto,semithick, scale=1]
        \tikzstyle{admmnode}=[
            circle,
            draw=black,
            thick,
            text=black,
            minimum size=0.7cm
        ]

        \node[] (C)  at (-2.2,0){\(\cdots\)};

        \node[admmnode, fill=gray!15] (A) at (-1.5,0){\(i\)};
        % \node[draw,text centered] at (-3,-1){\(\mathcal{T}_i = \{\ldots,j,\ldots\}\)};

        \node[admmnode, fill=gray!15] (B) at (1.5,0){\(j\)};
        % \node[draw,text centered] at (3,-1){\(\mathcal{R}_j = \{\ldots,i,\ldots\}\)};

        \node[] (D)  at (2.2,0){\(\cdots\)};

        \draw[-stealth,black, line width=1.2] (A) to[bend left=20] node[above, pos=0.5, sloped, scale=1]{\(\x_i, \{\phi_1,\ldots,\phi_i\}\)}  (B);

        \draw[stealth-,gray, line width=1.2] (A) to[bend right=20] node[below, pos=0.5, sloped,scale=1]{\((\wf_j)_i,(\uuf_j)_i,\{\phi_1,\ldots,\phi_M\}\)}  (B);

    \end{tikzpicture}
\end{document}

### 2022-05-05 paper.tex
waiting for simulation to finish

@@
 This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
-This research received funding in part by the Research Foundation - Flanders (FWO) grant 12ZD622N as well as from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
+This research received funding in part from the Research Foundation - Flanders (FWO) grant 12ZD622N as well as from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
 This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.
@@
 
-The expanding field of distributed signal processing in wireless sensor networks (WSN) brought forward algorithms for distributed noise control, echo cancellation, or beamforming, however, research into the task of BSI is limited.
-\cite{bertrandApplicationsTrendsWireless2011b}
-\begin{todo}
-    References
-\end{todo}
+The expanding field of distributed signal processing in wireless sensor networks (WSN) brought forward algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, or beamforming \cite{6663655,9670697}, however, research into the task of BSI is limited.
 While there exist time-domain algorithms as introduced in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, they do not pose apt comparisons to the frequency-domain algorithm being proposed.
@@
 
+The major types of network topologies for distributed signal processing can be distinguished by the way information is shared within the network.
+In a centralized or star topology, where nodes transmit their signals to a dedicated device (fusion center), the processing happens (partly) centralized.
+This has drawbacks, such as the dependence on one or a small number of dedicated devices and a potentially large number of signals to be processed on these devices.
+Therefore, it is advantageous to consider ad-hoc network topologies, as we do in this paper, where nodes only communicate with their respective neighbors.
+We refer the reader to \cite{bertrandApplicationsTrendsWireless2011b} for a more detailed review of WSNs and their topologies.
+
 We consider a WSN consisting of \(M\) sensors each acquiring an output signal \(\x_i(n)\).
@@
 (b) visualizes the data transmitted between nodes \(i\) and \(j\) for each frame \(m\).
-(c) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global variable components \(({\hf})_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
+(c) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global variable components \(\hf_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
     \label{fig:sensor_network:WSN_mapping}
@@
 Defined by \(\Rset_i\), each node \(i \in \Mset\) has its own signal information and additionally signal information of its neighbors available.
-This is used to solve a BSI problem of the same form as in \eqref{eq:frequency_domain:min_prob}, which however only involves the subset of channels.
+This is used to solve a BSI sub-problem of the same form as in \eqref{eq:frequency_domain:min_prob}, which however only involves the subset of channels.
 We define the local variables \(\wf_i = \left[ \left\{ (\wf_i)_j^\T \right\}_{j \in \Rset_i} \right]^\T\), which is a stacked vector of locally estimated frequency responses (cf.
@@
 It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
-The choice to present the median is based on the fact that randomly generated impulse responses may have close common zeros diminishing identifyability (for all algorithms) \cite{naylorNearCommonZerosBlind2008}, here then considered outliers.
+The choice to present the median is based on the fact that randomly generated impulse responses may have close common zeros diminishing identifiability (for all algorithms) \cite{naylorNearCommonZerosBlind2008}, here then considered outliers.
 
@@
 Topologies satisfying this definition for \(\zeta \in \{0.0,\,0.25,\,0.5,\,0.75\}\) were generated.
-\autoref{fig:perf_eval:NPM_over_time_exp2} shows the median of 30 Monte-Carlo runs for the two setups, which suggests a proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error appears not dependent on \(\zeta\).
+\autoref{fig:perf_eval:NPM_over_time_M4} and \autoref{fig:perf_eval:NPM_over_time_M8} show the median NPM (30 Monte-Carlo runs) for \(M=4\) and \(M=8\) respectively.
+The plots suggests a proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error appears to be not dependent on \(\zeta\).
 \begin{attention}
-    Some plots and values will change slightly.
+    Some plots and values will change slightly and I will fit it onto 4 pages.
 \end{attention}
@@
 In this paper, a distributed adaptive algorithm for blind system identification using ADMM in the context of sensor networks was developed.
-Each node in a WSN solves a BSI sub-problem estimating channel responses using signal data from neighboring nodes to form the cross-relation problem with a subset of channels.
-Through 
-\begin{todo}
-    FINISH
-\end{todo}
-%  while maintaining steady-state error performance and convergence speed.
-% Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms and that steady-state performance is not affected by separating the BSI problem into sub-problems while convergence speed is.
+The BSI problem is distributed amongst the nodes by exploiting the separability of the cross-relation problem formulation which leads to node-wise sub-problems using signal information of a node's neighborhood.
+The nodes solve the subproblem and transmit estimates to their respective neighbors which are combined into consensus estimates,
+Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms.
+Further they suggest that steady-state performance is not affected by the separation of the full BSI problem into node-wise sub-problems while convergence speed is.
 

### 2022-05-05 paper.tex
waiting for simulation to finish

@@
 Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms.
-Further they suggest that steady-state performance is not affected by the separation of the full BSI problem into node-wise sub-problems while convergence speed is.
+Further, they suggest that steady-state performance is not affected by the separation of the full BSI problem into node-wise sub-problems while convergence speed is.
 

### 2022-05-05 paper.tex
waiting for simulation to finish

@@
 Here, \(\bar{\wf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\wf_j)_i\) and \(\bar{\uuf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uuf_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) computed at node \(i\).
-The values of all \(\phi_i\), \(i \in \Mset\) are transmitted and relayed through the network until can compute the denominator in \eqref{eq:online_admm:consensus_update}.
+The values of all \(\phi_i\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
 
@@
 
-The second simulation is a small-scale assessment of the influence of the overlap of sub-problems.
+The second simulation is a small-scale assessment of the influence of the number of connections within the WSN.
 Two base scenarios, \(M=4\) and \(M=8\) are evaluated using short (\(L=16\)) random impulse responses and with semi-random topologies.

### 2022-05-05 paper.tex
jans comments included

@@
 \documentclass{article}
-\usepackage[preprint]{spconfa4}
+\usepackage{spconfa4}
 \usepackage{amsmath,graphicx}
@@
 The normalized multi-channel frequency-domain LMS (NMCFLMS) \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} algorithm for instance is an efficient algorithm utilizing the fast Fourier transform (FFT) which has been extended to include constraints to improve robustness to noise and performance on acoustic impulse responses (RNMCFLMS \cite{huNoiseRobustBlind2015}, \(l_p\)-RNMCFLMS \cite{heNoiseRobustFrequencyDomain2018}, phase-constrained-\(l_p\)-RNMCFLMS \cite{joRobustBlindMultichannel2021}).
-The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the BFGS method to estimate the Hessian of the problem.
+The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the Broyden–Fletcher–Goldfarb–Shanno (BFGS) \cite{brodlie1977assessment} method to estimate the Hessian of the problem.
 
@@
 We consider a WSN consisting of \(M\) sensors each acquiring an output signal \(\x_i(n)\).
-We define a set \(\Tset_i \subseteq \Mset\) for each node \(i\) with \(i \in \Mset\), which contains the indices of all nodes which have access to the signals \(\x_i(n)\), i.e.
-the signal information is transmitted to.
+We define a set \(\Tset_i \subseteq \Mset\) for each node \(i\) with \(i \in \Mset\), which contains the indices of the set of nodes which signal \(\x_i(n)\) is transmitted to.
 Further, we define a set \(\Rset_i \subseteq \Mset\) for each node with \(i \in \Mset\), which contains all indices of nodes from which the node receives signal information.
@@
 \begin{equation}
-    \tilde{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1}
+    \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1}
 \end{equation}
@@
 \begin{equation}
-    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}.
+    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}
 \end{equation}
@@
 \autoref{fig:sensor_network:WSN_detail}).
-For this paper, we assume that all transmissions are done instantaneously whenever variables are required by neighboring nodes.
+For this paper, we assume that all transmissions are done instantaneously and error-free whenever variables are required by neighboring nodes.
 
@@
 Each topology is generated by forming a ring topology as marked with solid arrows on the inset of \autoref{fig:perf_eval:NPM_over_time_M4} and additionally randomly selecting a defined number of connections from all remaining possible connections, marked with dashed arrows.
-The parameter \(\zeta\) is defined as the number of randomly selected connections to possible connections (excluding the ring topology).
+The parameter \(\zeta\) is defined as the ratio of randomly selected connections to possible connections (excluding the ring topology).
 Topologies satisfying this definition for \(\zeta \in \{0.0,\,0.25,\,0.5,\,0.75\}\) were generated.
@@
 The BSI problem is distributed amongst the nodes by exploiting the separability of the cross-relation problem formulation which leads to node-wise sub-problems using signal information of a node's neighborhood.
-The nodes solve the subproblem and transmit estimates to their respective neighbors which are combined into consensus estimates,
+The nodes solve the subproblem and transmit estimates to their respective neighbors which are combined into consensus estimates.
 Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms.

### 2022-05-06 paper.tex
only plots left

@@
 % ---------------
-\name{M.
+% \name{M.
 Blochberger\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
@@
 van Waterschoot}
-\address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
+% \address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
+
+\twoauthors{M. Blochberger, F. Elvander, R. Ali, M. Moonen, T. van Waterschoot
+    \thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
+This research received funding in part from the Research Foundation - Flanders (FWO) grant 12ZD622N as well as from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
+This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.
+Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}}
+        {KU Leuven\\Department of Electrical Engineering (ESAT), STADIUS\\3001 Leuven, Belgium}
+        {J. Østergaard}
+        {Aalborg University\\
+        Department of Electronic Systems\\
+        9220 Aalborg, Denmark}
 %
@@
 In this paper, we use the general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} to distribute and solve the optimization problem posed by the task.
-We separate the inter-channel cross-relations of the BSI problem according to the network's topology, i.e.
-each node solves a sub-problem using data from its network neighbors, and the entirety of connected nodes subsequently reaches a consensus for the channel frequency responses.
+We separate the inter-channel cross-relations of the BSI problem according to the network's topology, i.e., each node solves a sub-problem using data from its network neighbors, and the entirety of connected nodes subsequently reaches a consensus for the channel frequency responses.
 The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
@@
 where \(i \in \Mset \triangleq \{1, \ldots, M\} \).
-Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated to \(\mtxb{s}(n)\).
+Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated with \(\mtxb{s}(n)\).
 The signal model is described by
 \begin{equation}
-    \x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n)
+    \x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n),
 \end{equation}
@@
 This can be achieved by exploiting the relative channel information when more than one channel is available, and the identifiability conditions \cite{guanghanxuLeastsquaresApproachBlind1995} are satisfied.
-These conditions are: (i) the channel transfer functions have no common zeros (i.e.
-the polynomials are not co-prime), and (ii) the covariance matrix of the input signal \(\mtxb{s}(n)\) is of full rank (i.e.
-the signal has a number of modes \(\geq 2L+1\)).
+These conditions are: (i) the channel transfer functions have no common zeros (i.e., the polynomials are not co-prime), and (ii) the covariance matrix of the input signal \(\mtxb{s}(n)\) is of full rank (i.e., the signal has a number of modes \(\geq 2L+1\)).
 
-The fundamental equality of this approach in the noiseless case \(\mtxb{v}_i(n) = 0\), is 
+The fundamental equality of this approach in the noiseless case \(\mtxb{v}_i(n) = 0\) is 
 \begin{equation}
@@
 which states that the channel output signal convolved with the impulse response of another is equal to the vice-versa as follows from the commutativity property of the convolution.
-Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g.
-\cite{huangAdaptiveMultichannelLeast2002} for a more thorough derivation) yields the system of equations
+Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g., \cite{huangAdaptiveMultichannelLeast2002} for a more detailed derivation) yields the system of equations
 \begin{equation}
-    \R \h = \bm{0} \label{eq:cross_rel:null_space}\\
+    \R \h = \bm{0}, \label{eq:cross_rel:null_space}\\
 \end{equation}
-where \(\R\) is an \(M L \times M L\) matrix given by:
+where \(\R\) is an \(M L \times M L\) matrix given by
 \begin{equation}
@@
 \begin{equation}
-    \Rf \hf = \bm{0} \label{eq:frequency_domain:null_space}\\
+    \Rf \hf = \bm{0}, \label{eq:frequency_domain:null_space}\\
 \end{equation}
@@
 \end{bmatrix}^\T \) is a stacked vector of channel frequency responses and the \(M L \times M L\) matrix \(\Rf\) is recursively estimated by \begin{equation}
-    \hat{\Rf}(m) = \eta \hat{\Rf}(m-1) + (1-\eta )\tilde{\Rf}(m).
+    \hat{\Rf}(m) = \eta \hat{\Rf}(m-1) + (1-\eta )\tilde{\Rf}(m),
 \end{equation}
-where \(\eta \in [0,1]\) is an exponential smoothing factor and \(\tilde{\Rf}(m)\) is constructed analogously to \eqref{eq:cross_rel:data_matrix}, however with covariance matrices replaced by instantaneous cross-spectrum matrices
+where \(\eta \in [0,1]\) is an exponential smoothing factor.
+The matrix \(\tilde{\Rf}(m)\) is constructed similarly to \eqref{eq:cross_rel:data_matrix}, with \(\sum_{i \neq 1} \tilde{\Rf}_{ii}\) and \(-\tilde{\Rf}_{ij}\) on the diagonal and off-diagonal blocks respectively, where the instantaneous cross-spectrum matrices are defined as
 \begin{equation}
@@
 \begin{align}
-    \bm{{W}}_{L \times 2L}^{01} &= \mtxb{F}_{L \times L} \mtxb{W}_{L \times 2L}^{01} \mtxb{F}_{2L \times 2L}^{-1}\\
+    \bm{{W}}_{L \times 2L}^{01} &= \mtxb{F}_{L \times L} \mtxb{W}_{L \times 2L}^{01} \mtxb{F}_{2L \times 2L}^{-1},\\
     \bm{{W}}_{2L \times L}^{10} &= \mtxb{F}_{2L \times 2L} \mtxb{W}_{2L \times L}^{10} \mtxb{F}_{L \times L}^{-1}\label{eq:frequency_domain:overlap}
-\end{align} are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the discrete Fourier transform (DFT) matrices for sizes \(L\) and \(2L\) respectively and \(
+\end{align}
+are the frequency-domain overlap-save matrices where \(\mtxb{F}_{L \times L}\) and \(\mtxb{F}_{2L \times 2L}\) are the discrete Fourier transform (DFT) matrices for sizes \(L\) and \(2L\) respectively and \(
     \mtxb{W}_{L \times 2L}^{01} = \begin{bmatrix}
@@
     \end{bmatrix}\)
-    and \(
+, \(
     \mtxb{W}_{2L \times L}^{10} = \begin{bmatrix}
@@
 % as the minimization problem
-\begin{align}
-    \hat{\hf} = \arg \min_{\hf} \quad &\hf^\herm \hat{\Rf} \hf \label{eq:frequency_domain:min_prob}\\
+\begin{equation}
+    \begin{aligned}
+        \hat{\hf} = \arg \min_{\hf} \quad &\hf^\herm \hat{\Rf} \hf \\
         \text{s.t. } \quad &\hf^\herm \hf = 1.
-\end{align}
+    \end{aligned}\label{eq:frequency_domain:min_prob}
+\end{equation}
 
@@
 The major types of network topologies for distributed signal processing can be distinguished by the way information is shared within the network.
-In a centralized or star topology, where nodes transmit their signals to a dedicated device (fusion center), the processing happens (partly) centralized.
+For example, in a centralized or star topology, where nodes transmit their signals to a dedicated device (fusion center), the processing is (partly) centralized.
 This has drawbacks, such as the dependence on one or a small number of dedicated devices and a potentially large number of signals to be processed on these devices.
@@
 We consider a WSN consisting of \(M\) sensors each acquiring an output signal \(\x_i(n)\).
-We define a set \(\Tset_i \subseteq \Mset\) for each node \(i\) with \(i \in \Mset\), which contains the indices of the set of nodes which signal \(\x_i(n)\) is transmitted to.
-Further, we define a set \(\Rset_i \subseteq \Mset\) for each node with \(i \in \Mset\), which contains all indices of nodes from which the node receives signal information.
-Note that \(i \in \Tset_i\) and \(i \in \Rset_i\) for simplifying notation in later sections, but evidently, no actual transmission is necessary in that case, as the signal \(\x_i(n)\) is available locally at node \(i\).
+For each node \(i\), let \(\Tset_i \subseteq \Mset\) be the set of indices of nodes that have access to the signal \(\x_i\), i.e. the set of nodes that \(\x_i(n)\) is transmitted  to.
+Correspondingly, let \(\Rset_i \subseteq \Mset\) be the set of indices of nodes from which node \(i\) receives signal information, i.e., if \(i \in \Tset_j\), then \(j \in \Rset_i\).
+Note that \(i \in \Tset_i\) and \(i \in \Rset_i\) for simplifying notation in later sections, but evidently, no actual transmission is necessary, as the signal \(\x_i(n)\) is available locally at node \(i\).
 \autoref{fig:sensor_network:WSN_overview} shows a network where each node shares its signal information with one or more neighbors.
-For this work, we assume synchronicity of all nodes (i.e. no sampling rate offset) and perfect transmission of data with no time delay.
+For this work, we assume synchronicity of all nodes (i.e., no sampling rate offset) and perfect transmission of data with no time delay.
 
@@
     \vspace*{-0.1cm}
-    \caption{(a) shows an example of a network topology with 4 nodes (\(\circ\)).
+    \caption{(a) Network topology with 4 nodes.
 Arrows indicate exchange of signal information.
-(b) visualizes the data transmitted between nodes \(i\) and \(j\) for each frame \(m\).
+(b) Data transmission between nodes \(i\) and \(j\) for each frame \(m\).
 (c) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global variable components \(\hf_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
@@
 \label{ssec:general_consensus_admm}
-Defined by \(\Rset_i\), each node \(i \in \Mset\) has its own signal information and additionally signal information of its neighbors available.
+Recall that in addition to its own signal information, each node \(i \in \Mset\) has access to that of nodes \(j \in \Rset_i\).
 This is used to solve a BSI sub-problem of the same form as in \eqref{eq:frequency_domain:min_prob}, which however only involves the subset of channels.
@@
 \begin{equation}
-    \tilde{J}(\wf) = \sum_{i \in \Mset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Mset} \wf_i^\herm \hat{\aRhof}_i \wf_i.
+    \tilde{J}(\wf) = \sum_{i \in \Mset} \tilde{J}_i(\wf_i)  = \sum_{i \in \Mset} \wf_i^\herm \hat{\aRhof}_i \wf_i
     \label{eq:problem_splitting:cost_function}
@@
 Minimization problems with separable cost functions, as introduced here, can be solved by the well-established method of consensus ADMM \cite{boydDistributedOptimizationStatistical2011}
-\begin{align}
-    \underset{\wf,\,\hf}{\operatorname{minimize}} \quad &\sum_{i \in \Mset} \tilde{J}_i(\wf_i)\label{eq:general_consensus_admm:min_prob}\\
-    \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)},\quad i \in \Mset,\,j \in \Rset_i\label{eq:general_consensus_admm:eq_constraint}\\
-    &\hf^\herm \hf = 1\label{eq:general_consensus_admm:norm_constraint}
-\end{align}
-where \(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e.
-one of the frequency responses in the stacked vector, to the corresponding global variable components \(\hf_j\) (cf.
+\begin{equation}
+    \begin{aligned}
+        \underset{\wf,\,\hf}{\operatorname{minimize}} \quad &\sum_{i \in \Mset} \tilde{J}_i(\wf_i)\\
+        \text{subject to} \quad &(\wf_i)_j = \hf_{\mathcal{G}(i,j)}\quad i \in \Mset,\,j \in \Rset_i\\
+        &\hf^\herm \hf = 1
+    \end{aligned}\label{eq:general_consensus_admm:min_prob}
+\end{equation}
+where \(\mathcal{G}(i,j)\) denotes the mapping of \(L\) local variable components \((\wf_i)_j\), i.e., one of the frequency responses in the stacked vector, to the corresponding global variable components \(\hf_j\) (cf.
 \autoref{fig:problem_splitting:parameter_mapping}).
@@
 This defines \(\tilde{\hf}_i = \left[ \left\{ \hf_j^\T \right\}_{j \in \Rset_i} \right]^\T\).
-The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces consensus, i.e.
-a common solution taking into account estimates of all nodes that share data of the same channel.
-
+The equality constraint between local variables \(\wf_i\) and global variable \(\hf\) enforces consensus, i.e., a common solution taking into account estimates of all nodes that share data of the same channel.
 The augmented Lagrangian for this particular general-form consensus problem is
-\begin{align}
+\begin{equation}
+    \begin{aligned}
         \mathcal{L}_{\rho} &(\wf,\hf,\uuf) = \sum_{i \in \Mset} \left( \wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)\right.
-\vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2} \nonumber\\
+\vphantom{+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2}\\
         \vphantom{\wf_i^\herm \hat{\aRhof}_i \wf_i + 2 \Re \left( \uuf_i^{\herm} \left(\wf_i - \tilde{\hf}_i\right) \right)} & \qquad \qquad \qquad \qquad \left.
-+ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right)\label{eq:general_consensus_admm:lagrangian}
-\end{align}
++ \rho \left\| \wf_i - \tilde{\hf}_i \right\|^2 \right)
+    \end{aligned}\label{eq:general_consensus_admm:lagrangian}
+\end{equation}
 where \(\uuf \triangleq (\uuf_1,\ldots,\uuf_M)\) are the stacked local dual variables (Lagrange multipliers) \(\uuf_i = \left[ \left\{ (\uuf_i)_j^{\T} \right\}_{j \in \Rset_i} \right]^\T\) with \((\uuf_i)_j\) denoting the dual variable for channel \(j\) at node \(i\).
-These variables follow from the equality constraints in \eqref{eq:general_consensus_admm:eq_constraint}.
+These variables follow from the consensus equality constraint in \eqref{eq:general_consensus_admm:min_prob}.
 % The local variables \(\wf\) and global variable \(\hf\) are as introduced
@@
 \begin{align}
-    \wf_i^{k+1} &= \underset{\wf_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\wf,\hf^k,\uuf^k),\label{eq:general_consensus_admm:local}\\
+    \wf_i^{k+1} &= \underset{\wf_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\wf,\hf^k,\uuf^k)\label{eq:general_consensus_admm:local}\\
     \hf^{k+1} &= \underset{\hf, \|\hf\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\wf^{k+1},\hf,\uuf^k)\label{eq:general_consensus_admm:global}\\
-    \uuf_i^{k+1} &= \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right).\label{eq:general_consensus_admm:dual}
+    \uuf_i^{k+1} &= \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right),\label{eq:general_consensus_admm:dual}
 \end{align}
@@
 \begin{equation}
-    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right)\label{eq:online_admm:local_update}
+    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right),\label{eq:online_admm:local_update}
 \end{equation}
@@
 \begin{equation}
-    \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1}
+    \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1},
 \end{equation}
 which is straightforward to compute.
-
-% The global variable \(\hf\), a stacked vector of the \(M\) single-channel consensus variables \(\hf_i\), is updated by a distributed update.
 It may be readily verified (cf. \cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by an update step which computes
 \begin{equation}
-    \hf_i^{m+1} = \frac{\bar{\hf}_i^{m+1}}{\sqrt{\sum_{j \in \Tset_i} \phi_i}}\label{eq:online_admm:consensus_update}
+    \hf_i^{m+1} = \frac{\bar{\hf}_i^{m+1}}{\sqrt{\sum_{j \in \Tset_i} \|\bar{\hf}_i^{m+1}\|^2}}\label{eq:online_admm:consensus_update}
 \end{equation}
@@
 \begin{equation}
-    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}
+    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}.
 \end{equation}
-and the squared norm \(\phi_i = \|\bar{\hf}_i^{m+1}\|^2\).
-Here, \(\bar{\wf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\wf_j)_i\) and \(\bar{\uuf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uuf_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) computed at node \(i\).
-The values of all \(\phi_i\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
-
-The dual variables are straightforward to compute as
+Here, \(\bar{\wf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\wf_j)_i\) and \(\bar{\uuf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uuf_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) respectively, computed at node \(i\).
+The values of all \(\|\bar{\hf}_i^{m+1}\|^2\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
+Finally, the update of the dual variables is given by
 \begin{equation}
@@
 \end{equation}
-
 The computations of local, consensus and dual variables, in \eqref{eq:online_admm:local_update}, \eqref{eq:online_admm:consensus_update} and \eqref{eq:online_admm:dual_update} respectively, require data transmitted by other nodes (cf.
@@
     \vspace*{-0.2cm}
-    \caption{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!64\) at different SNR values.
-Shown are (a) NPM at \(\text{SNR}=10\,\text{dB}\) over frame index \(m\) for convergence speed comparison and (b) the steady-state NPMs over different SNRs.}
+    \caption{(a) NPM at \(\text{SNR}=10\,\text{dB}\) over frame index \(m\) and (b) steady-state NPMs over different SNRs.}
     \label{fig:perf_eval:NPM_over_time_exp1}
@@
 \begin{equation}
-    \text{NPM}(m) = 20\,\log_{10} \left(\left\| \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m) \right\| / \left\|\h(m)\right\| \right)
+    \text{NPM}(m) = 20\,\log_{10} \left(\left\| \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m) \right\| / \left\|\h(m)\right\| \right),
 \end{equation}
@@
 \begin{equation}
-    \text{SNR} = 10 \log_{10} \left(\frac{\sigma_s^2 \| \h_t \|}{M \sigma_v^2} \right)
+    \text{SNR} = 10 \log_{10} \left(\frac{\sigma_s^2 \| \h_t \|}{M \sigma_v^2} \right),
 \end{equation}
@@
 The step sizes are hand tuned for similar convergence speed: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
-\autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM of 30 Monte-Carlo runs over frame index \(m\).
-\autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median of 30 Monte-Carlo runs where the averaged NPM of \(100\) frames after convergence is plotted.
+\autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).
+\autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median (30 Monte-Carlo runs) where the averaged NPM of \(100\) frames after convergence is plotted.
 It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
@@
     \vspace*{-0.2cm}
-    \caption[Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\)]{Comparison of ADMM-BSI convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\) for \(\text{SNR}=20\,\text{dB}\).
-NPM is plotted for systems of (a) 4 nodes/channels and (b) 8 nodes/channels.
+    \caption[Convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\)]{Convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\) for \(\text{SNR}=20\,\text{dB}\).
+NPM for systems of (a) 4 nodes/channels and (b) 8 nodes/channels.
 The inset of (a) shows the base ring topology (black arrows) and all other possible connections (dashed black arrows).}
@@
 \autoref{fig:perf_eval:NPM_over_time_M4} and \autoref{fig:perf_eval:NPM_over_time_M8} show the median NPM (30 Monte-Carlo runs) for \(M=4\) and \(M=8\) respectively.
-The plots suggests a proportional relation of convergence speed, channel number \(M\) and sub-problem overlap \(\zeta\) while the steady-state error appears to be not dependent on \(\zeta\).
-\begin{attention}
-    Some plots and values will change slightly and I will fit it onto 4 pages.
-\end{attention}
+The plots suggests a proportional relation of convergence speed, channel number \(M\) and \(\zeta\) while the steady-state error appears to be not dependent on \(\zeta\).
 

### 2022-05-06 paper.tex
addresses

@@
 Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}}
-        {KU Leuven\\Department of Electrical Engineering (ESAT), STADIUS\\3001 Leuven, Belgium}
+        {KU Leuven\\
+        Dept. of Electrical Engineering (ESAT)\\
+        % STADIUS\\
+        3001 Leuven, Belgium}
         {J. Østergaard}
         {Aalborg University\\
-        Department of Electronic Systems\\
+        Dept. of Electronic Systems\\
+        % Section on Artificial Intelligence and Sound\\
         9220 Aalborg, Denmark}

### 2022-05-06 python/algorithms/admm_newton_fq.py
separate simulation folders

@@ -112,7 +112,7 @@ class NodeProcessor:
         # if self.buffer_ind >= self.buffer_size:
         #     self.buffer_ind = 0
         #     self.buffer_filled = True
-        # pass
+        pass
 
     def step(self) -> None:
         # if not self.buffer_filled:
@@ -123,16 +123,11 @@ class NodeProcessor:
     def solveLocalLS(self) -> None:
         R = self.construct_Rxp()  # construct matrix R_x+
         self.R_xp_ = R if self.first else self.eta * self.R_xp_ + (1 - self.eta) * R
-        y = self.R_xp_ @ self.x + self.y + self.rho * (self.x - self.z_l)
-        # self.R_norm.append(np.linalg.norm(R))
-        V = np.diag(1 / (np.diag(self.R_xp_) + self.rho))
-        # self.V = V if self.first else self.eta * self.V + (1 - self.eta) * V
         self.first = False
-        # self.V_norm.append(np.linalg.norm(V))
-        self.x = self.x - self.mu * V @ y
-        # self.x_norm.append(np.linalg.norm(self.x))
-        # self.x = self.x - self.mu*np.linalg.solve(
-        #     R + self.rho*np.eye(self.L*self.N), y)
+        y = self.R_xp_ @ self.x + self.y + self.rho * (self.x - self.z_l)
+        self.x = self.x - self.mu * np.linalg.solve(
+            self.R_xp_ + self.rho * np.eye(self.L * self.N), y
+        )
         # self.x = np.linalg.solve(
         #     R.conj().T@R + self.rho*np.eye(self.L*self.N), y)
         pass
@@ -288,7 +283,7 @@ class Network:
             x_avg[node.global_indices] += node.x * self.g[node.global_indices]
             y_avg[node.global_indices] += node.y * self.g[node.global_indices]
         pp = x_avg + 1 / node.rho * y_avg  # WHAT DO WITH RHO IF NOT SAME FOR ALL
-        self.z = pp / (np.linalg.norm(pp)) * self.L / self.N
+        self.z = pp / (np.linalg.norm(pp))
         pass
 
     def broadcastGlobalVariable(self) -> None:

### 2022-05-06 python/algorithms/admm_newton_fq_diag.py

@@ -112,7 +112,7 @@ class NodeProcessor:
         # if self.buffer_ind >= self.buffer_size:
         #     self.buffer_ind = 0
         #     self.buffer_filled = True
-        pass
+        # pass
 
     def step(self) -> None:
         # if not self.buffer_filled:
@@ -123,11 +123,16 @@ class NodeProcessor:
     def solveLocalLS(self) -> None:
         R = self.construct_Rxp()  # construct matrix R_x+
         self.R_xp_ = R if self.first else self.eta * self.R_xp_ + (1 - self.eta) * R
-        self.first = False
         y = self.R_xp_ @ self.x + self.y + self.rho * (self.x - self.z_l)
-        self.x = self.x - self.mu * np.linalg.solve(
-            self.R_xp_ + self.rho * np.eye(self.L * self.N), y
-        )
+        # self.R_norm.append(np.linalg.norm(R))
+        V = np.diag(1 / (np.diag(self.R_xp_) + self.rho))
+        # self.V = V if self.first else self.eta * self.V + (1 - self.eta) * V
+        self.first = False
+        # self.V_norm.append(np.linalg.norm(V))
+        self.x = self.x - self.mu * V @ y
+        # self.x_norm.append(np.linalg.norm(self.x))
+        # self.x = self.x - self.mu*np.linalg.solve(
+        #     R + self.rho*np.eye(self.L*self.N), y)
         # self.x = np.linalg.solve(
         #     R.conj().T@R + self.rho*np.eye(self.L*self.N), y)
         pass
@@ -283,7 +288,7 @@ class Network:
             x_avg[node.global_indices] += node.x * self.g[node.global_indices]
             y_avg[node.global_indices] += node.y * self.g[node.global_indices]
         pp = x_avg + 1 / node.rho * y_avg  # WHAT DO WITH RHO IF NOT SAME FOR ALL
-        self.z = pp / (np.linalg.norm(pp)) * self.L / self.N
+        self.z = pp / (np.linalg.norm(pp))
         pass
 
     def broadcastGlobalVariable(self) -> None:

### 2022-05-06 python/plot_data.py

@@ -43,7 +43,7 @@ L_p = 64
 N_p = 5
 
 dir = "data/simulation_random/"
-files = sorted(os.listdir(dir))
+files = (file for file in os.listdir(dir) if os.path.isfile(os.path.join(dir, file)))
 for filename in files:
     print(filename)
     with open(dir + filename, "rb") as f:

### 2022-05-06 python/simulation_1/plot.py

@@ -1,0 +1,231 @@
+# %%
+import os
+import numpy as np
+import time
+import utils
+import matplotlib.pyplot as plt
+
+# %% random IRS
+SNRs = [5, 10, 15, 20, 30, 40, 50]
+id = 0
+runs_ = []
+run_ = []
+L_ = []
+N_sens_ = []
+SNR_ = []
+h_ = []
+err_MCQN_ = {}
+err_NMCFLMS_ = {}
+err_RNMCFLMS_ = {}
+err_LPRNMCFLMS_ = {}
+err_ADMM_newton_td_ = {}
+err_ADMM_newton_fq_ = {}
+err_ADMM_newton_fq_diag_ = {}
+for SNR in SNRs:
+    err_MCQN_[SNR] = None
+    err_NMCFLMS_[SNR] = None
+    err_RNMCFLMS_[SNR] = None
+    err_LPRNMCFLMS_[SNR] = None
+    err_ADMM_newton_td_[SNR] = None
+    err_ADMM_newton_fq_[SNR] = None
+    err_ADMM_newton_fq_diag_[SNR] = None
+
+dir = "data/"
+files = (file for file in os.listdir(dir) if os.path.isfile(os.path.join(dir, file)))
+for filename in files:
+    print(filename)
+    with open(dir + filename, "rb") as f:
+        runs = np.load(f)
+        run = np.load(f)
+        L = np.load(f)
+        N_sens = np.load(f)
+        SNR = int(np.load(f))
+        h = np.load(f)
+        err_MCQN = np.load(f)
+        err_NMCFLMS = np.load(f)
+        err_RNMCFLMS = np.load(f)
+        err_LPRNMCFLMS = np.load(f)
+        err_ADMM_newton_td = np.load(f)
+        err_ADMM_newton_fq = np.load(f)
+        err_ADMM_newton_fq_diag = np.load(f)
+
+        if not np.isnan(err_MCQN).any():
+            err_MCQN_[SNR] = (
+                err_MCQN
+                if err_MCQN_[SNR] is None
+                else np.vstack((err_MCQN_[SNR], err_MCQN))
+            )
+        if not np.isnan(err_NMCFLMS).any():
+            err_NMCFLMS_[SNR] = (
+                err_NMCFLMS
+                if err_NMCFLMS_[SNR] is None
[…]

### 2022-05-06 python/simulation_1/simulation_1.py

@@ -1,43 +1,69 @@
 # %%
 import sys
+
+sys.path.append("..")
 import os.path
 import utils
 import numpy as np
 import scipy.signal as signal
-import admm_r1_td as admm
-import admm_newton_fq as sb_newton_fq
-import admm_newton_fq_diag as sb_newton_fq_diag
-import simo_bsi_central as cent
+from algorithms import admm_r1_td as admm
+from algorithms import admm_newton_fq as sb_newton_fq
+from algorithms import admm_newton_fq_diag as sb_newton_fq_diag
+from algorithms import simo_bsi_central as cent
 import matplotlib.pyplot as plt
 
 # %%
 process_id = int(sys.argv[1])
 SNR = int(sys.argv[2])
 N_sens = int(sys.argv[3])
-density = float(sys.argv[4])
-print("Job: %d, SNR: %d, N_sens: %d, density: %f" % (process_id, SNR, N_sens, density))
+L = int(sys.argv[4])
+print("Job: %d, SNR: %d, N_sens: %d, L: %d" % (process_id, SNR, N_sens, L))
 
 # %%
 runs = 30
-seed = 12345
 plot = False
 
 # %%
-L = 16
+# L = 64
 N_f = 1024
+# N_sens = 3
 
 # %%
-N_s = 16000
+N_s = 8000 * 100
 
 # %%
+seed = 12345
 rng = np.random.RandomState()
 rng.seed(seed)
+# %%
+G = np.zeros((N_sens, N_sens))
+offdiag = np.arange(N_sens - 1)
+G[offdiag, offdiag + 1] = 1  # setting the directed ring as base
+G[-1, 0] = 1
+network_td = admm.Network(L)
+network_newton_fq = sb_newton_fq.Network(L)
+network_newton_fq_diag = sb_newton_fq_diag.Network(L)
+
+rho = 1
+for n in range(N_sens):
+    name = "node%d" % (n)
+    network_td.addNode(name, rho)
+    network_newton_fq.addNode(name, rho)
+    network_newton_fq_diag.addNode(name, rho)
+for n in range(N_sens):
+    name = "node%d" % (n)
+    connections = []
+    for j in range(N_sens):
+        name1 = "node%d" % (j)
+        if G[n, j] > 0:
+            connections.append(name1)
+    network_td.setConnection(name, connections)
[…]

### 2022-05-06 python/simulation_2/plot.py

@@ -1,0 +1,132 @@
+# %%
+import os
+import numpy as np
+import time
+import utils
+
+# import scipy.signal as signal
+import matplotlib.pyplot as plt
+
+# %% random connectivity
+SNRs = [20]
+N_senses = [4, 6, 8]
+densities = [0.0, 0.25, 0.5, 0.75]
+
+err_ADMM_newton_td_ = {}
+err_ADMM_newton_fq_ = {}
+err_ADMM_newton_fq_diag_ = {}
+for i in range(len(densities)):
+    err_ADMM_newton_td_[i] = {}
+    err_ADMM_newton_fq_[i] = {}
+    err_ADMM_newton_fq_diag_[i] = {}
+    for N in N_senses:
+        err_ADMM_newton_td_[i][N] = None
+        err_ADMM_newton_fq_[i][N] = None
+        err_ADMM_newton_fq_diag_[i][N] = None
+
+dir = "data/"
+files = sorted(os.listdir(dir))
+for filename in files:
+    print(filename)
+    with open(dir + filename, "rb") as f:
+        runs = np.load(f)
+        run = np.load(f)
+        L = np.load(f)
+        N_sens = int(np.load(f))
+        SNR = int(np.load(f))
+        G = np.load(f)
+        h = np.load(f)
+        err_MCQN = np.load(f)
+        err_NMCFLMS = np.load(f)
+        err_RNMCFLMS = np.load(f)
+        err_LPRNMCFLMS = np.load(f)
+        err_ADMM_newton_td = np.load(f)
+        err_ADMM_newton_fq = np.load(f)
+        err_ADMM_newton_fq_diag = np.load(f)
+
+        pid = int(filename.split("_")[0])
+        if pid < 3:
+            did = 0
+            density = 0.0
+        elif pid < 6:
+            did = 1
+            density = 0.25
+        elif pid < 9:
+            did = 2
+            density = 0.5
+        else:
+            did = 3
+            density = 0.75
+
+        if not np.isnan(err_ADMM_newton_td).any():
+            err_ADMM_newton_td_[did][N_sens] = (
+                err_ADMM_newton_td
+                if err_ADMM_newton_td_[did][N_sens] is None
+                else np.vstack((err_ADMM_newton_td_[did][N_sens], err_ADMM_newton_td))
+            )
+        if not np.isnan(err_ADMM_newton_fq).any():
[…]

### 2022-05-06 python/simulation_2/simulation_2.py

@@ -4,67 +4,71 @@ import os.path
 import utils
 import numpy as np
 import scipy.signal as signal
-import admm_r1_td as admm
-import admm_newton_fq as sb_newton_fq
-import admm_newton_fq_diag as sb_newton_fq_diag
-import simo_bsi_central as cent
+from ..algorithms import admm_r1_td as admm
+from algorithms import admm_newton_fq as sb_newton_fq
+from algorithms import admm_newton_fq_diag as sb_newton_fq_diag
+from algorithms import simo_bsi_central as cent
 import matplotlib.pyplot as plt
 
 # %%
 process_id = int(sys.argv[1])
 SNR = int(sys.argv[2])
-N_sens = 6
-L = 128
-print("Job: %d, SNR: %d, N_sens: %d, L: %f" % (process_id, SNR, N_sens, L))
+N_sens = int(sys.argv[3])
+density = float(sys.argv[4])
+print("Job: %d, SNR: %d, N_sens: %d, density: %f" % (process_id, SNR, N_sens, density))
 
 # %%
-runs = 50
+runs = 30
+seed = 12345
 plot = False
 
 # %%
-# L = 64
+L = 16
 N_f = 1024
-# N_sens = 3
 
 # %%
 N_s = 16000
 
 # %%
-seed = 12345
 rng = np.random.RandomState()
 rng.seed(seed)
 
 # %%
-with open("../generate_irs/h.npy", "rb") as f:
-    h = np.load(f)
-# %%
 for run in range(runs):
-    if os.path.isfile("data/simulation_rim/%d_%d.npy" % (process_id, run)):
+    if os.path.isfile("data/%d_%d.npy" % (process_id, run)):
         print("run %d is already there" % (run))
         continue
-
-    # # %%
-    # if plot:
-    #     fig, ax1 = plt.subplots()
-    #     ax1.set_title("Digital filter frequency response")
-    #     for n in range(N_sens):
-    #         ax1.plot(w, 20 * np.log10(abs(h_f[n, :])))
-    #     ax1.set_ylabel("Amplitude [dB]")
-    #     ax1.set_xlabel("Frequency [rad/sample]")
-    #     ax1.grid()
-    #     plt.show()
+    # %%
+    h = np.array([]).reshape(0, 1)
+    h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
+    for n in range(N_sens):
+        h_ = rng.normal(size=(L, 1))
+        h_ = h_ / np.linalg.norm(h_)
[…]

### 2022-05-06 python/simulation_random.py

@@ -1,299 +1,0 @@
-# %%
-import sys
-import os.path
-import utils
-import numpy as np
-import scipy.signal as signal
-import admm_r1_td as admm
-import admm_newton_fq as sb_newton_fq
-import admm_newton_fq_diag as sb_newton_fq_diag
-import simo_bsi_central as cent
-import matplotlib.pyplot as plt
-
-# %%
-process_id = int(sys.argv[1])
-SNR = int(sys.argv[2])
-N_sens = int(sys.argv[3])
-L = int(sys.argv[4])
-print("Job: %d, SNR: %d, N_sens: %d, L: %d" % (process_id, SNR, N_sens, L))
-
-# %%
-runs = 30
-plot = False
-
-# %%
-# L = 64
-N_f = 1024
-# N_sens = 3
-
-# %%
-N_s = 8000 * 100
-
-# %%
-seed = 12345
-rng = np.random.RandomState()
-rng.seed(seed)
-
-# %%
-for run in range(runs):
-    if os.path.isfile("data/simulation_random/%d_%d.npy" % (process_id, run)):
-        print("run %d is already there" % (run))
-        continue
-    # %%
-    h = np.array([]).reshape(0, 1)
-    h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
-    for n in range(N_sens):
-        h_ = rng.normal(size=(L, 1))
-        h_ = h_ / np.linalg.norm(h_)
-        w, hh = signal.freqz(h_, worN=N_f)
-        h_f[n, :] = hh
-        h = np.concatenate([h, h_])
-
-    # %%
-    if plot:
-        fig, ax1 = plt.subplots()
-        ax1.set_title("Digital filter frequency response")
-        for n in range(N_sens):
-            ax1.plot(w, 20 * np.log10(abs(h_f[n, :])))
-        ax1.set_ylabel("Amplitude [dB]")
-        ax1.set_xlabel("Frequency [rad/sample]")
-        ax1.grid()
-        plt.show()
-
-    # %%
-    if plot:
-        plt.stem(h)
-        plt.title("filter taps of stacked imp resp")
-        plt.show()
-
-    # %%
-    G = np.zeros((N_sens, N_sens))
-    offdiag = np.arange(N_sens - 1)
[…]

### 2022-05-06 python/simulation_simir.py

@@ -1,164 +1,0 @@
-# %%
-import utils
-import numpy as np
-import scipy.signal as signal
-import admm_r1_td as admm
-import simo_bsi_central as cent
-import matplotlib.pyplot as plt
-
-# %%
-L = 64
-N_f = 1024
-N_sens = 3
-
-# %%
-fs = 16000
-l = 120
-N_s = 8000
-
-# %%
-with open("h.npy", "rb") as f:
-    h = np.load(f)
-
-# %%
-h_f = np.zeros((N_sens, N_f), dtype=np.complex128)
-fig, ax1 = plt.subplots()
-ax1.set_title("Digital filter frequency response")
-for n in range(N_sens):
-    h_ = h[n * L : (n + 1) * L]
-    w, hh = signal.freqz(h_, worN=N_f)
-    h_f[n, :] = hh
-    ax1.plot(w, 20 * np.log10(abs(hh)))
-    # plt.legend()
-ax1.set_ylabel("Amplitude [dB]")
-ax1.set_xlabel("Frequency [rad/sample]")
-ax1.grid()
-plt.show()
-
-# %%
-plt.stem(h)
-plt.title("filter taps of stacked imp resp")
-plt.show()
-
-# %%
-network_td = admm.Network(L)
-rho = 1
-network_td.addNode("node1", rho)
-network_td.addNode("node2", rho)
-network_td.addNode("node3", rho)
-
-# node 1 sends to node 2 and 3
-network_td.setConnection("node1", ["node2"])
-# network_td.setConnection("node2", ["node1"])
-network_td.setConnection("node2", ["node3"])
-network_td.setConnection("node3", ["node1"])
-network_td.setBufferSize(1)
-
-# %% GENERATE AR SIGNAL
-N_ff = 1025
-b1 = signal.firwin(N_ff, 0.25, pass_zero=False)
-M = 10
-Ah = np.zeros((M, N_ff - M - 1))
-for l in range(M):
-    Ah[l, :] = b1[M - l : M - l + N_ff - M - 1]
-y = b1[M + 1 :]
-a_ = np.linalg.solve(Ah @ Ah.T, Ah @ y)
-b = np.concatenate([np.ones((1,)), -a_])
-
-# %%
-p0 = 1e-2
-u = np.random.normal(size=(N_s, 1)) * np.sqrt(p0)
-# %%
[…]

### 2022-05-06 tikz/topology_details.tex
waiting for simulation to finish

@@
 
-        \draw[-stealth,black, line width=1.2] (A) to[bend left=20] node[above, pos=0.5, sloped, scale=1]{\(\x_i, \{\phi_1,\ldots,\phi_i\}\)}  (B);
+        \draw[-stealth,black, line width=1.2] (A) to[bend left=20] node[above, pos=0.5, sloped, scale=1]{\(\x_i, \hf_i, \{\|\bar{\hf}_1\|^2,\ldots,\|\bar{\hf}_i\|^2\}\)}  (B);
 
-        \draw[stealth-,gray, line width=1.2] (A) to[bend right=20] node[below, pos=0.5, sloped,scale=1]{\((\wf_j)_i,(\uuf_j)_i,\{\phi_1,\ldots,\phi_M\}\)}  (B);
+        \draw[stealth-,gray, line width=1.2] (A) to[bend right=20] node[below, pos=0.5, sloped,scale=1]{\((\wf_j)_i,(\uuf_j)_i,\{\|\bar{\hf}_1\|^2,\ldots,\|\bar{\hf}_M\|^2\}\)}  (B);
 

### 2022-05-06 tikz/topology_inset_simulation.tex

% Tikz File 'topology_general.tex'
\documentclass{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz,amsmath,amssymb}
\usetikzlibrary{arrows,snakes,backgrounds}
    \begin{document}
    \begin{tikzpicture}[->,shorten >=1pt,auto,semithick]
        \tikzstyle{admmnode}=[
            circle,
            draw=black,
            thick,
            fill=gray,
            text=black
        ]
        \tikzstyle{centernode}=[
            diamond,
            draw=black,
            thick,
            fill=gray!40,
            text=black
        ]

        \node[admmnode, fill=gray!15] (A) at (-1,1){\(1\)};
        \node[admmnode, fill=gray!15] (B) at (1,1){\(2\)};
        \node[admmnode, fill=gray!15] (C) at (1,-1){\(3\)};
        \node[admmnode, fill=gray!15] (D) at (-1,-1){\(4\)};

        \draw[-stealth, line width=1.25] (A) to[bend left=10] node[]{} (B);
        \draw[dashed,-stealth, line width=1.25] (A) to[bend left=10] node[]{} (C);
        \draw[dashed,-stealth, line width=1.25] (A) to[bend left=10] node[]{} (D);
        \draw[-stealth, line width=1.25] (B) to[bend left=10] node[]{} (C);
        \draw[dashed,-stealth, line width=1.25] (B) to[bend left=10] node[]{} (A);
        \draw[dashed,-stealth, line width=1.25] (B) to[bend left=10] node[]{} (D);
        \draw[-stealth, line width=1.25] (C) to[bend left=10] node[]{} (D);
        \draw[dashed,-stealth, line width=1.25] (C) to[bend left=10] node[]{} (A);
        \draw[dashed,-stealth, line width=1.25] (C) to[bend left=10] node[]{} (B);
        \draw[-stealth, line width=1.25] (D) to[bend left=10] node[]{} (A);
        \draw[dashed,-stealth, line width=1.25] (D) to[bend left=10] node[]{} (B);
        \draw[dashed,-stealth, line width=1.25] (D) to[bend left=10] node[]{} (C);

    \end{tikzpicture}
\end{document}

### 2022-05-06 generate_irs/generate_irs.py
delete unused files

@@ -1,73 +1,0 @@
-# %%
-import numpy as np
-import matplotlib.pyplot as plt
-import rim
-
-# %%
-xs = [1, 1, 1]
-# xr = np.random.uniform(0, 2, size=(6, 3))
-xr = [
-    [0.92781265, 1.13393288, 0.26736836],
-    [1.43182171, 1.56376992, 1.59195482],
-    [1.93766398, 0.46898242, 0.1320927],
-    [0.47049847, 1.36370444, 0.56008512],
-    [0.18023421, 0.99715069, 1.75508388],
-    [0.33782243, 0.99060236, 1.48623386],
-]
-Nt = 256
-L = [2, 2, 2]
-beta = [0.6, 0.6, 0.6, 0.6, 0.6, 0.6]
-Fs = 8000
-N = [20, 20, 20]
-xr_dirs = [[1, 0, 0], [1, 0, 0], [0, 1, 0], [1, 0, 0], [1, 0, 0], [0, 1, 0]]
-xr_types = ["o", "o", "o", "o", "o", "o"]
-
-h_gen, seed = rim.rim(
-    xs,
-    xr,
-    Nt,
-    L,
-    beta,
-    Fs,
-    Rd=0.0,
-    N=N,
-    Tw=20,
-    Fc=0.9,
-    MicDirs=xr_dirs,
-    MicTypes=xr_types,
-)
-
-# %%
-L = 128
-fig, axes = plt.subplots(h_gen.shape[1], 1, figsize=(8, 10))
-h_gen /= np.max(h_gen)
-h = np.zeros((L * 6,))
-for i, row in enumerate(axes):
-    h_ = h_gen[:, i]
-    h_ /= np.max(h_)
-    start = np.argmax(h_ == 1)
-    h[i * L : (i + 1) * L] = h_[start : start + L]
-    row.plot(h_[start : start + L])
-    row.set_ylabel("Amplitude [1]")
-    row.set_xlabel("Samples [1]")
-    row.spines["right"].set_visible(False)
-    row.spines["top"].set_visible(False)
-    row.set_ylim((-1, 1))
-    row.grid()
-plt.tight_layout()
-plt.show()
-
-# %%
-fig, axes = plt.subplots(1, 1, figsize=(8, 3))
-for i in range(6):
-    x = np.arange(i * L, (i + 1) * L)
-    plt.plot(x, h[i * L : (i + 1) * L])
[…]

### 2022-05-06 generate_irs/rim.py

@@ -1,100 +1,0 @@
-
-import numpy as np
-import librimrs as rimrs
-
-
-# def test(xr):
-#     return rimrs.rim(xr)
-
-
-def rim(xs, xr, Nt, L, beta, Fs, c=343, Rd=1e-2, N=(0, 0, 0), Tw=20, Fc=0.9, seed=0, MicDirs=None, MicTypes=None):
-    """
-    `h = rim(xs, xr, L, T60, Nt, Fs)`
-    Randomized Image Source Method
-    #### Arguments:
-    * `xs`  : Source position in meters (must be array-like)
-    * `xr`  : Microphone position in meters (must be array-like for mic array)
-    * `Nt`  : Time samples
-    * `L`   : 3 element array-like containing dimensions of the room
-    * `beta`/`T60` : 6 element array-like containing reflection coefficients of walls/reverberation time
-    * `Fs`  : sampling frequency
-    #### Keyword Arguments:
-    * `c = 343`    : speed of sound
-    * `Rd = 1e-2`  : random displacement (in meters)
-    * `N = (0,0,0)`: 3 element array-like representing order of reflection when `N == (0;0;0)` full order is computed.
-    * `Tw = 20`    : taps of fractional delay filter
-    * `Fc = 0.9`   : cut-off frequency of fractional delay filter
-    #### Outputs:
-    * `h`: vector or matrix where each column is an impulse response corresponding to the microphone positions `xr`
-    * `seed`: randomization seed to preserve spatial properties when other RIR at different position are needed
-    """
-    xs = np.asarray(xs, dtype=np.float64)
-    assert xs.shape == (3,)
-
-    xr = np.atleast_2d(np.asarray(xr, dtype=np.float64)).T.copy()
-    assert xr.shape[0] == 3
-
-    M = xr.shape[1]  # nuber of microphones
-
-    if MicDirs != None:
-        mic_dirs = np.atleast_2d(np.asarray(
-            MicDirs, dtype=np.float64)).T.copy()
-        assert mic_dirs.shape[0] == 3
-    else:
-        mic_dirs = np.ones(shape=(3, M))
-
-    if MicTypes != None:
-        mic_types_ = np.asarray(MicTypes)
-        mic_types = np.zeros(shape=mic_types_.shape)
-        for i in range(mic_types.size):
[…]

### 2022-05-06 paper.tex
minor change and remove pdf

@@
 
-The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)).
+The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)) with a ring topology where each node transmits its signal information to one neighbor.
 The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.

### 2022-05-06 python/algorithms/simo_bsi_central.py
updated simulation 2 plots

@@ -18,7 +18,7 @@ class MCALG:
                     - x[:, j, None][::-1].T
                     @ self.h[(i * self.L) : (i * self.L + self.L)]
                 )
-                X += e ** 2
+                X += e**2
         return X
 
     def compute_X_prior(self, x) -> float:
@@ -31,7 +31,7 @@ class MCALG:
                     - x[:, j, None][::-1].T
                     @ self.h_old[(i * self.L) : (i * self.L + self.L)]
                 )
-                X += e ** 2
+                X += e**2
         return X
 
     def construct_Rxp(self, x):
@@ -109,10 +109,10 @@ class VSSUCMCLMS(MCALG):
 
 
 class MCN(MCALG):
-    def __init__(self, ρ, λ, L, N, x_vars, buffer_size) -> None:
+    def __init__(self, rho, lambd, L, N, x_vars, buffer_size) -> None:
         MCALG.__init__(self, L, N, buffer_size)
-        self.ρ = ρ
-        self.λ = λ
+        self.rho = rho
+        self.lambd = lambd
         self.h = np.zeros(shape=(L * N, 1))
         self.h[0::L] = 1
         self.h = self.h / np.sqrt(N)
@@ -125,24 +125,24 @@ class MCN(MCALG):
         X = self.compute_X(x)  # error function Χ
         R_xp = self.construct_Rxp(x)  # construct matrix R_x+
 
-        self.R_xp_ = self.λ * self.R_xp_ + R_xp
+        self.R_xp_ = self.lambd * self.R_xp_ + R_xp
         # update step
         W = (
             2 * self.R_xp_
             - 4 * self.h @ self.h.T @ self.R_xp_
             - 4 * self.R_xp_ @ self.h @ self.h.T
         )
-        delta_h = self.h - self.ρ * np.linalg.solve(W, R_xp @ self.h - X * self.h)
+        delta_h = self.h - self.rho * np.linalg.solve(W, R_xp @ self.h - X * self.h)
         self.h = delta_h / np.linalg.norm(delta_h)
         pass
 
 
 class MCQN(MCALG):
-    def __init__(self, ρ, λ, η, L, N, x_vars, buffer_size) -> None:
+    def __init__(self, rho, lambd, eta, L, N, x_vars, buffer_size) -> None:
[…]

### 2022-05-06 python/plot_data.py

@@ -1,523 +1,0 @@
-# %%
-import os
-import numpy as np
-import time
-import utils
-
-# import scipy.signal as signal
-import matplotlib.pyplot as plt
-from matplotlib import rc
-
-# %%
-class SimulationData:
-    variable: str
-    variable_range: list
-
-
-# %% random IRS
-SNRs = [5, 10, 15, 20, 30, 40, 50]
-id = 0
-runs_ = []
-run_ = []
-L_ = []
-N_sens_ = []
-SNR_ = []
-h_ = []
-err_MCQN_ = {}
-err_NMCFLMS_ = {}
-err_RNMCFLMS_ = {}
-err_LPRNMCFLMS_ = {}
-err_ADMM_newton_td_ = {}
-err_ADMM_newton_fq_ = {}
-err_ADMM_newton_fq_diag_ = {}
-for SNR in SNRs:
-    err_MCQN_[SNR] = None
-    err_NMCFLMS_[SNR] = None
-    err_RNMCFLMS_[SNR] = None
-    err_LPRNMCFLMS_[SNR] = None
-    err_ADMM_newton_td_[SNR] = None
-    err_ADMM_newton_fq_[SNR] = None
-    err_ADMM_newton_fq_diag_[SNR] = None
-
-L_p = 64
-N_p = 5
-
-dir = "data/simulation_random/"
-files = (file for file in os.listdir(dir) if os.path.isfile(os.path.join(dir, file)))
-for filename in files:
-    print(filename)
-    with open(dir + filename, "rb") as f:
-        runs = np.load(f)
-        run = np.load(f)
-        L = np.load(f)
-        N_sens = np.load(f)
-        SNR = int(np.load(f))
-        h = np.load(f)
-        err_MCQN = np.load(f)
-        err_NMCFLMS = np.load(f)
-        err_RNMCFLMS = np.load(f)
-        err_LPRNMCFLMS = np.load(f)
-        err_ADMM_newton_td = np.load(f)
-        err_ADMM_newton_fq = np.load(f)
-        err_ADMM_newton_fq_diag = np.load(f)
-
-        if L != L_p or N_sens != N_p:
-            continue
-
-        if not np.isnan(err_MCQN).any():
-            err_MCQN_[SNR] = (
-                err_MCQN
-                if err_MCQN_[SNR] is None
-                else np.vstack((err_MCQN_[SNR], err_MCQN))
-            )
[…]

### 2022-05-06 python/simulation_2/plot.py

@@ -107,6 +107,7 @@ plt.show()
 # %%
 lim = 2500
 for N_sens in [4, 8]:
+    lines = ["-", "--", "-.", ":"]
     fig = plt.figure(figsize=(3, 2.5))
     for i in range(len(densities)):
         if err_ADMM_newton_fq_diag_[i][N_sens] is not None:
@@ -115,6 +116,7 @@ for N_sens in [4, 8]:
                 * np.log10(
                     np.nanmedian(err_ADMM_newton_fq_diag_[i][N_sens], axis=0)[:lim]
                 ),
+                lines.pop(),
                 label=r"$\zeta = $" + "%1.2f" % (densities[i]),
             )
     # plt.title(r"$M=$")

### 2022-05-06 python/simulation_1/plot.py
simulation 1 run without regularization

@@ -7,27 +7,20 @@ import matplotlib.pyplot as plt
 
 # %% random IRS
 SNRs = [5, 10, 15, 20, 30, 40, 50]
-id = 0
-runs_ = []
-run_ = []
-L_ = []
-N_sens_ = []
-SNR_ = []
-h_ = []
 err_MCQN_ = {}
 err_NMCFLMS_ = {}
-err_RNMCFLMS_ = {}
+# err_RNMCFLMS_ = {}
 err_LPRNMCFLMS_ = {}
-err_ADMM_newton_td_ = {}
-err_ADMM_newton_fq_ = {}
+# err_ADMM_newton_td_ = {}
+# err_ADMM_newton_fq_ = {}
 err_ADMM_newton_fq_diag_ = {}
 for SNR in SNRs:
     err_MCQN_[SNR] = None
     err_NMCFLMS_[SNR] = None
-    err_RNMCFLMS_[SNR] = None
+    # err_RNMCFLMS_[SNR] = None
     err_LPRNMCFLMS_[SNR] = None
-    err_ADMM_newton_td_[SNR] = None
-    err_ADMM_newton_fq_[SNR] = None
+    # err_ADMM_newton_td_[SNR] = None
+    # err_ADMM_newton_fq_[SNR] = None
     err_ADMM_newton_fq_diag_[SNR] = None
 
 dir = "data/"
@@ -43,10 +36,10 @@ for filename in files:
         h = np.load(f)
         err_MCQN = np.load(f)
         err_NMCFLMS = np.load(f)
-        err_RNMCFLMS = np.load(f)
+        # err_RNMCFLMS = np.load(f)
         err_LPRNMCFLMS = np.load(f)
-        err_ADMM_newton_td = np.load(f)
-        err_ADMM_newton_fq = np.load(f)
+        # err_ADMM_newton_td = np.load(f)
+        # err_ADMM_newton_fq = np.load(f)
         err_ADMM_newton_fq_diag = np.load(f)
 
         if not np.isnan(err_MCQN).any():
@@ -61,30 +54,30 @@ for filename in files:
                 if err_NMCFLMS_[SNR] is None
                 else np.vstack((err_NMCFLMS_[SNR], err_NMCFLMS))
             )
-        if not np.isnan(err_RNMCFLMS).any():
-            err_RNMCFLMS_[SNR] = (
-                err_RNMCFLMS
-                if err_RNMCFLMS_[SNR] is None
[…]

### 2022-05-06 python/simulation_1/simulation_1.py

@@ -94,26 +94,12 @@ for run in range(runs):
         plt.show()
 
     # %%
-    # GENERATE AR SIGNAL
-    N_ff = 1025
-    b1 = signal.firwin(N_ff, 0.25, pass_zero=False)
-    M = 20
-    Ah = np.zeros((M, N_ff - M - 1))
-    for l in range(M):
-        Ah[l, :] = b1[M - l : M - l + N_ff - M - 1]
-    y = b1[M + 1 :]
-    a_ = np.linalg.solve(Ah @ Ah.T, Ah @ y)
-    b = np.concatenate([np.ones((1,)), -a_])
-
-    # %%
+    # GENERATE SIGNAL
     p0 = 1e-2
     u = np.random.normal(size=(N_s, 1)) * np.sqrt(p0)
-    # %%
     s = u / u.max()
     # %%
-    # s = signal.lfilter([1], b, u, axis=0)
-
-    # %%
+    # CONVOLUTION WITH IRS
     hopsize = L
     s_ = np.concatenate([np.zeros(shape=(L - 1, 1)), s])
     var_s = np.var(s)
@@ -132,9 +118,10 @@ for run in range(runs):
     # CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD
     print("CENTRALIZED TIME DOMAIN QUASI NEWTON METHOD")
     err_MCQN = []
-    rhos = [0.025, 0.02, 0.01, 0.005, 0.01, 0.01, 0.01]
-    rho = rhos[process_id]  # step size
-    lambd = 1e-5  # regularization
+    # rhos = [0.01, 0.01, 0.01, 0.01, 0.01, 0.01, 0.01]
+    # rho = rhos[process_id]  # step size
+    rho = 0.01
+    lambd = 0  # regularization
     eta = 0.98  # forgetting factor
     buffer_size = L
 
@@ -160,17 +147,17 @@ for run in range(runs):
 
     # %%
     # CENTRALIZED ROBUST NORMALIZED FREQUENCY DOMAIN LMS METHOD
-    print("CENTRALIZED ROBUST NORMALIZED FREQUENCY DOMAIN LMS METHOD")
-    err_RNMCFLMS = []
-    rho = 0.2  # step size
-    lambd = 0.98  # forgetting factor
-    sigma = 0.01  # regularization
-    eta = 0.4  # coupling factor
[…]

### 2022-05-06 paper.tex

@@
     % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
-    \hspace*{-0.2cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}
+    \hspace*{-0.2cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/simulation_2/plots/NPM_over_time_M4.png}
         \put(57,42.5){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.6]{tikz/topology_inset_simulation}}
     \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
-    \hspace*{-0.0cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
+    \hspace*{-0.0cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/simulation_2/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
     \vspace*{-0.2cm}

### 2022-05-06 paper.tex
comments jesper

@@
 This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.
-Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}}
+Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-dist-bsi-admm}.}}
         {KU Leuven\\
@@
         3001 Leuven, Belgium}
-        {J. Østergaard}
+        {J. Østergaard, J. Jensen}
         {Aalborg University\\
@@
     In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a wireless sensor network (WSN).
-    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
+    The network consists of a fixed number of nodes each equipped with a processing unit and a sensor that represents an output channel of the SIMO system.
     The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels in a way that is determined by the network topology.
@@
 \begin{keywords}
-    blind system identification, multichannel signal processing, distributed signal processing, ADMM, Online-ADMM
+    blind system identification, multichannel signal processing, distributed signal processing, admm, online-admm
 \end{keywords}
@@
 Out of various multichannel BSI algorithms which have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.
-The normalized multi-channel frequency-domain LMS (NMCFLMS) \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} algorithm for instance is an efficient algorithm utilizing the fast Fourier transform (FFT) which has been extended to include constraints to improve robustness to noise and performance on acoustic impulse responses (RNMCFLMS \cite{huNoiseRobustBlind2015}, \(l_p\)-RNMCFLMS \cite{heNoiseRobustFrequencyDomain2018}, phase-constrained-\(l_p\)-RNMCFLMS \cite{joRobustBlindMultichannel2021}).
+The normalized multi-channel frequency-domain LMS (NMCFLMS) \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} algorithm for instance is an efficient algorithm utilizing the fast Fourier transform (FFT) which has been extended to include constraints to improve robustness to noise and performance on acoustic impulse responses such as the RNMCFLMS \cite{huNoiseRobustBlind2015}, \(l_p\)-RNMCFLMS \cite{heNoiseRobustFrequencyDomain2018} or phase-constrained-\(l_p\)-RNMCFLMS \cite{joRobustBlindMultichannel2021} algorithms.
 The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the Broyden–Fletcher–Goldfarb–Shanno (BFGS) \cite{brodlie1977assessment} method to estimate the Hessian of the problem.
@@
 where \(\mtxb{H}_i\) is the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) of length \(L\) which represents the system to be identified.
-For this paper, the length of the impulse responses \(L\) is assumed to be known.
+For this paper, the length \(L\) of the impulse responses is assumed to be known.
 
@@
 which states that the channel output signal convolved with the impulse response of another is equal to the vice-versa as follows from the commutativity property of the convolution.
-Left-multiplication and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g., \cite{huangAdaptiveMultichannelLeast2002} for a more detailed derivation) yields the system of equations
+Left-multiplication with \(\x_i(n)\), assuming deterministic \(\h_j\), and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g., \cite{huangAdaptiveMultichannelLeast2002} for a more detailed derivation) yields the system of equations
 \begin{equation}
@@
     \end{bmatrix}^\T\)
-denote the time-domain overlap-save matrices.
+denote the time-domain overlap-save matrices \cite{huangClassFrequencydomainAdaptive2003}.
 
@@
 This has drawbacks, such as the dependence on one or a small number of dedicated devices and a potentially large number of signals to be processed on these devices.
-Therefore, it is advantageous to consider ad-hoc network topologies, as we do in this paper, where nodes only communicate with their respective neighbors.
+Therefore, it can be advantageous to consider ad-hoc network topologies, as we do in this paper, where nodes only communicate with their respective neighbors.
 We refer the reader to \cite{bertrandApplicationsTrendsWireless2011b} for a more detailed review of WSNs and their topologies.
@@
 
-The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the update step as
+The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
 \begin{equation}
@@
 \end{equation}
-where \(\sigma_s^2\) and \(\sigma_v^2\) are the variance of signal and noise respectively which both are modelled by (channel-independent) white Gaussian noise (WGN).
+where \(\sigma_s^2\) and \(\sigma_v^2\) are the variance of signal and noise respectively which for this paper both are modelled by (channel-independent) white Gaussian noise (WGN).
 
-The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)) with a ring topology where each node transmits its signal information to one neighbor.
-The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.
-The step sizes are hand tuned for similar convergence speed: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
+For this paper, the first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)) with a ring topology where each node transmits its signal information to one neighbor.
+The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8\!\times\!10^{5}\) samples of WGN to ensure convergence of all algorithms.
+The step sizes are hand tuned, so that the steady state is reached at similar frame counts (or later than the proposed algorithm): \(\mu_{\text{MCQN}}=0.01,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
 \autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).

### 2022-05-07 python/simulation_1/plot.py
new plots for simulation 1

@@ -163,14 +163,16 @@ for SNR in SNRs:
 
 # %%
 fig = plt.figure(figsize=(5, 2.5))
-plt.plot(SNRs, 20 * np.log10(err_MCQN_avg), marker="o", label="MCQN")
-plt.plot(SNRs, 20 * np.log10(err_NMCFLMS_avg), marker=">", label="NMCFLMS")
-plt.plot(SNRs, 20 * np.log10(err_LPRNMCFLMS_avg), marker="^", label=r"$l_p$-RNMCFLMS")
+plt.plot(SNRs, 20 * np.log10(err_MCQN_avg), ":", marker="o", label="MCQN")
+plt.plot(SNRs, 20 * np.log10(err_NMCFLMS_avg), "--", marker=">", label="NMCFLMS")
+plt.plot(
+    SNRs, 20 * np.log10(err_LPRNMCFLMS_avg), "-.", marker="^", label=r"$l_p$-RNMCFLMS"
+)
 plt.plot(
     SNRs,
     20 * np.log10(err_ADMM_newton_fq_diag_avg),
     marker="s",
-    label="ADMM BSI",
+    label="proposed",
 )
 plt.xlabel("SNR [dB]")
 plt.ylabel("Average NPM [dB]")
@@ -185,30 +187,37 @@ utils.savefig(fig, "NPM_over_SNR_L%d_M%d" % (L, N_sens))
 
 # %%
 fig = plt.figure(figsize=(5, 2.5))
-SNR = 10
+SNR = 20
 if err_MCQN_[SNR] is not None:
-    plt.plot(20 * np.log10(np.nanmedian(err_MCQN_[SNR], axis=0)[:-L]), label="MCQN")
+    plt.plot(
+        20 * np.log10(np.nanmedian(err_MCQN_[SNR], axis=0)[:-L]), "--", label="MCQN"
+    )
 if err_NMCFLMS_[SNR] is not None:
     plt.plot(
-        20 * np.log10(np.nanmedian(err_NMCFLMS_[SNR], axis=0)[:-L]), label="NMCFLMS"
+        20 * np.log10(np.nanmedian(err_NMCFLMS_[SNR], axis=0)[:-L]),
+        ":",
+        label="NMCFLMS",
     )
 if err_LPRNMCFLMS_[SNR] is not None:
     plt.plot(
         20 * np.log10(np.nanmedian(err_LPRNMCFLMS_[SNR], axis=0)[:-L]),
[…]

### 2022-05-07 paper.tex
new plots for simulation 1 in paper

@@
     \centering
-    \hspace*{-0.2cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_time_SNR10.png}\label{fig:perf_eval:NPM_over_time_SNR10}}\\
+    \hspace*{-0.2cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/simulation_1/plots/NPM_over_time_SNR20.png}\label{fig:perf_eval:NPM_over_time_SNR20}}\\
     \vspace*{-0.3cm}
-    \hspace*{-0.2cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/plots/NPM_over_SNR_L64_M5.png}\label{fig:perf_eval:NPM_over_SNR_L64_M5}}
+    \hspace*{-0.2cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=4cm]{python/simulation_1/plots/NPM_over_SNR_L64_M5.png}\label{fig:perf_eval:NPM_over_SNR_L64_M5}}
     \vspace*{-0.2cm}
-    \caption{(a) NPM at \(\text{SNR}=10\,\text{dB}\) over frame index \(m\) and (b) steady-state NPMs over different SNRs.}
+    \caption{(a) NPM at \(\text{SNR}=20\,\text{dB}\) over frame index \(m\) and (b) steady-state NPMs over different SNRs.}
     \label{fig:perf_eval:NPM_over_time_exp1}
@@
 The step sizes are hand tuned, so that the steady state is reached at similar frame counts (or later than the proposed algorithm): \(\mu_{\text{MCQN}}=0.01,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
-\autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).
+\autoref{fig:perf_eval:NPM_over_time_SNR20} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).
 \autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median (30 Monte-Carlo runs) where the averaged NPM of \(100\) frames after convergence is plotted.

### 2022-05-07 python/simulation_1/plot.py
new plots for simulation 1

@@ -163,8 +163,8 @@ for SNR in SNRs:
 
 # %%
 fig = plt.figure(figsize=(5, 2.5))
-plt.plot(SNRs, 20 * np.log10(err_MCQN_avg), ":", marker="o", label="MCQN")
-plt.plot(SNRs, 20 * np.log10(err_NMCFLMS_avg), "--", marker=">", label="NMCFLMS")
+plt.plot(SNRs, 20 * np.log10(err_MCQN_avg), "--", marker="o", label="MCQN")
+plt.plot(SNRs, 20 * np.log10(err_NMCFLMS_avg), ":", marker=">", label="NMCFLMS")
 plt.plot(
     SNRs, 20 * np.log10(err_LPRNMCFLMS_avg), "-.", marker="^", label=r"$l_p$-RNMCFLMS"
 )

### 2022-05-07 python/simulation_2/plot.py
new plots for simulation 2

@@ -108,7 +108,7 @@ plt.show()
 lim = 2500
 for N_sens in [4, 8]:
     lines = ["-", "--", "-.", ":"]
-    fig = plt.figure(figsize=(3, 2.5))
+    fig = plt.figure(figsize=(2.75, 2.5))
     for i in range(len(densities)):
         if err_ADMM_newton_fq_diag_[i][N_sens] is not None:
             plt.plot(

### 2022-05-08 paper.tex
only katy's comments left

@@
     % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
-    \hspace*{-0.2cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/simulation_2/plots/NPM_over_time_M4.png}
-        \put(57,42.5){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.6]{tikz/topology_inset_simulation}}
+    \hspace*{-0.1cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.8cm 0.3cm},clip,height=4cm]{python/simulation_2/plots/NPM_over_time_M4.png}
+        \put(60,53){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.6]{tikz/topology_inset_simulation}}
     \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
-    \hspace*{-0.0cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/simulation_2/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
+    \hspace*{0.3cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.8cm 0.3cm},clip,height=4cm]{python/simulation_2/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
     \vspace*{-0.2cm}

### 2022-05-08 paper.tex
include katy's comments

@@
 \begin{abstract}
-    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a wireless sensor network (WSN).
+    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain, using the alternating direction method of multipliers (ADMM) in a wireless sensor network (WSN).
     The network consists of a fixed number of nodes each equipped with a processing unit and a sensor that represents an output channel of the SIMO system.
-    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels in a way that is determined by the network topology.
-    Each node delivers estimates for the subset of channel frequency responses, which then are combined into a consensus estimate per channel using general-form consensus ADMM in an adaptive updating scheme.
-    With numerical simulations, we show that it is possible to achieve convergence speeds and steady-state misalignment values comparable to fully centralized low-cost frequency-domain algorithms.
+    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems containing a subset of channels, in a way that is determined by the network topology.
+    Each node delivers estimates for the subset of channel frequency responses, which are then combined into a consensus estimate per channel using general-form consensus ADMM in an adaptive updating scheme.
+    Using numerical simulations, we show that it is possible to achieve convergence speeds and steady-state misalignment values comparable to fully centralized low-cost frequency-domain algorithms.
 \end{abstract}
@@
 It was introduced in \cite{satoMethodSelfRecoveringEqualization1975} and various algorithms have been proposed since.
-Early algorithms used higher-order statistics \cite{godardSelfRecoveringEqualizationCarrier1980,tongNewApproachBlind1991,mendelTutorialHigherorderStatistics1991} for channel estimation, however a high computational complexity has motivated research into algorithms using only second-order statistics.
-Such algorithms include the cross-relation (CR) algorithm \cite{langtongBlindIdentificationEqualization1994, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017} and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
-Out of various multichannel BSI algorithms which have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.
-The normalized multi-channel frequency-domain LMS (NMCFLMS) \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} algorithm for instance is an efficient algorithm utilizing the fast Fourier transform (FFT) which has been extended to include constraints to improve robustness to noise and performance on acoustic impulse responses such as the RNMCFLMS \cite{huNoiseRobustBlind2015}, \(l_p\)-RNMCFLMS \cite{heNoiseRobustFrequencyDomain2018} or phase-constrained-\(l_p\)-RNMCFLMS \cite{joRobustBlindMultichannel2021} algorithms.
-The quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} on the other hand is a time-domain algorithm that utilizes the Broyden–Fletcher–Goldfarb–Shanno (BFGS) \cite{brodlie1977assessment} method to estimate the Hessian of the problem.
+Early algorithms used higher-order statistics \cite{godardSelfRecoveringEqualizationCarrier1980,tongNewApproachBlind1991,mendelTutorialHigherorderStatistics1991} for channel estimation, however, a high computational complexity has motivated research into algorithms that only use second-order statistics.
+Such algorithms include the cross-relation (CR) algorithm \cite{langtongBlindIdentificationEqualization1994, guanghanxuLeastsquaresApproachBlind1995}, subspace algorithms \cite{moulinesSubspaceMethodsBlind1995,gannotSubspaceMethodsMultimicrophone2003,diamantarasEfficientSubspaceMethod2008,mayyalaStructureBasedSubspaceMethod2017}, and maximum-likelihood algorithms \cite{yingbohuaFastMaximumLikelihood1996}.
+Out of the various multichannel BSI algorithms that have been proposed, adaptive cross-relation-based least-mean-squares (LMS) algorithms in the time and frequency domain are the ones most widely used.
+For instance, the normalized multi-channel frequency-domain LMS (NMCFLMS) \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} algorithm is an efficient algorithm utilizing the fast Fourier transform (FFT) which has been extended to include constraints which improve robustness to noise and performance for acoustic impulse responses such as the RNMCFLMS \cite{huNoiseRobustBlind2015}, \(l_p\)-RNMCFLMS \cite{heNoiseRobustFrequencyDomain2018} or phase-constrained-\(l_p\)-RNMCFLMS \cite{joRobustBlindMultichannel2021} algorithms.
+On the other hand, the quasi-Netwon algorithm \cite{habetsOnlineQuasiNewtonAlgorithm2010} is a time-domain algorithm that utilizes the Broyden–Fletcher–Goldfarb–Shanno (BFGS) \cite{brodlie1977assessment} method to estimate the Hessian of the problem.
 
-The expanding field of distributed signal processing in wireless sensor networks (WSN) brought forward algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, or beamforming \cite{6663655,9670697}, however, research into the task of BSI is limited.
-While there exist time-domain algorithms as introduced in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, they do not pose apt comparisons to the frequency-domain algorithm being proposed.
+The expanding field of distributed signal processing in wireless sensor networks (WSN) has brought forward algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,9670697}.
+However, research into the task of BSI is limited.
+While there exist time-domain algorithms as introduced in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, they do not pose apt comparisons to the frequency-domain algorithm being proposed here.
 In this paper, we use the general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} to distribute and solve the optimization problem posed by the task.
-We separate the inter-channel cross-relations of the BSI problem according to the network's topology, i.e., each node solves a sub-problem using data from its network neighbors, and the entirety of connected nodes subsequently reaches a consensus for the channel frequency responses.
-The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
+We separate the inter-channel cross-relations of the BSI problem according to the network's topology, i.e., each node solves a sub-problem using data from its network neighbors and the entirety of the connected nodes subsequently reach a consensus for the channel frequency responses.
+The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm which is also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
 
-As shown in numerical simulations, the resulting algorithm provides good estimation results as compared to state-of-the-art centralized frequency-domain algorithms.
+As shown in numerical simulations, the resulting algorithm provides good estimation results when compared to state-of-the-art centralized frequency-domain algorithms.
 
@@
 \label{ssec:signal_model}
-We consider an acoustic SIMO system with the input signal \(\mtxb{s}(n) = \begin{bmatrix}
+We consider an acoustic SIMO system with input signal \(\mtxb{s}(n) = \begin{bmatrix}
     s(n)&s(n-1)&\ldots&s(n-2L+2)
-\end{bmatrix}^{\T}\) and the \(M\) output signals \(\x_i(n)= \begin{bmatrix}
+\end{bmatrix}^{\T}\) and \(M\) output signals \(\x_i(n)= \begin{bmatrix}
     x_i(n)&x_i(n-1)&\ldots&x_i(n-L+1)
@@
 where \(\mtxb{H}_i\) is the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) of length \(L\) which represents the system to be identified.
-For this paper, the length \(L\) of the impulse responses is assumed to be known.
+For the purpose of this paper, the length \(L\) of the impulse responses is assumed to be known.
 
 % #############################################################################
-\subsection{Cross-relation approach}
+\subsection{Cross-relation Approach}
 \label{ssec:cross_rel}
@@
 which states that the channel output signal convolved with the impulse response of another is equal to the vice-versa as follows from the commutativity property of the convolution.
-Left-multiplication with \(\x_i(n)\), assuming deterministic \(\h_j\), and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\) and combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g., \cite{huangAdaptiveMultichannelLeast2002} for a more detailed derivation) yields the system of equations
+Left-multiplication with \(\x_i(n)\), assuming deterministic \(\h_j\), and applying the expectation operator to form the covariance matrix \(\R_{ij}(n) = \ev{\x_i(n) \x_j^\T(n)}\), and then combining all cross-relations \eqref{eq:cross_rel:equality_conv} (see e.g., \cite{huangAdaptiveMultichannelLeast2002} for a more detailed derivation) yields the system of equations
 \begin{equation}
@@
 \end{bmatrix}^\T\).
-Formulating the problem in the frequency domain, the derivation is analogous.
+The derivation is analogous when formulating the problem in the frequency domain.
 We denote all frequency-domain variables in bold italic (e.g.
@@
 Analogously to the time-domain formulation, the \(ML \times 1\) vector \(\hf\) is a stacked vector of complex-valued frequency responses.
-The null-space problem in \eqref{eq:frequency_domain:null_space} can not be solved by computing the eigenvector corresponding to the zero-valued eigenvalue because, in the presence of noise, the system matrix \(\Rf\) is of full rank and may not have any.
-Therefore it is best solved by posing it as a quadratic minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002} with a non-triviality constraint to avoid the zero solution:
+The null-space problem in \eqref{eq:frequency_domain:null_space} cannot be solved by computing the eigenvector corresponding to the zero-valued eigenvalue because, in the presence of noise, the system matrix \(\Rf\) is of full rank and may not have any.
+Therefore, it is best solved by posing it as a quadratic minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002} with a non-triviality constraint to avoid the zero solution:
 %  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
@@
 The major types of network topologies for distributed signal processing can be distinguished by the way information is shared within the network.
-For example, in a centralized or star topology, where nodes transmit their signals to a dedicated device (fusion center), the processing is (partly) centralized.
+For example, in a centralized or star topology where nodes transmit their signals to a dedicated device (fusion center), the processing is (partly) centralized.
 This has drawbacks, such as the dependence on one or a small number of dedicated devices and a potentially large number of signals to be processed on these devices.
@@
 Correspondingly, let \(\Rset_i \subseteq \Mset\) be the set of indices of nodes from which node \(i\) receives signal information, i.e., if \(i \in \Tset_j\), then \(j \in \Rset_i\).
-Note that \(i \in \Tset_i\) and \(i \in \Rset_i\) for simplifying notation in later sections, but evidently, no actual transmission is necessary, as the signal \(\x_i(n)\) is available locally at node \(i\).
+Note that \(i \in \Tset_i\) and \(i \in \Rset_i\) for simplifying notation in later sections, but no actual transmission is necessary as the signal \(\x_i(n)\) is available locally at node \(i\).
 \autoref{fig:sensor_network:WSN_overview} shows a network where each node shares its signal information with one or more neighbors.
@@
 (b) Data transmission between nodes \(i\) and \(j\) for each frame \(m\).
-(c) shows the equivalent parameter mapping of the local variable components \(({\wf}_i)_j\) to the global variable components \(\hf_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
+(c) Parameter mapping of the local variable components \(({\wf}_i)_j\) to the global variable components \(\hf_j\) via \(\mathcal{G}(i,j)\) for the network in (a).}
     \label{fig:sensor_network:WSN_mapping}
@@
 Recall that in addition to its own signal information, each node \(i \in \Mset\) has access to that of nodes \(j \in \Rset_i\).
-This is used to solve a BSI sub-problem of the same form as in \eqref{eq:frequency_domain:min_prob}, which however only involves the subset of channels.
-We define the local variables \(\wf_i = \left[ \left\{ (\wf_i)_j^\T \right\}_{j \in \Rset_i} \right]^\T\), which is a stacked vector of locally estimated frequency responses (cf.
+This is used to solve a BSI sub-problem of the same form as in \eqref{eq:frequency_domain:min_prob}, which only involves the subset of channels.
+We define the local variables \(\wf_i = \left[ \left\{ (\wf_i)_j^\T \right\}_{j \in \Rset_i} \right]^\T\), which are stacked vectors of locally estimated frequency responses (cf.
 \autoref{fig:problem_splitting:parameter_mapping}).
@@
 \autoref{fig:problem_splitting:parameter_mapping}).
-For brevity, the mapped global variables \((\tilde{\hf}_i)_j = \hf_{\mathcal{G}(i,j)}\) are introduced.
+For the sake of brevity, the mapped global variables \((\tilde{\hf}_i)_j = \hf_{\mathcal{G}(i,j)}\) are introduced.
 This defines \(\tilde{\hf}_i = \left[ \left\{ \hf_j^\T \right\}_{j \in \Rset_i} \right]^\T\).
@@
 \end{align}
-where \(k\) is the iteration index. Evidently, this is an iterative algorithm, therefore we will introduce the online/adaptive aspect of the proposed algorithm in the following.
+where \(k\) is the iteration index. Evidently, this is an iterative algorithmand we will therefore introduce the online/adaptive aspect of the proposed algorithm in the following.
 
@@
 \end{equation}
-The computations of local, consensus and dual variables, in \eqref{eq:online_admm:local_update}, \eqref{eq:online_admm:consensus_update} and \eqref{eq:online_admm:dual_update} respectively, require data transmitted by other nodes (cf.
+The computations of local, consensus, and dual variables in \eqref{eq:online_admm:local_update}, \eqref{eq:online_admm:consensus_update} and \eqref{eq:online_admm:dual_update} respectively, require data transmitted by other nodes (cf.
 \autoref{fig:sensor_network:WSN_detail}).
-For this paper, we assume that all transmissions are done instantaneously and error-free whenever variables are required by neighboring nodes.
+For this paper, we assume that all transmissions are done instantaneously whenever variables are required by neighboring nodes and are error-free.
 
@@
 The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8\!\times\!10^{5}\) samples of WGN to ensure convergence of all algorithms.
-The step sizes are hand tuned, so that the steady state is reached at similar frame counts (or later than the proposed algorithm): \(\mu_{\text{MCQN}}=0.01,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
+The step sizes are hand-tuned, so that the steady state is reached at similar frame counts (or later than the proposed algorithm): \(\mu_{\text{MCQN}}=0.01,\,\mu_{\text{NMCFLMS}}=0.3,\,\mu_{l_p-\text{NMCFLMS}}=0.4,\,\mu_{\text{ADMM}}=0.6,\,\rho=1,\,\eta=0.98 \).
 \autoref{fig:perf_eval:NPM_over_time_SNR20} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).
 \autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median (30 Monte-Carlo runs) where the averaged NPM of \(100\) frames after convergence is plotted.
-It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
-The choice to present the median is based on the fact that randomly generated impulse responses may have close common zeros diminishing identifiability (for all algorithms) \cite{naylorNearCommonZerosBlind2008}, here then considered outliers.
+It can be observed that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
+The choice to present the median is based on the fact that randomly generated impulse responses may have (near) common zeros which diminish the identifiability of these systems \cite{naylorNearCommonZerosBlind2008}, here considered outliers.
 
@@
 \autoref{fig:perf_eval:NPM_over_time_M4} and \autoref{fig:perf_eval:NPM_over_time_M8} show the median NPM (30 Monte-Carlo runs) for \(M=4\) and \(M=8\) respectively.
-The plots suggests a proportional relation of convergence speed, channel number \(M\) and \(\zeta\) while the steady-state error appears to be not dependent on \(\zeta\).
+The plots suggest a proportional relation between convergence speed, channel number \(M\) and \(\zeta\).
+Moreover, the steady-state error appears to be independent of \(\zeta\).
 
